---
title: "WHAM_Run32A_addLPUE_qRand"
output: html_document
date: '2022-05-06'
---

## Model description
Recruitment random effects as in run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with additional LPUE index (index 3). The selectivity for the LPUE index was set to mirror that estimated for the fleet. A catchability random effect was applied to the LPUE index to account for process errors where standardization didn't completely account for unequal inclusion probability.

LPUE index and CV pulled from Plaice_LPUE_Standardization_Index_01242022.lxsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the LPUE index in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 3
#modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices)) # LPUE 
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 2), "logistic") # LPUE assumed logistic selectivity

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(2,0.4))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # set up index selectivity object
fix_index_sel[[3]] = 1:2 #fix logistic selectivity pars for third index because we aren't going to use it.

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block - index 3 (LPUE) selectivity will be the same as the fleet
randeffect <- c(rep("iid", 3), "none")#, asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(n_selblocks = 1+use_n_indices,
                 model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

# Setup catchability random effect
catchability <- list(re=c("none", "none", "iid")) # Try applying catchability random effect to account for process errors where standardization didn't completely account for unequal inclusion probability.

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, catchability = catchability, model_name = "WHAM_Run32A") 
input$data$selblock_pointer_indices[,3] = 1 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run32A_addLPUE_qRand", "WHAM_Run32A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# WHAM_Run32A <- fit_wham(input, do.osa =F, do.retro=F) # Run without OSA and retro calculations
WHAM_Run32A <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=TRUE) 
check_convergence(WHAM_Run32A)
print(paste("Number of parameters", length(WHAM_Run32A$par), sep=" "))

plot_wham_output(mod=WHAM_Run32A, out.type='html')
# plot_wham_output(mod=WHAM_Run32A, out.type='png', dir.main = paste(here::here(), "WHAM_Run32A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run32A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run32A_addLPUE_qRand", "WHAM_Run32A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run32A_addLPUE_qRand/WHAM_Run32A_input.rds", sep="/"))

# Rerun data
ReRun32A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Returned an "error during model fit - check for unidentifiable parameters" when a full state-space model with random effects for all ages was run. However, the run converged with only a recruitment random effect was included. 

LPUE catchability estimates varied over time in run 32A but NEFSC catchability estimates were similar to those in run 32.

OSA residuals for run 32A fit to the fleet and the LPUE index were more normally distributed, while the NEFSC residuals were similarly distributed. OSA residuals for fit to age comp data were similarly or slightly more normally distributed compared to run 32. 
