---
title: "WHAM_Run23A_SelRandEffect-iidFleetOnly"
output: html_document
date: '2022-03-16'
---

## Model description
This run is similar to run 23 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity), but the iid random effect for selectivity is only applied to the fleet, index selectivities are constant over time. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # NA means do not fix RUN THIS LINE IF YOU GET AN ERROR THAT fix_index_sel can't be found then run the below to overwrite the correctly specified object with ages you want to fix!!!

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run23A") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run23A_SelRandEffect-iidFleetOnly", "WHAM_Run23A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run23A <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run23A)
print(paste("Number of parameters", length(WHAM_Run23A$par), sep=" "))

plot_wham_output(mod=WHAM_Run23A, out.type='html')
# plot_wham_output(mod=WHAM_Run23A, out.type='png', dir.main = paste(here::here(), "WHAM_Run23A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run23A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run23A_SelRandEffect-iidFleetOnly", "WHAM_Run23A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run23A_SelRandEffect-iidFleetOnly/WHAM_Run23A_input.rds", sep="/"))

# Rerun data
ReRun23A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Higher AIC but lower Mohn's rho values for SSB and Fbar than Run23. Similar fleet age comp residual patterns and scale, patterns similar for indices but higher age comp residuals in Run23A. Run23A has larger likelihood contributions across the board. Fleet residuals are similar, but OSA residuals for indices are slightly less normally distributed than those for Run23. Most differences in index selectivity between the two runs occur in ages 2-3, some variability at older ages but these tend to be smaller variations. Selectivity at older ages (5+) tended to be lower in run 23A than run 23. Run 23A had slightly higher SSB and R, and lower F expectations than run 23 and SSB and F CVs were lower for Run23A for the last ~15 years of the timeseries.

