---
title: "WHAM_Run18_2SelBlock_logistic-normal-agecomp"
output: html_document
date: '2022-03-01'
---

## Model description
This run is the same as run 16 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, two selectivity blocks, one from 1980-1999 and another from 2000-2019), but changes the age composition model from multinomial to logistic-normal-miss0 which applies a logistic normal model and treats zero observations as missing.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_2SelBlock.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
use_n_selBlocks = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4), c(2,0.4)) # logistic parameters for each selectivity block, based on model type

init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:(asap3$dat$n_fleets*use_n_selBlocks), function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

# Specify age_comp model to use
age_comp <- "logistic-normal-miss0"

input <- prepare_wham_input(asap3, selectivity = sel_list, age_comp = age_comp, model_name = "WHAM_Run18") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run18_2SelBlock_logistic-normal-agecomp", "WHAM_Run18_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run18 <- fit_wham(input, do.osa=F,do.retro=F) 
#age 11 selectivity for second survey is going to 1
WHAM_Run18$parList$logit_selpars #[2,11]
#suggest fixing this selectivity at 1. OR redo free selectivity exercise with this age comp likelihood.
WHAM_Run18 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run18)
print(paste("Number of parameters", length(WHAM_Run18$par), sep=" "))

plot_wham_output(mod=WHAM_Run18, out.type='html')
# plot_wham_output(mod=WHAM_Run18, out.type='png', dir.main = paste(here::here(), "WHAM_Run18", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run18, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run18_2SelBlock_logistic-normal-agecomp", "WHAM_Run18_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run18_2SelBlock_logistic-normal-agecomp/WHAM_Run18_input.rds", sep="/"))

# Rerun data
Rerun18 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model converged but hessian was not invertible. Index selectivity patterns look less dome shaped, in particular selectivity increases from age 9-11+ for index 2 (NEFSC fall), while run 16 only had an increase in selectivity between ages 10 and 11+. May be worth exploring this age comp model in conjunction with logistic selectivity for fleet 2.
