---
title: "WHAM_Run12_FreeSelectivity-at-age"
output: html_document
date: '2022-02-25'
---

## Model description
This run is similar to [run 2](https://github.com/ahart1/PlaiceWG2021/blob/main/Plaice_Baseline_UpdatedData_Runs.Rmd) and uses revised WHAM, updated maturity and natural mortality. Selectivity is freely estimated for all fleets and ages. Commercial fleet selectivity is assumed to be logistic, while survey age-specific selectivity was estimated. 

Major differences from run 2 include: revised discard data (estimated rather than imputed) and an 11+ group in the NEFSC spring and fall surveys.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel = lapply(1:use_n_indices, function(x) c(rep(0.5,8),1,1,1))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index 
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run12") 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run12 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run12)
print(paste("Number of parameters", length(WHAM_Run12$par), sep=" "))

plot_wham_output(mod=WHAM_Run12, out.type='html')
# plot_wham_output(mod=WHAM_Run12, out.type='png', dir.main = paste(here::here(), "WHAM_Run12", sep="/"))
```

### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run12_FreeSelectivity-at-age", "WHAM_Run12_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run12, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run12_FreeSelectivity-at-age", "WHAM_Run12_model.rds", sep="/"))
```

## Comments
Model converged but hessian was not invertible. Next step is to try fixing selectivity for 1+ ages. Since NEFSC spring and fall selectivities appear dome-shaped except for 11+ in the fall, try fixing spring age 4 and 5 selectivity at 1 and fall age 4 selectivity at 1 (similar to freely estimated values for these ages). 

