---
title: "WHAM_Run24_SelRandEffect-ar1_y"
output: html_document
date: '2022-03-02'
---

## Model description
This run is similar to run 23 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity), but incorporates an AR1 random effect for annually correlated selectivity ("ar1_y" option) instead of an iid random effect.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("ar1_y", asap3$dat$n_fleet_sel_blocks), rep("ar1_y", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run24") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run24_SelRandEffect-ar1_y", "WHAM_Run24_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run24 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run24)
print(paste("Number of parameters", length(WHAM_Run24$par), sep=" "))

plot_wham_output(mod=WHAM_Run24, out.type='html')
# plot_wham_output(mod=WHAM_Run24, out.type='png', dir.main = paste(here::here(), "WHAM_Run24", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run24, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run24_SelRandEffect-ar1_y", "WHAM_Run24_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run24_SelRandEffect-ar1_y/WHAM_Run24_input.rds", sep="/"))

# Rerun data
Rerun24 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Age comp residuals for fleet and indices are a bit larger than for run 23. There are also larger retrospective patterns than run 23. Recruitment CV at the end of the timeseries is higher than run 23, and full F estimates in the mid-1990s were much higher for some years than in run 23. OSA residuals may be a bit more normally distributed thatn those for run 23.

