---
title: "WHAM_Run9_RevisedData-M-Maturity"
output: html_document
date: '2022-02-28'
---

## Model description

This run is similar to [run 1](https://github.com/ahart1/PlaiceWG2021/blob/main/Plaice_Baseline_UpdatedData_Runs.Rmd) and uses revised WHAM data, updated M, and updated maturity as an input. The run uses the model as specified in the ASAP-style .dat input file.

Major differences from run 1 include: revised discard data (estimated rather than imputed) and an 11+ group in the NEFSC spring and fall surveys (with selectivity of ages 10-11+ initially set at 1). Total catch was also corrected to be biomass rather than numbers. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
input <- prepare_wham_input(asap3, model_name = "WHAM_Run9") 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run9 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run9)
print(paste("Number of parameters", length(WHAM_Run9$par), sep=" "))

plot_wham_output(mod=WHAM_Run9, out.type='html')
# plot_wham_output(mod=WHAM_Run9, out.type='png', dir.main = paste(here::here(), "WHAM_Run9", sep="/"))
```

### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run9_RevisedData-M-Maturity", "WHAM_Run9_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run9, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run9_RevisedData-M-Maturity", "WHAM_Run9_model.rds", sep="/"))
```

## Comments
Strong residual pattern for fleet 1 catch, index 1 & 2 age comps don't fit particularly well for ages 1-5 and there are strong negative residuals for index age 1 & 2 with positive residuals for older ages. 
