---
title: "WHAM_Run27_Full-State-Space"
output: html_document
date: '2022-03-16'
---

## Model description
This run is similar to run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), and implements a full state-space model with random effects for all NAA.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# Specify recruitment model
recruit_model = 2 # random effects with a constant mean

# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") 
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment
NAA_re$cor = "iid" # iid random effects are the default

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, recruit_model = recruit_model, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run27") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run27_Full-State-Space", "WHAM_Run27_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run27 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run27)
print(paste("Number of parameters", length(WHAM_Run27$par), sep=" "))

plot_wham_output(mod=WHAM_Run27, out.type='html')
# plot_wham_output(mod=WHAM_Run27, out.type='png', dir.main = paste(here::here(), "WHAM_Run27", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run27, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run27_Full-State-Space", "WHAM_Run27_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run27_Full-State-Space/WHAM_Run27_input.rds", sep="/"))

# Rerun data
ReRun27 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Run27 has a smaller AIC and smaller Mohn's rho for R, SSB, and Fbar compared to Run25 and Run26. Recruitment CVs were much higher than those in Run25, and SSB and Full F CVs were slightly higher. The fleet's Full F followed a similar trend but the scale differed slightly from Run25. Selectivity for index 2 (NEFSC fall) was less variable than in Run25. Selectivity for the index plus group (11+) was lower than that in Run25. Catch residuals were smaller and were slightly more evenly distributed around zero. Fleet and index fit to annual age comps appear to be a bit better and age comp residuals were generally smaller. Likelihood contributions were generally smaller than those in Run25, except for the NAA likelihood contribution which was larger. 
 
Age 2 residuals were largely positive with negative residuals in the last ~15 years, age 3 residuals were evenly distributed about zero until the last ~15 years of the timeseries which were biased negatively. Age 4 had larger negative residuals and again were biased negatively over the last ~15 years. Age 5 and 6 had more evenly distributed residuals, but ages 8-11 had more negatively biased residuals for the later half of the timeseries. OSA residuals are slightly more normally distributed than Run25. 

