---
title: "WHAM_Run29DE_splitNEFSC-FreeSel-nlAgeComp"
output: html_document
date: '2022-04-11'
---

## Model description
This script contains two additional model runs: run 29D freely estimates selectivity-at-age, run 29E explores a logistic-normal-miss0 age composition likelihood model. 

Both runs implement a full state-space model as in run 29 with NEFSC bottom trawl surveys split into Albatross (1980-2008, indices 1 and 3 for spring/fall) and Bigelow (2009-2019, indices 2 and 4 for spring/fall) time series. No iid random effect for selectivity were implemented in run 29D, but run 29E included selectivity random effects for the fleet and index 1 (Albatross spring).

Run 29D freely estimated selectivity at age, and fixed catchability at 2 for all indices. 

Based on selectivity estimates from run 29D, run 29E fixed full selectivity at age 4 for index 1 (Albatross spring), ages 4 and 5 for index 2 (Bigelow spring), ages 4, 5, and 11 for index 3 (Albatross spring), and age 4 for index 4 (Bigelow fall). Catchability was not fixed for any index for run 29E, but the age composition likelihood was set to logistic-normal-miss0.


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC.DAT", sep="/"))
```

## Run 29D
### Run 29D: Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
#init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

randeffect <- c(rep("none", asap3$dat$n_fleet_sel_blocks),  "none", rep("none", 3)) # Don't include selectivity random effect

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))
# Set up catchability settings
catchability <- list(
  initial_q = rep(2,use_n_indices))

# Format input
input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, 
  catchability = catchability, model_name = "WHAM_Run29", age_comp = "logistic-normal-miss0")
input$map$logit_q = factor(rep(NA,use_n_indices)) #don't estimate q
#input$data$selpars_lower[] = 1e-6
```

### Run 29D: Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29DE_splitNEFSC-FreeSel-nlAgeComp", "WHAM_Run29D.rds", sep="/"))
```

### Run 29D: Fit model, check convergence, and run diagnostics
```{r}
# Run model and check convergence
WHAM_Run29D_free <- fit_wham(input, do.osa=F, do.retro=F) 
check_convergence(WHAM_Run29D_free)

# Look at catchability results 
q_sel = t(sapply(1:4, function(x) {
  sel = WHAM_Run29D_free$rep$QAA[1,x,]
  q = max(sel)
  sel = sel/q
  return(c(q,sel))
}))
q_sel[1:2,1]/q_sel[3:4,1]
q_sel[,-1]
q_sel[,1]

#plot_wham_output(mod=WHAM_Run29D_free, out.type='html')
```

### Run 29D: Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29D_free, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29DE_splitNEFSC-FreeSel-nlAgeComp", "WHAM_Run29D_free_model.rds", sep="/"))
```


## Run 29E: Use results of run 29D to implement better selectivity and explore logistic-normall-miss0 age comp likelihood
### Run 29E: Prepare model input
```{r}
# Fix selectivity
fix_index_sel[[1]] <- c(4) # Fix age 4  for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- 4:5 # Fix age 4 & 5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4:5,11) # Fix age 4, 5, and 11 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- 4 # Fix age 4  for for index 4 (NEFSC spring Bigelow)
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))
for(i in 1:4) init_index_sel[[i]][fix_index_sel[[i]]] <- 1 # replace initial values for 1 for the ages where selectivity fixed

randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks),  "iid", rep("none", 3)) # Don't include selectivity random effects except for index 1 (Albatross spring)
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index, same as Run 29D
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, 
  model_name = "WHAM_Run29E_ln_acomp", age_comp = "logistic-normal-miss0")
```

### Run 29E: Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29DE_splitNEFSC-FreeSel-nlAgeComp", "WHAM_Run29E_ln_acomp_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
Without OSA an retro
```{r}
WHAM_Run29E_ln_acomp <- fit_wham(input, do.osa=F, do.retro = F, MakeADFun.silent = TRUE) 
# Look at catchability results
q_sel = t(sapply(1:4, function(x) {
  sel = WHAM_Run29E_ln_acomp$rep$QAA[1,x,]
  q = max(sel)
  sel = sel/q
  return(c(q,sel))
}))
q_sel[1:2,1]/q_sel[3:4,1]
q_sel[,-1]
q_sel[,1]

```

With OSA and retro
```{r}
# Run with OSA residuals
input$par = WHAM_Run29E_ln_acomp$parList
WHAM_Run29E_ln_acomp <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run29E_ln_acomp)
print(paste("Number of parameters", length(WHAM_Run29E_ln_acomp$par), sep=" "))

plot_wham_output(mod=WHAM_Run29E_ln_acomp, out.type='html')
```

### Run 29E: Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29E_ln_acomp, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29DE_splitNEFSC-FreeSel-nlAgeComp", "WHAM_Run29E_ln_acomp_model.rds", sep="/"))
```

### Rerun model Run 29E using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29DE_splitNEFSC-FreeSel-nlAgeComp/WHAM_Run29E_ln_acomp_input.rds", sep="/"))

# Rerun data
ReRun29E <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment


