---
title: "WHAM_Run37A_VAST_ALL-randSel"
output: html_document
date: '2022-04-04'
---

## Model description
A full state-space model was implemented as in run 37 (logistic fleet selectivity, age-specific index selectivity, recruitment about the mean, fit to VAST index that combines all observed state indices), but an implemented a selectivity iid random effect for fleet and both indices. 

VAST numbers at age 1-9+ were taken from:
SPRING
- VAST Spatiotemporal survey index -> Age Runs -> Spring -> NumbersAtAgeSpring.csv
FALL
- VAST Spatiotemporal survey index -> Age Runs -> Fall -> NumbersAtAgeFall.csv

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateVASTIndices.DAT", sep="/"))

# Overwrite settings to stop using design-based NEFSC indices
asap3$dat$use_index_acomp[1:2] <- 0 # don't use index age comp
asap3$dat$use_index[1:2] <- 0 # don't use design-based NEFSC spring and fall indices

# Overwrite to use VAST index that integrates all available surveys (except LPUE index)
asap3$dat$use_index_acomp[11:12] <- 1 # use index age comp
asap3$dat$use_index[11:12] <- 1 # Use VAST model-based spring and fall indices

```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST spring
                       c(1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0)) # all VAST fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Setup storage object to populate 

fix_index_sel[[1]] <- c(2,3) # Fix age 3 & 4 for for index 1 all VAST spring
fix_index_sel[[2]] <- c(1,2) # Fix age 5 for for index 2 all VAST fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run37A") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37A_VAST_ALL-randSel", "WHAM_Run37A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run37A <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE) 
check_convergence(WHAM_Run37A)
print(paste("Number of parameters", length(WHAM_Run37A$par), sep=" "))

plot_wham_output(mod=WHAM_Run37A, out.type='html')
# plot_wham_output(mod=WHAM_Run37A, out.type='png', dir.main = paste(here::here(), "WHAM_Run37A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run37A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37A_VAST_ALL-randSel", "WHAM_Run37A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run37A_VAST_ALL-randSel/WHAM_Run37A_input.rds", sep="/"))

# Rerun data
ReRun37A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment

Adding iid selectivity random effects impacted the fleet but had little to no effect on the indices (minor variation in age 1 of index 1). Fit to index 1 is still poor with large positive residuals for most of the time series, but fit to index 2 has more evenly distributed residuals. Estimates appear to follow the same pattern as the fleet (same peaks). Full selection in the spring was fixed at older ages than in the fall, as was the case in model runs fit to observation-based indices.

This model had a smaller AIC and Mohn's rho patterns than Run37 (AIC isn't really comparable since different selectivity likelihood contribution). 
