---
title: "WHAM_Run34A_addMENH-LPUE_mirrorLPUE"
output: html_document
date: '2022-04-13'
---

## Model description
Recruitment random effects as in run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), with a iid selectivity random effect implemented for the fleet all indices except for the LPUE index (which mirrors the selectivity of the fleet for this run). This run fits to the NEFSC spring and fall indices and 3  additional indices: MENH spring and fall indices (index 3 and 4 respectively) and an LPUE index (index 5). 

MENH spring data was pulled from AMP_MENH_Spring_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

MENH fall data was pulled from AMP_MENH_Fall_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

LPUE index and CV pulled from Plaice_LPUE_Standardization_Index_01242022.lxsx


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MENH indices
asap3$dat$use_index_acomp[13:14] <- 1 # use index age comp
asap3$dat$use_index[13:14] <- 1 # use indices 13-14 (MENH)

# Overwrite settings to use the LPUE indicex in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 5
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 4), "logistic") # LPUE assumed logistic selectivity

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.8, 1, 0.4, 0.4, 0.5, 0.1, 0.1, 0.1, 0.1, 0.3, 0.1), # MENH spring (use starting estimates near those from run 31)
                       c(1, 0.4, 0.5, 0.2, 0.3, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1), # MENH fall (use starting estimates near those from run 31)
                       c(2,0.4)) # LPUE

# 0.04843349 0.6157584 0.6436321    1    1 0.8981852 0.8581329 0.8172894 0.7999838 0.8132373 0.6745355
# 0.2633954 0.7743464 0.8426259    1 0.9262489 0.8587785 0.6430631 0.6836228 0.6509611 0.5972868 0.9575805
# 0.8118541    1 0.7135416 0.4065451 0.3872475 0.1606907 0.1668656 0.1554841 0.1444159 0.3003880 0.09012246
# 1 0.3935902 0.5589707 0.2486273 0.35360393 0.07816696 0.07757999 0.07303873 0.04486841 0.2022034 0.03608968

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for index 1 NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for index 2 NEFSC fall
fix_index_sel[[3]][1] <- 2 # Fix age 2 for index 3 MENH spring
fix_index_sel[[4]][1] <- 1 # Fix age 1 for index 4 MENH fall
fix_index_sel[[5]] = 1:2 #fix logistic selectivity pars for third index because we aren't going to use it.

# Setup random effect by selectivity block - index 3 (LPUE) selectivity will be the same as the fleet
randeffect <- c("iid", rep("iid", 4), "none")#, asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(n_selblocks = 1+use_n_indices,
                 model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run34A") 
input$data$selblock_pointer_indices[,5] = 1 # Mirror selectivity for LPUE index (5) using fleet selectivity
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run34A_addMENH-LPUE_mirrorLPUE", "WHAM_Run34A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# WHAM_Run34A <- fit_wham(input, do.osa =F, do.retro=F) # Run without OSA and retro calculations
WHAM_Run34A <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run34A)
print(paste("Number of parameters", length(WHAM_Run34A$par), sep=" "))

plot_wham_output(mod=WHAM_Run34A, out.type='html')
# plot_wham_output(mod=WHAM_Run34A, out.type='png', dir.main = paste(here::here(), "WHAM_Run34A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run34A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run34A_addMENH-LPUE_mirrorLPUE", "WHAM_Run34A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run34A_addMENH-LPUE_mirrorLPUE/WHAM_Run34A_input.rds", sep="/"))

# Rerun data
ReRun34A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment


