---
title: "Plaice_Bridge_Runs"
output: html_document
---

This document contains code to run a bridge run (VPA to WHAM using same ASAP .dat file used for ASAP bridge run) and an initial WHAM run with updated assessment data based on ToR2&3 data decisions.

# Load R packages
```{r}
library(tidyverse)
library(wham)
```

# Try bridge run - VPA to WHAM: Run 1 in WG spreadsheet
This run uses the same file as the ASAP bridge run, the abundance indices at each age mean that selectivity for each index is estimated at 1. 

Load ASAP .dat file used for ASAP bridge run & prep for use in WHAM bridge run
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceASAP1-2019VPAINPUT.DAT", sep="/"))

input <- prepare_wham_input(asap3, model_name = "model_try_bridge") 
```
Fit bridge model, check convergence, and plot output
```{r}
model_try_bridge <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_try_bridge)
print(paste("Number of parameters", length(model_try_bridge$par), sep=" "))

plot_wham_output(mod=model_try_bridge, out.type='html')
plot_wham_output(mod=model_try_bridge, out.type='png', dir.main = paste(here::here(), "model_try_bridge", sep="/"))

saveRDS(model_try_bridge, file=paste(here::here(), "model_try_bridge", "model_try_bridge.rds", sep="/"))
```

How does this relate to the 2018 VPA? https://apps-nefsc.fisheries.noaa.gov/saw/sasi/uploads/2019_PLA_UNIT_MOD_VPA_T2018_NEC_ONLY.dat


# Bridge run with multi-age indices: Run 2 in WG spreadsheet
The .dat file used for the ASAP bridge run treats each survey age as a separate index so selectivity for each index = 1. The following bridge run aggregates surveys to include multiple ages, and otherwise uses the same data as the ASAP bridge run with the following exception:

- Index 19 from the ASAP bridge .dat file was excluded from the WHAM .dat bridge file, but was not used for fitting either bridge model

Load .dat file adapted from ASAP bridge run to include multi=age survey for WHAM bridge run
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM1-2019VPAINPUT.DAT", sep="/"))

input <- prepare_wham_input(asap3, model_name = "model_bridge") 
```
Fit bridge model, check convergence, and plot output
```{r}
model_bridge <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_bridge)
print(paste("Number of parameters", length(model_bridge$par), sep=" "))

plot_wham_output(mod=model_bridge, out.type='html')
plot_wham_output(mod=model_bridge, out.type='png', dir.main = paste(here::here(), "model_bridge", sep="/"))

saveRDS(model_bridge, file=paste(here::here(), "model_bridge", "model_bridge.rds", sep="/"))
```
