---
title: "Plaice_Baseline_Model_Variations"
output: html_document
---

This document pulls in the most up-to-date data for plaice to develop a baseline model similar to the bridge run (only NEFSC trawl data)

This document updates the bridge run model with most up-to-date data for plaice (downloaded from shared drive 2/3/22) and adjusts model structure to take advantage of state-space modeling features. Subsequent runs vary the data inputs and assumptions of the base case.

All attempted runs are numbered here, key runs with informative outputs are also included in the working group spreadsheet for WHAM runs and may be numbered differently. To find the code below that corresponds with a given spreadsheet run # search for the following string in this document: "Run # in WG spreadsheet"
- WG spreadsheet runs 1 & 2 may be found in "Plaice_Bridge_Run.Rmd" 

# Load R packages
```{r}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

# Load most up-to-date data
- Don't use Age 0 data
- M = 0.3, may also try freely estimating M in WHAM

Major data updates include:
- M set to 0.3
- Fixed maturity schedule over time
- Updated catch, NEFSC survey, and MADMF survey data
- Included VAST survey estimates
- Spring index month set to 4, fall index month set to 10 (bridge run set all to 1)

### Load data available to use in WHAM
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019.DAT", sep="/"))
```

### Data passed to WHAM via PlaiceWHAM-2019.DAT can also be loaded into R via the following:

Catch data
```{r}
# Catch-at-age data (use middle table with 11+ group)
CAA <- read_xlsx(paste(here::here(), "data", "AMP_Tables and Figures_USE THIS.xlsx", sep="/"), sheet = 15, skip = 2, range = "AA3:AN43")
CAA <- drop_columns(CAA, "Age 0") 
# Catch weight-at-age data (use middle table with the following warning: PLUS GROUP 11+ MID-YEAR WEIGHTS (NEED TO ADDRESS THE SHADED CLLS WITH DECREASING WTS)) - equivalent to WAA matrix 1 in bridge data
cWAA <- read_xlsx(paste(here::here(), "data", "AMP_Tables and Figures_USE THIS.xlsx", sep="/"), sheet = 16, range = "AB3:AN43")
cWAA <- drop_columns(cWAA, "Age 0") 
```

Jan1 spawning stock WAA - equivalent to WAA matrix 2&3 in bridge data
```{r}
jan1WAA <- read_xlsx(paste(here::here(), "data", "AMP_Tables and Figures_USE THIS.xlsx", sep="/"), sheet = 17, skip = 2, range = "A3:L43") 
```

VAST indices
```{r}
# Spring
sVAST <- read_xlsx(paste(here::here(), "data", "Plaice_VAST_Indices.xlsx", sep="/"), sheet = 1)

# Fall
fVAST <- read_xlsx(paste(here::here(), "data", "Plaice_VAST_Indices.xlsx", sep="/"), sheet = 2)
fVAST <- drop_columns(fVAST, "Season") # Drop mislabeled column (confirmed with AHansell 2/3/22)

# At some point should replace NA with -999 to be safe
```

Survey indices
```{r}
# Spring & fall indices for: NEFSC, MADMF
indices <- readRDS(paste(here::here(), "data", "Survey Data", "NEFSC and MADMF", "AMPLAsurveyData", "Indices.rds", sep="/"))

# Spring NAA (1st table is NAA, 2nd is proportion at age)
sNAA <- readRDS(paste(here::here(), "data", "Survey Data", "NEFSC and MADMF", "AMPLAsurveyData", "NAASpring.rds", sep="/"))

# Fall NAA
fNAA <- readRDS(paste(here::here(), "data", "Survey Data", "NEFSC and MADMF", "AMPLAsurveyData", "NAAFall.rds", sep="/"))

# MENH survey
```


# Run 1: Use updated data - Run 3 in WG spreadsheet
Check updated data file usable. Run with fit to NEFSC spring and fall surveys, I didn't do anything to selectivity so this is likely to be weird. 

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019.DAT", sep="/"))

input <- prepare_wham_input(asap3, model_name = "model_dataUpdate") 
```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate)
print(paste("Number of parameters", length(model_dataUpdate$par), sep=" "))

plot_wham_output(mod=model_dataUpdate, out.type='html')
# plot_wham_output(mod=model_dataUpdate, out.type='png', dir.main = paste(here::here(), "model_dataUpdate", sep="/"))
saveRDS(model_dataUpdate, file=paste(here::here(), "model_dataUpdate", "model_dataUpdate.rds", sep="/"))
```

Large negative residuals for survey age 1 & 2, large positive residuals for ages 3-5. Selectivity taken from bridge run is unrealistic & needs to be updated.

# Run 1A: Check impact of M change - Run 3A in WG spreadsheet
Fit model to updated data but revert to the natural mortality used in the VPA (0.2) to evaluate the effect of this change (to 0.3 in fully updated data) on SSB/R/F timeseries. 

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019.DAT", sep="/"))

M_input <- list(initial_means = rep(0.2, 11))

input <- prepare_wham_input(asap3, model_name = "model_dataUpdate1A", M = M_input) 
```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate1A <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate1A)
print(paste("Number of parameters", length(model_dataUpdate1A$par), sep=" "))

plot_wham_output(mod=model_dataUpdate1A, out.type='html')
# plot_wham_output(mod=model_dataUpdate1A, out.type='png', dir.main = paste(here::here(), "model_dataUpdate1A", sep="/"))
saveRDS(model_dataUpdate1A, file=paste(here::here(), "model_dataUpdate1A", "model_dataUpdate1A.rds", sep="/"))
```

Intermediate SSB/F/R timeseries estimates when compared to VPA bridge and fully updated models (run 2). 

# Run 1B: Check impact of M & maturity change - no run in WG spreadsheet
Fit model to updated data but revert to the natural mortality used in the VPA (0.2) and old maturity from the VPA bridge to evaluate the effect of this change on SSB/R/F timeseries. 

Prep data for use: no maturity data in final year since using VPA data through 2018
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_VPAMaturity.DAT", sep="/"))

M_input <- list(initial_means = rep(0.2, 11))

input <- prepare_wham_input(asap3, model_name = "model_dataUpdate1B", M = M_input) 
```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate1B <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate1B)
print(paste("Number of parameters", length(model_dataUpdate1B$par), sep=" "))

plot_wham_output(mod=model_dataUpdate1B, out.type='html')
# plot_wham_output(mod=model_dataUpdate1B, out.type='png', dir.main = paste(here::here(), "model_dataUpdate1B", sep="/"))
saveRDS(model_dataUpdate1B, file=paste(here::here(), "model_dataUpdate1B", "model_dataUpdate1B.rds", sep="/"))
```

## Compare the bridge run (revised format) with Run 1A (updated data but old natural mortality assumption)
```{r}
## Compare several
model_list <- paste(here::here(), c("model_bridge/model_bridge.rds",             "model_dataUpdate1B/model_dataUpdate1B.rds", "model_dataUpdate1A/model_dataUpdate1A.rds",  "model_dataUpdate/model_dataUpdate.rds"), sep="/")
models <- lapply(model_list, readRDS)
# models <- list(model_dataUpdate, model_dataUpdate3, model_dataUpdate4, model_dataUpdate5)
names(models) <- c("Bridge", "Updated_oldM-oldMat", "Updated_oldM-newMat", "Updated_newM-Mat")

compare_wham_models(models, do.plot = TRUE, do.table=FALSE, fdir=paste(here::here(), "model_comparison", sep="/"), plot.opts=list(which = 1))

# Model runs 1,3,4 only
compare_wham_models(models[c(1,3,4)], do.plot = TRUE, do.table=FALSE, fdir=paste(here::here(), "model_comparison", sep="/"), plot.opts=list(which = 1))

## Generate tables for all models
compare_wham_models(models[], do.plot = FALSE, do.table=TRUE, fdir=paste(here::here(), "model_comparison", sep="/"))
```

# Run 2: Update selectivity 
Change input file so selectivity is estimated.

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel = lapply(1:use_n_indices, function(x) c(rep(0.5,8),1,1,0))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index 
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
# browser() # Useful debugger 
input <- prepare_wham_input(asap3 = asap3, selectivity = sel_list, model_name = "model_dataUpdate2")


```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate2 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate2)
print(paste("Number of parameters", length(model_dataUpdate2$par), sep=" "))

# plot_wham_output(mod=model_dataUpdate2, out.type='html')
plot_wham_output(mod=model_dataUpdate2, out.type='png', dir.main = paste(here::here(), "model_dataUpdate2", sep="/"))

saveRDS(model_dataUpdate2, file=paste(here::here(), "model_dataUpdate2", "model_dataUpdate2.rds", sep="/"))
```
Much better residual patterns and improved fit to survey indices. May still want to check age 1 & NAA plots - it looks like recruitment might be weird. Missing values (0s) in survey weight-at-age data for older fish could be a problem. Survey age 4 appears to have second highest selectivity with age 10+ estimated at 1. 

Hessian not positive definite. 

# Run 3: Fix age 4 selectivity for indices - Run 4 in WG spreadsheet
Fix age 4 selectivity at 1. For index 1 this matches the freely estimated value, for index 2 age 4 has the second highest selectivity (10+ has highest) when selectivity is freely estimated.

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,0))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix
#fix_index_sel[[1]][1] <- 4 # Fix age for for index 1,  NA means do not fix them
#fix_index_sel[[2]][1] <- 4 # Fix age for for index 2

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
input <- prepare_wham_input(asap3 = asap3, selectivity = sel_list, model_name = "model_dataUpdate3")

```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate3 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate3)
print(paste("Number of parameters", length(model_dataUpdate3$par), sep=" "))

plot_wham_output(mod=model_dataUpdate3, out.type='html')
# plot_wham_output(mod=model_dataUpdate3, out.type='png', dir.main = paste(here::here(), "model_dataUpdate3", sep="/"))

saveRDS(model_dataUpdate3, file=paste(here::here(), "model_dataUpdate3", "model_dataUpdate3.rds", sep="/"))
```
There doesn't appear to be much difference in model fit or diagnostics compared to Run 2 but the hessian for this model is invertable. The selectivity pattern is very similar to Run 2 for index 1 and index 2 has slightly higher selectivity estimates for intermediate ages near age 4. Both indices still have 10+ estimates at 1. 

# Run 4: Add random effect for recruitment - random about mean - Run 5 in WG spreadsheet
Same as run 3 (freely estimate selectivity but fix index age 4) but also add random effect for recruitment that is random about the mean

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") #random about mean
NAA_re$recruit_model = 2 # random effects with a constant mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,0))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index 
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
input <- prepare_wham_input(asap3 = asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "model_dataUpdate4")

```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate4 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate4)
print(paste("Number of parameters", length(model_dataUpdate4$par), sep=" "))

plot_wham_output(mod=model_dataUpdate4, out.type='html')
# plot_wham_output(mod=model_dataUpdate4, out.type='png', dir.main = paste(here::here(), "model_dataUpdate4", sep="/"))

saveRDS(model_dataUpdate4, file=paste(here::here(), "model_dataUpdate4", "model_dataUpdate4.rds", sep="/"))
```

Recruitment residuals look a bit better (distributed about 0 rather than all positive, but very large residuals at end of time series are concerning). OSA residuals for the fleet and both indices look a bit bigger.

# Run 5: Add random effect for recruitment - random walk - Run 6 in WG spreadsheet
Same as run 4 (freely estimate selectivity but fix index age 4) but with add random effect for recruitment with random walk

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") #random effect on recruitment
NAA_re$recruit_model = 1 # random effects with random walk
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,0))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index 
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
input <- prepare_wham_input(asap3 = asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "model_dataUpdate5")

```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate5 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate5)
print(paste("Number of parameters", length(model_dataUpdate5$par), sep=" "))

plot_wham_output(mod=model_dataUpdate5, out.type='html')
# plot_wham_output(mod=model_dataUpdate5, out.type='png', dir.main = paste(here::here(), "model_dataUpdate5", sep="/"))

saveRDS(model_dataUpdate5, file=paste(here::here(), "model_dataUpdate5", "model_dataUpdate5.rds", sep="/"))
```

Recruitment residuals at the end of the timeseries are still fairly large, but are not biased negatively. More closely track recruitment variability. No strong retrospective patterns. Selectivity for age 10+ is still much higher than ages 5-9.

# Run 6: Add random effect for recruitment - AR1 - Run 7 in WG spreadsheet
Same as run 4 (freely estimate selectivity but fix index age 4) but with add random effect for recruitment with random walk

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# AR1 random effects for recruitment only 
NAA_re = list(sigma = "rec", # random effect on recruitment
              cor = "ar1_y") # AR1 correlated by year
NAA_re$recruit_model = 1 # random effects with random walk
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,0))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index 
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
input <- prepare_wham_input(asap3 = asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "model_dataUpdate6")

```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate6 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate6)
print(paste("Number of parameters", length(model_dataUpdate6$par), sep=" "))

plot_wham_output(mod=model_dataUpdate6, out.type='html')
# plot_wham_output(mod=model_dataUpdate6, out.type='png', dir.main = paste(here::here(), "model_dataUpdate6", sep="/"))

saveRDS(model_dataUpdate6, file=paste(here::here(), "model_dataUpdate6", "model_dataUpdate6.rds", sep="/"))
```
## Compare run 5 and 6
Compare the bridge run (revised format) with Run 1A (updated data but old natural mortality assumption)
```{r}
## Compare run 5 and 6
model_list <- paste(here::here(), c("model_dataUpdate5/model_dataUpdate5.rds", "model_dataUpdate6/model_dataUpdate6.rds"), sep="/")
models <- lapply(model_list, readRDS)
names(models) <- c("Run5", "Run6")

compare_wham_models(models, do.plot = TRUE, do.table=FALSE)

# Calculate AIC & other diagnostic tables for run 5 & 6
compare_wham_models(c(list(model_dataUpdate5), list(model_dataUpdate6)), do.plot = FALSE, do.table=TRUE)
```
Very little difference in expected outcomes between runs 5 & 6, slight difference in recruitment in last 5 years of timeseries (not surprising since large residuals observed at end of timeseries in previous runs). Since run 6 adds a parameter, recommend sticking with run 5

# In progress beyond this point

# Run 7: Add MADMF surveys 
Run 5 model with NEFSC + MADMF spring and fall surveys

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# Select MADMF spring and fall surveys (indices 3 + 4) for use in addition to NEFSC
asap3$dat$use_index <- c(1,1,1,1,0,0,0,0,0,0,0,0)

# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") #random about mean
NAA_re$recruit_model = 1 # random effects with random walk
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Turn off age comp for MADMF spring and fall survey (since not provided)
asap$dat$use_index_acomp <- c(1,1,0,0)

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,0))
init_index_sel[[3]] <- c(rep(1, 11)) # initial values for all ages = 1
init_index_sel[[4]] <- c(rep(1, 11)) # initial values for all ages = 1

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for NEFSC indices,  NA means do not fix
fix_index_sel[[3]] <- c(1:11) # Fix selectivity for MADMF spring & fall
fix_index_sel[[4]] <- c(1:11)

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index 
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
input <- prepare_wham_input(asap3 = asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "model_dataUpdate7")

```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate7 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate7)
print(paste("Number of parameters", length(model_dataUpdate7$par), sep=" "))

plot_wham_output(mod=model_dataUpdate7, out.type='html')
# plot_wham_output(mod=model_dataUpdate7, out.type='png', dir.main = paste(here::here(), "model_dataUpdate7", sep="/"))

saveRDS(model_dataUpdate7, file=paste(here::here(), "model_dataUpdate7", "model_dataUpdate7.rds", sep="/"))
```
Both the spring and fall MADMF survey indices (3 and 4) have very large negative residuals towards the end of the time series and somewhat smaller but still large residuals early in the time series. Introduces residual pattern for NEFSC indices (1 and 2), residuals move from large negative residuals early in the time series to large positive residuals at the end of the time series. 



# Use VAST data instead
# Only NEFSC VAST index

# Run 8: Fit to VAST NEFSC spring and fall surveys
Fit to VAST estimated NEFSC indices (i.e. model-based index) rather than observation-based NEFSC indices

Prep data for use
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_selectivity.DAT", sep="/"))

# Select VAST estimated NEFSC spring and fall surveys (indices 5 and 6) 
asap3$dat$use_index <- c(0,0,0,0,1,1,0,0,0,0,0,0)

# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") #random about mean
NAA_re$recruit_model = 1 # random effects with random walk
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Turn off age comp for spring and fall survey (since not estimated)
asap$dat$use_index_acomp <- c(0,0)

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) rep(1, 11)) # initial values for all ages = 1

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) 1:11) # Fix all ages for VAST NEFSC indices,  NA means do not fix

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

##### Prep WHAM input
input <- prepare_wham_input(asap3 = asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "model_dataUpdate8")

```
Run model with raw updated data, check convergence, and plot output
```{r}
model_dataUpdate8 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(model_dataUpdate8)
print(paste("Number of parameters", length(model_dataUpdate8$par), sep=" "))

plot_wham_output(mod=model_dataUpdate8, out.type='html')
# plot_wham_output(mod=model_dataUpdate8, out.type='png', dir.main = paste(here::here(), "model_dataUpdate8", sep="/"))

saveRDS(model_dataUpdate8, file=paste(here::here(), "model_dataUpdate8", "model_dataUpdate8.rds", sep="/"))
```

Higher recruitment CV than observation-based model. Very large residuals for both spring and fall indices, spring index (1) more positive than negative residuals except end of timeseries. Fleet OSA residuals also less normally distributed.


# NEFSC VAST + MADMF VAST
# NEFSC VAST + MENH VAST
# NEFSC VAST + MADMF VAST + MENH VAST
# ALL VAST



Notes - not all plots (e.g. plot.cv) will be generated if not positive definite hessian (no sdreport)

# Compare model F, SSB, Recruitment
```{r}
## Compare all models
model_list <- paste(here::here(), c("model_bridge/model_bridge.rds", "model_dataUpdate/model_dataUpdate.rds", "model_dataUpdate3/model_dataUpdate3.rds", "model_dataUpdate4/model_dataUpdate4.rds", "model_dataUpdate5/model_dataUpdate5.rds"), sep="/")
models <- lapply(model_list, readRDS)
# models <- list(model_dataUpdate, model_dataUpdate3, model_dataUpdate4, model_dataUpdate5)
names(models) <- c("Bridge", "Updated", "Fix_Age4", "R_mean", "R_walk")

compare_wham_models(models, do.plot = TRUE, do.table=FALSE, fdir=paste(here::here(), "model_comparison", sep="/"), plot.opts=list(which = 1))

## Generate tables for all models
compare_wham_models(models, do.plot = FALSE, do.table=TRUE, fdir=paste(here::here(), "model_comparison", sep="/"), plot.opts=list(which = 1))

expandModels <- c(models, list(readRDS(paste(here::here(), "model_try_bridge/model_try_bridge.rds", sep="/"))))
names(expandModels) <- c("Bridge", "Updated", "Fix_Age4", "R_mean", "R_walk", "try_bridge")
compare_wham_models(expandModels, do.plot = FALSE, do.table=TRUE, fdir=paste(here::here(), "model_comparison", sep="/"), plot.opts=list(which = 1))

## Only plot the first 2 models
compare_wham_models(models[1:2], do.plot = TRUE, do.table=FALSE, fdir=paste(here::here(), "model_comparison", sep="/"), plot.opts=list(which = 1))
```



