---
title: "WHAM_Run29A_splitNEFSC-BigUnits"
output: html_document
date: '2022-04-04'
---

## Model description
Full state-space model as in run 29 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, iid selectivity random effect for fleet and index 1, Albatross spring, recruitment that is random about the mean), with NEFSC bottom trawl surveys split into Albatross (1980-2008, indices 1 and 3 for spring/fall) and Bigelow (2009-2019, indices 2 and 4 for spring/fall) time series, but NEFSC data is in Albatross AND Bigelow units, rather than using only Albatross units as in run 29. The aggregate index for this run was also in biomass units rather than abundance. 

An initial run was conducted to freely estimate selectivity-at-age for the fleet and all indices with selectivity random effects for all indices implemented (see comment on line 44 for details and WHAM_Run29_input_FreeSelEstimate.rds for data used in this run). Although this run did not converge, it suggested that ages 4-5 for Albatross spring (index 1), age 5 for Bigelow spring (index 2), age 4 for Albatross spring (index 3), and ages 4-5 for Bigelow fall (index 4) were fully selected so selectivity was fixed at 1 for these ages in the converged run below, and only Albatross spring had variable selectivity so a random effect was only included for this index in the full run below. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

# Tried running with the following 4 lines commented to freely estimate all survey selectivities-at-age and no survey selectivity random effect (line 52 uncommented, line 51 commented) 
fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks),  "iid", rep("none", 3)) # Don't include selectivity random effects for surveys except for Albatross spring, use to freely estimate selectivity for fleets
# randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks),  rep("iid", use_n_indices)) # Don't include selectivity random effects for surveys, use to freely estimate selectivity for fleets

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29A_splitNEFSC-BigUnits", "WHAM_Run29_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# WHAM_Run29 <- fit_wham(input, do.osa=F,do.retro=F) 
# check_convergence(WHAM_Run29)
# WHAM_Run29$parList$sel_repars #variance of selectivity random effects -> 0 for (last 3) surveys except first (Albatross Spring?) 
# # I suspect that the increased flexibility in the random effects for numbers at age negates the need for selectivity RE for these surveys. So, perhaps try removing the selectivity re for at least the last 3 surveys.
# print(paste("Number of parameters", length(WHAM_Run29$par), sep=" "))

# Run with OSA residuals
WHAM_Run29 <- fit_wham(input, MakeADFun.silent = TRUE, do.retro = FALSE, do.osa=FALSE) 
WHAM_Run29 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE) 
check_convergence(WHAM_Run29)
print(paste("Number of parameters", length(WHAM_Run29$par), sep=" "))

plot_wham_output(mod=WHAM_Run29, out.type='html')
# plot_wham_output(mod=WHAM_Run29, out.type='png', dir.main = paste(here::here(), "WHAM_Run29", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29A_splitNEFSC-BigUnits", "WHAM_Run29_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29A_splitNEFSC-BigUnits/WHAM_Run29_input.rds", sep="/"))

# Rerun data
ReRun29 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Index 4 (Bigelow fall) selectivity was more dome-shaped for this run (there was no increase from age 10 to 11+ as in run 29), while this pattern still evident in index 3 (Albatross fall). Index also has slightly higher selectivity estimates for age 8 compared to ages 7 and 9. 

Catchability estimates for index 2 (Bigelow spring), 3 (Albatross fall), and 4 (Bigelow fall) were more similar in run 29A than in 29 where the Albatross estimates were higher than for the Bigelow indices. Catchability for run 29A index 1 (Albatross spring) was lower than for other indices. 

Catch residuals were larger in magnitude but had less of a pattern early in the time series. Residuals for indices had larger extremes but generally followed the same pattern. 

Fleet and index age comp residuals (observed-predicted) were smaller than for run 29, although the catch age comp residuals were not plotted from 2009-2019? 

