---
title: "WHAM_Run16_FixSelectivity-at-age_2SelBlock"
output: html_document
date: '2022-02-28'
---

## Model description
This run is the same as run 13 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity), but includes two selectivity blocks, one from 1980-1999 and another from 2000-2019.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_2SelBlock.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
use_n_selBlocks = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4), c(2,0.4)) # logistic parameters for each selectivity block, based on model type

init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:(asap3$dat$n_fleets*use_n_selBlocks), function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run16") 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run16 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run16)
print(paste("Number of parameters", length(WHAM_Run16$par), sep=" "))

plot_wham_output(mod=WHAM_Run16, out.type='html')
# plot_wham_output(mod=WHAM_Run16, out.type='png', dir.main = paste(here::here(), "WHAM_Run16", sep="/"))
```

### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run16_FixSelectivity-at-age_2SelBlock", "WHAM_Run16_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run16, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run16_FixSelectivity-at-age_2SelBlock", "WHAM_Run16_model.rds", sep="/"))
```

## Comment
Still several years with large residuals especially at ages 1-3 for the fleet & both surveys. Catch residuals have a consistent pattern of negative at the beginning and end of the timeseries and positive residuals in the middle. Recruitment residuals are all positive - this is a plotting artifact and the NAA_4panel_1.png plot for runs that treat R as a fixed effect (as is done here) is not an informative diagnostic. There is also a slight retrospective pattern, but this falls within in the middle of the range observed across runs. The fleet and index age comp likelihood contribution is a bit smaller than for run 13.

