---
title: "WHAM_Run42B_addEnvCov-R-NAO-withEffect-2Lag"
output: html_document
date: '2022-05-02'
---

## Model description
Model specified as in run 29B with 2 major differences, 1) both age 4 and 5 were fixed at full selectivity for all indices (impacts Bigelow spring and Albatross fall) and 2) incorporates this environmental effect on recruitment. The North Atlantic Oscillation (NAO) Annual was the environmental covariate considered here, with a 1 year lag (bottom temperature in year t impacts recruitment in year t+1) and a random walk process model.


### Environmental covariate description
Jamie Behan sourced the North Atlantic Oscillation (NAO) data from the National Oceanic and Atmospheric Administration (NOAA) National Centers for Environmental Information and can be accessed from https://www.ncdc.noaa.gov/teleconnections/nao/. These data are monthly anomalies of the surface sea level pressure difference (hPa) calculated from the 1950-2000 climatological daily mean and standard deviation base period.”

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load environmental data 
NAO <- read.csv(paste(here::here(), "data", "NAO_se.csv", sep="/"))
# Add placeholder for missing years of data
NAO <- rbind(c(1981, -999, -999, -999, -999), NAO) # 1981
NAO <- rbind(c(1980, -999, -999, -999, -999), NAO) # 1980
NAO <- rbind(c(1979, -999, -999, -999, -999), NAO) # 1979
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "NAO",
    mean = as.matrix(NAO$mean),
    logsigma = as.matrix(NAO$se),
    year = as.numeric(NAO$Year),
    use_obs = matrix(c(FALSE, FALSE, FALSE, rep(TRUE, nrow(NAO)-3)), ncol = 1, nrow=nrow(NAO)), # use all obs except the first 3 (no data 1979, 1980, 1981 not full year of data in 1981) 
    lag = 2, # NAO anomaly in year t impact R in year t+1
    #process_model = "ar1",
    process_model = "rw",
    where = "recruit", # "recruit" for recruitment effect
    how = 1 # 1 for controlling = density-independent mortality
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(4,5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4,5) # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run42B") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run42B_addEnvCov-R-NAO-withEffect-2Lag", "WHAM_Run42B_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run42B <- fit_wham(input, do.osa = TRUE, do.retro = TRUE) 
check_convergence(WHAM_Run42B)
print(paste("Number of parameters", length(WHAM_Run42B$par), sep=" "))

plot_wham_output(mod=WHAM_Run42B, out.type='html')
# plot_wham_output(mod=WHAM_Run42B, out.type='png', dir.main = paste(here::here(), "WHAM_Run42B", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run42B, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run42B_addEnvCov-R-NAO-withEffect-2Lag", "WHAM_Run42B_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run42B_addEnvCov-R-NAO-withEffect-2Lag-2Lag/WHAM_Run42B_input.rds", sep="/"))

# Rerun data
ReRun42B <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment

OSA age comp residual patterns and distributions were similar for run 42 and 42B and the same was true for OSA residuals for fit to aggregate fleet and index data. 

OSA residuals for fit to the NAO time series were not very normally distributed.

AIC was larger but still within 2 of the AIC score for run 42 and was identical to the score for Run 42A so this run should be considered equivalent. 
