---
title: "WHAM_Run28_Extended-Catch1960"
output: html_document
date: '2022-03-18'
---

## Model description
Recruitment random effects as in Run25 (the full state space model returned an error when tried) including iid selectivity random effects, but catch time series was extended back to 1960 to take full advantage of available fleet data. ASAP file was expanded to include longer catch time series as in ASAP run 14 and several additional years of NEFSC spring and fall survey data. Discard total CV and effective sample size set to 0 for 1960-1979, Recruitment CV was also set very small for the first 10 years (1960-1970) of the time series. 

Earlier iterations of this model tried:

- full state space model as in Run27 - returned error: NA/NaN gradient evaluation

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_1960.DAT", sep="/"))
```

### Prepare model input
```{r}
# iid random effects for recruitment only
NAA_re = list(sigma = "rec") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 

fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Setup index object,  NA means do not fix 
fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), "iid", "iid") 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, recruit_model = recruit_model, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run28") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run28_Extended-Catch1960", "WHAM_Run28_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run28 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run28)
print(paste("Number of parameters", length(WHAM_Run28$par), sep=" "))

plot_wham_output(mod=WHAM_Run28, out.type='html')
# plot_wham_output(mod=WHAM_Run28, out.type='png', dir.main = paste(here::here(), "WHAM_Run28", sep="/"))
```

```{r}
# debug NA/NaN
WHAM_Run28 <- fit_wham(input, do.fit=F)
therep = WHAM_Run28$report()
names(therep)
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run28, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run28_Extended-Catch1960", "WHAM_Run28_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run28_Extended-Catch1960/WHAM_Run28_input.rds", sep="/"))

# Rerun data
ReRun28 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Fleet catch residuals were mostly positive prior to 1980 with a larger proportion of 11+ fish for years when no age composition data was available. Both indices had mostly positive residuals prior to 1980.  Fleet and index age composition residuals were similar between Run28 and Run25. Likelihood contributions were also similar between these two runs with higher contributions for fleet catch and NAA in Run28. OSA residuals for the fleet and index 2 (NEFSC fall) were less normally distributed than in Run25 while index 1 was similar across these runs. Run28 trends in SSB, Fbar, and R were similar in years where both models had data, while CVs for SSB and F were high early in the timeseries and were much smaller from 1980 on, while R CV peaked in the late 1960s-early 1970s before returning to smaller values. F40% was similar between Run25 and Run28, but Run28 had much higher expectations for SSB and Yield at F40%, and higher CI with the expectations from Run25 falling near the lower CI for Run28. Run28 had smaller Mohn's rho values for SSB, Fbar, and R than Run25.

