---
title: "Compare_ASAP_Run46B"
output: html_document
date: '2022-04-11'
---

## Model description
Re-run ASAP run 46B in WHAM without random effects so comparative diagnostic plots can be easily generated between ASAP and WHAM runs.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data used in ASAP run
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "Run46B.DAT", sep="/"))
```

### Prepare model input
```{r}
input <- prepare_wham_input(asap3, model_name = "Compare_ASAP_Run46B") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "Compare_ASAP_Run46B", "Compare_ASAP_Run46B_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
Compare_ASAP_Run46B <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE) 
check_convergence(Compare_ASAP_Run46B)
print(paste("Number of parameters", length(Compare_ASAP_Run46B$par), sep=" "))

# plot_wham_output(mod=Compare_ASAP_Run46B, out.type='html')
```

### Save output
```{r}
# Save fitted model
saveRDS(Compare_ASAP_Run46B, file=paste(here::here(), "WG_Revised_Runs", "Compare_ASAP_Run46B", "Compare_ASAP_Run46B_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "Compare_ASAP_Run46B/Compare_ASAP_Run46B_input.rds", sep="/"))

# Rerun data
ReRun_Compare_ASAP_Run46B <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment


