---
title: "WHAM_Run31_addMENH"
output: html_document
date: '2022-03-18'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with additional MENH spring and fall indices (index 3 and 4 respectively).

MENH spring data was pulled from AMP_MENH_Spring_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

MENH fall data was pulled from AMP_MENH_Fall_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MENH indices
asap3$dat$use_index_acomp[13:14] <- 1 # use index age comp
asap3$dat$use_index[13:14] <- 1 # use indices 13-14 (MENH)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1), # MENH spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1)) # MENH fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for index 1 NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for index 2 NEFSC fall
fix_index_sel[[3]][1] <- 2 # Fix age 2 for index 3 MENH spring
fix_index_sel[[4]][1] <- 1 # Fix age 1 for index 4 MENH fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run31") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run31_addMENH", "WHAM_Run31_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run31 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run31)
print(paste("Number of parameters", length(WHAM_Run31$par), sep=" "))

plot_wham_output(mod=WHAM_Run31, out.type='html')
# plot_wham_output(mod=WHAM_Run31, out.type='png', dir.main = paste(here::here(), "WHAM_Run31", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run31, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run31_addMENH", "WHAM_Run31_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run31_addMENH/WHAM_Run31_input.rds", sep="/"))

# Rerun data
ReRun31 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Without fixed selectivity at 1 for MENH indices model converges but doesn't have invertible hessian, based on results try fixing at 1 for ages 1 (looks like age 2-3 for spring MENH may also be high). Fixing age 1 at full selectivity converged but did not have an invertible hessian  (spring estimates age 2 at full selectivity, fall doesn't but has high selectivity so going to try fixing full selectivity for age 2 - still not invertible hessian). Try fixing full selectivity for age 2 in spring and age 1 in fall, only recruitment random effect, weird spike in selectivity for age 10 fish in both seasons, change age 10 and 11+ starting parameters to 0.1. - this option converged and had an invertible hessian. 

