---
title: "WHAM_Run31_addMENH"
output: html_document
date: '2022-04-04'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with additional MENH spring and fall indices (index 3 and 4 respectively).

MENH spring data was pulled from AMP_MENH_Spring_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

MENH fall data was pulled from AMP_MENH_Fall_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MENH indices
asap3$dat$use_index_acomp[13:14] <- 1 # use index age comp
asap3$dat$use_index[13:14] <- 1 # use indices 13-14 (MENH)
```

### Prepare model input
```{r}
# iid random effects 
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1), # MENH spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1)) # MENH fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for index 1 NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for index 2 NEFSC fall
fix_index_sel[[3]][1] <- 2 # Fix age 2 for index 3 MENH spring
fix_index_sel[[4]][1] <- 1 # Fix age 1 for index 4 MENH fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run31") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run31_addMENH", "WHAM_Run31_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run31 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run31)
print(paste("Number of parameters", length(WHAM_Run31$par), sep=" "))

plot_wham_output(mod=WHAM_Run31, out.type='html')
# plot_wham_output(mod=WHAM_Run31, out.type='png', dir.main = paste(here::here(), "WHAM_Run31", sep="/"))
beep()
beep()
beep()
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run31, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run31_addMENH", "WHAM_Run31_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run31_addMENH/WHAM_Run31_input.rds", sep="/"))

# Rerun data
ReRun31 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Fixing full selectivity for MENH age 2 in spring and age 1 in fall, and changing starting selectivity estimates for age 10 and 11+ to 0.1 resulted in a model that converged with an invertible hessian. 

Fleet residuals follow similar patterns in runs 27 and 31. Residuals or index 1 and 2 were similar across runs 27 and 31, index 3 and 4 had more negative residuals towards the end of the time series. Fleet OSA residuals are similar in both runs but the maximum residual is slighlty smaller for run 31. Index 1 and 2 (NEFSC spring and fall) have larger residuals in run 31 (also seen in observed-predicted residuals), particularly for ages 1-3 but were more evenly positive and negative while age 1 in run 27 index 1 had largely negative residuals and index 2 for this run had largely positive residuals.

Fleet and index 1 and 2 age comp likelihood contributions were larger in run 31 than 27. The distribution of OSA residuals were similar for the fleet and indices 1 and 2 across runs, this includes age comp OSA residual distributions.

CV around recruitment estimates was higher early in the time series and lower towards the end of the time series, opposite the pattern observed in run 27. More variability in index 2 (NEFSC fall) was estimated in run 31 than 27,  particularly for ages 1-3. Selectivity for index 3 and 4 (MENH spring and fall) increased for age 10 over that estimated for age 9 and 11+. 

