---
title: "WHAM_Run37B_VAST_ALL-split"
output: html_document
date: '2022-04-18'
---

## Model description
A full state-space model was implemented as in run 37A (logistic fleet selectivity, age-specific index selectivity, recruitment about the mean, fit to VAST index that combines all observed indices, selectivity iid random effect for all indices), but indices (in Albatross units) were split into Albatross (1980-2008) and Bigelow years (2009-2019). 

VAST numbers at age 1-9+ were taken from:
SPRING
- VAST Spatiotemporal survey index -> Age Runs -> Spring -> NumbersAtAgeSpring.csv
FALL
- VAST Spatiotemporal survey index -> Age Runs -> Fall -> NumbersAtAgeFall.csv

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateVASTIndices-split.DAT", sep="/"))

# Overwrite settings to stop using design-based NEFSC indices
asap3$dat$use_index_acomp[1:2] <- 0 # don't use index age comp
asap3$dat$use_index[1:2] <- 0 # don't use design-based NEFSC spring and fall indices

# Overwrite to use VAST indices that integrates all available surveys (except LPUE index)
asap3$dat$use_index_acomp[11:14] <- 1 # use index age comp
asap3$dat$use_index[11:14] <- 1 # Use VAST model-based spring and fall indices split into Albatross/Bigelow spring (11&12) and fall (13&14)
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST Albatross spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST Bigelow spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST Albatross fall
                       c(1, 05, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0)) # all VAST Bigelow fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Setup storage object to populate 

fix_index_sel[[1]] <- c(2) # Fix age 3 & 4 for for index 1 all VAST Albatross spring
fix_index_sel[[2]] <- c(2,3) # VAST Bigelow spring
fix_index_sel[[3]] <- c(1) # Fix age 5 for for index 2 all VAST Albatross fall
fix_index_sel[[4]] <- c(1) # VAST Bigelow fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), "iid", rep("none", 3))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run37B") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37B_VAST_ALL-split", "WHAM_Run37B_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run37B <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE) 
check_convergence(WHAM_Run37B)
print(paste("Number of parameters", length(WHAM_Run37B$par), sep=" "))

plot_wham_output(mod=WHAM_Run37B, out.type='html')
# plot_wham_output(mod=WHAM_Run37B, out.type='png', dir.main = paste(here::here(), "WHAM_Run37B", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run37B, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37B_VAST_ALL-split", "WHAM_Run37B_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run37B_VAST_ALL-split/WHAM_Run37B_input.rds", sep="/"))

# Rerun data
ReRun37B <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Hessian not invertible when run with freely estimated selectivity for all indices, or when selectivity random effects implemented for all indices. A model did converge when a selectivity random effect was only implemented for the Albatross spring index. 

The selectivity for the Albatross spring index was still not particularly variable in the converged run so run 37C explored excluding the selectivity random effects for all indices. Run 37B and 37C were equivalent according to AIC, but run 37C was more parsimonious and had the slightly smaller AIC value so run 37C is slightly preferred.
