---
title: "WHAM_Run25_RRandEffect-randMean"
output: html_document
date: '2022-03-03'
---

## Model description
This run is similar to run 23 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity), but also includes a random effect on recruitment that is random about the mean.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") 
NAA_re$recruit_model = 2 # random effects with a constant mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run25") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run25_RRandEffect-randMean", "WHAM_Run25_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run25 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run25)
print(paste("Number of parameters", length(WHAM_Run25$par), sep=" "))

plot_wham_output(mod=WHAM_Run25, out.type='html')
# plot_wham_output(mod=WHAM_Run25, out.type='png', dir.main = paste(here::here(), "WHAM_Run25", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run25, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run25_RRandEffect-randMean", "WHAM_Run25_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run25_RRandEffect-randMean/WHAM_Run25_input.rds", sep="/"))

# Rerun data
Rerun25 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Recruitment CV at the end of the timeseries is smaller than in run 23. Catch and index age comp residuals are very similar to run 23. Recruitment residuals at the end of the timeseries are large and negative. Fleet OSA residuals appear more normally distributed, but OSA residuals for both indices appear about as normally distributed as run 23.

