---
title: "WHAM_Run37C_VAST_ALL-split-noRand"
output: html_document
date: '2022-04-18'
---

## Model description
A full state-space model was implemented as in run 37B (logistic fleet selectivity, age-specific index selectivity, recruitment about the mean, fit to VAST index that combines all observed indices, selectivity iid random effect for the fleet, split Albatross/Bigelow indices), but the selectivity random effect for the spring Albatross index was removed since the variability in this selectivity was small. 

VAST numbers at age 1-9+ were taken from:
SPRING
- VAST Spatiotemporal survey index -> Age Runs -> Spring -> NumbersAtAgeSpring.csv
FALL
- VAST Spatiotemporal survey index -> Age Runs -> Fall -> NumbersAtAgeFall.csv

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateVASTIndices-split.DAT", sep="/"))

# Overwrite settings to stop using design-based NEFSC indices
asap3$dat$use_index_acomp[1:2] <- 0 # don't use index age comp
asap3$dat$use_index[1:2] <- 0 # don't use design-based NEFSC spring and fall indices

# Overwrite to use VAST indices that integrates all available surveys (except LPUE index)
asap3$dat$use_index_acomp[11:14] <- 1 # use index age comp
asap3$dat$use_index[11:14] <- 1 # Use VAST model-based spring and fall indices split into Albatross/Bigelow spring (11&12) and fall (13&14)
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST Albatross spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST Bigelow spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0), # all VAST Albatross fall
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0, 0)) # all VAST Bigelow fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Setup storage object to populate 

fix_index_sel[[1]] <- c(2) # Fix age 3 & 4 for for index 1 all VAST Albatross spring
fix_index_sel[[2]] <- c(2,3) # VAST Bigelow spring
fix_index_sel[[3]] <- c(1) # Fix age 5 for for index 2 all VAST Albatross fall
fix_index_sel[[4]] <- c(1) # VAST Bigelow fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run37C") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37C_VAST_ALL-split-noRand", "WHAM_Run37C_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run37C <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE) 
check_convergence(WHAM_Run37C)
print(paste("Number of parameters", length(WHAM_Run37C$par), sep=" "))

plot_wham_output(mod=WHAM_Run37C, out.type='html')
# plot_wham_output(mod=WHAM_Run37C, out.type='png', dir.main = paste(here::here(), "WHAM_Run37C", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run37C, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37C_VAST_ALL-split-noRand", "WHAM_Run37C_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run37C_VAST_ALL-split-noRand/WHAM_Run37C_input.rds", sep="/"))

# Rerun data
ReRun37C <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Compare via AIC: run 37B and 37C have AIC values within 2 of each other so these models should be considered equivalent, but run 37C has a slightly smaller AIC value, smaller Mohn's rho values and is more parsimonious and is therefore slightly preferred.
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run37B_VAST_ALL-split/WHAM_Run37B_model.rds",
                     "WHAM_Run37C_VAST_ALL-split-noRand/WHAM_Run37C_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c("37B", "37C"), sep="")

# Generate comparative diagnostics
compare_wham_models(models, do.plot = FALSE, do.table=TRUE, fdir=paste(here::here(), "WG_Revised_Runs", "Comparison_Output", sep="/"))
```
