---
title: "WHAM_Run39A_addEnvCov-anomSST-withEffect"
output: html_document
date: '2022-04-28'
---

## Model description
Model specified identically to run 39 but incorporates the environmental effect on recruitment. Annual sea surface temperature anomaly was the environmental covariate considered here, with a 1 year lag (bottom temperature in year t impacts recruitment in year t+1) and a random walk process model.

### Environmental covariate description
Raw sea surface temperature data used in the calculation of anomalies are available via the following:

NOAA_ERSST_V5 data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at https://psl.noaa.gov/data/gridded/data.noaa.ersst.v5.html.

NOAA High Resolution SST data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at https://psl.noaa.gov/data/gridded/data.noaa.oisst.v2.highres.html.

Calculated sea surface temperature anomalies were provided by Adam Kemberling, GMRI (https://adamkemberling.github.io/oisst_mainstays/R/markdown_reports/GOM_Annual_Report.html). For use in this analysis, these anomalies were averaged for all survey strata in the Gulf of Maine (including 3 small strata in the NE that fall within Canadian waters and were exculded from other plaice stock assessment datasets) and Georges Bank to generate an annual anomaly and standard error for all years where data was availble for the entire year (1982-2019). 


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load environmental data and add 3 years (1979-1981) of placeholder data that will not be used in model fitting (1st 2 years of data + 1979 since 1 year lag)
anomSST <- read.csv(paste(here::here(), "data", "GOM_BG_mean_anom_se.csv", sep="/"))
anomSST <- rbind(c(1981, -999, -999, -999, -999), anomSST)
anomSST <- rbind(c(1980, -999, -999, -999, -999), anomSST)
anomSST <- rbind(c(1979, -999, -999, -999, -999), anomSST)
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "SST_anomaly",
    mean = as.matrix(anomSST$mean),
    logsigma = as.matrix(anomSST$se),
    year = as.numeric(anomSST$Year),
    use_obs = matrix(c(FALSE, FALSE, FALSE, rep(TRUE, nrow(anomSST)-3)), ncol = 1, nrow=nrow(anomSST)), # use all obs except the first 2 (no data 1979 and 1980, not full year of data in 1981) 
    lag = 1, # SST anomaly in year t impact R in year t+1
    #process_model = "ar1",
    process_model = "rw",
    where = "recruit", # "recruit" for recruitment effect
    how = 1 # 1 for controlling = density-independent mortality
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run39A") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run39A_addEnvCov-anomSST-withEffect", "WHAM_Run39A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run39A <- fit_wham(input, do.osa = TRUE, do.retro = TRUE) 
check_convergence(WHAM_Run39A)
print(paste("Number of parameters", length(WHAM_Run39A$par), sep=" "))

plot_wham_output(mod=WHAM_Run39A, out.type='html')
# plot_wham_output(mod=WHAM_Run39A, out.type='png', dir.main = paste(here::here(), "WHAM_Run39A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run39A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run39A_addEnvCov-anomSST-withEffect", "WHAM_Run39A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run39A_addEnvCov-anomSST-withEffect/WHAM_Run39A_input.rds", sep="/"))

# Rerun data
ReRun39A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Recruitment and SSB slightly lower at end of time series compared to run 39 which fits to SST anomaly data but does not include an effect on Recruitment. CVs around estimates of F, R, and SSB are slightly higher at the end of the time series. This has consequences for SSB at F40% and Yield at F40% reference points which are slightly lower than run 39. 

There are slightly differences between the catchability estimates between run 39 and 39A but selectivity estimates are similar across these runs.

Fleet and index OSA residuals for fit to aggregate data and age comp OSA residuals are similar across both run 39 and 39A. OSA residuals for fit to the SST anomaly data are somewhat normally distributed in both runs. 

Mohn's rho values, including those for Recruitment are smaller for run 39 than 39A.

Collectively, it does not appear that a SST anomaly effect on R with a 1 year lag improves model fit or diagnostics. 

