---
title: "WHAM_Run38_addEnvCov-BT-noEffect"
output: html_document
date: '2022-04-28'
---

## Model description
Model specified as in run 29B but is fit with an environmental covariate that has no effect so it can be directly compared to run 38A that incorporates this environmental effect on recruitment. Mean annual bottom temperature was the environmental covariate considered here, with a 1 year lag (bottom temperature in year t impacts recruitment in year t+1) and a random walk process model.

When the calculated standard error for the annual bottom temperature measurements were used (some of which were very small) this prevented the OSA resiudals for Ecov_obs from being generated so instead a standard error of 0.01 was used in all years (see line 41-42). 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load and filter environmental data to match year range of other model data
annualBT <- read.csv(paste(here::here(), "data", "year_bt_stdmean.csv", sep="/"))
names(annualBT)[1] = "Year"
annualBT <- filter(annualBT, as.numeric(Year) > 1978) # Filter to match timeframe of other data + 1 year before other data (here 1979) to allow for 1 year lag
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "BT_FVCOM",
    mean = as.matrix(annualBT$mean_bt),
    # logsigma = as.matrix(log(annualBT$standard_err_bt)), #Overly small standard errors prevented OSA residuals for the environmental covariate from being generated
    logsigma = as.matrix(rep(log(0.01), length(annualBT$mean_bt))),
    year = as.numeric(annualBT$Year),
    use_obs = matrix(T, ncol = 1, nrow=nrow(annualBT)), # use all obs = T
    lag = 1, # BT in year t impact R in year t+1
    #process_model = "ar1",
    process_model = "rw",
    where = "none", # "recruit" for recruitment effect
    how = 0 # 1 for controlling = density-independent mortality
    # where = "recruit",
    # how = 1
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run38") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run38_addEnvCov-BT-noEffect", "WHAM_Run38_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run38 <- fit_wham(input, do.osa = TRUE, do.retro = TRUE) 
check_convergence(WHAM_Run38)
print(paste("Number of parameters", length(WHAM_Run38$par), sep=" "))

plot_wham_output(mod=WHAM_Run38, out.type='html')
# plot_wham_output(mod=WHAM_Run38, out.type='png', dir.main = paste(here::here(), "WHAM_Run38", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run38, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run38_addEnvCov-BT-noEffect", "WHAM_Run38_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run38_addEnvCov-BT-noEffect/WHAM_Run38_input.rds", sep="/"))

# Rerun data
ReRun38 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment


