---
title: "WHAM_Run27A_Full-State-Space_biomassUnit"
output: html_document
date: '2022-04-12'
---

## Model description
This run is identical to run 27 (full state-space model for all NAA, revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), but is fit to NEFSC aggregate indices in biomass units rather than abundance (age composition data still in numbers). Run is comparable to run 29C via AIC. An iid random effect for selectivity, was included only for the fleet and index 1 (NEFSC spring).

An initial run was conducted to freely estimate selectivity-at-age for the fleet and with a selectivity random effect implemented for all indices (see comments on lines 47 and 52 for details). Although this run did not converge, it suggested that ages 5 for NEFSC spring (index 1), ages 11 for NEFSC fall (index 2) were fully selected so selectivity was fixed at 1 for these ages in the converged run below, and only the spring index had variable selectivity so a random effect was only included for this index and the fleet in the full run below. Fall selectivity also peaked at age 4 so this intermediate age was also fixed at full selectivity. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA-biomass.DAT", sep="/"))
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 1)) # NEFSC fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # NA means do not fix, sets up storage object for correct number of indices

# comment out following 2 lines when freely estimating selectivity (also uncomment line 52 and comment out line 53)
fix_index_sel[[1]] <- c(5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]] <- c(4,11) # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
# randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), "none", "none") # use when freely estimating selectivity
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), "iid", "none") 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run27A") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run27A_Full-State-Space_biomassUnit", "WHAM_Run27A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run27A <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run27A)
print(paste("Number of parameters", length(WHAM_Run27A$par), sep=" "))

plot_wham_output(mod=WHAM_Run27A, out.type='html')
# plot_wham_output(mod=WHAM_Run27A, out.type='png', dir.main = paste(here::here(), "WHAM_Run27A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run27A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run27A_Full-State-Space_biomassUnit", "WHAM_Run27A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run27A_Full-State-Space_biomassUnit/WHAM_Run27A_input.rds", sep="/"))

# Rerun data
ReRun27A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment

