---
title: "WHAM_Run10_RevisedData-Maturity"
output: html_document
date: '2022-03-01'
---

## Model description

This run is similar to [run 1A](https://github.com/ahart1/PlaiceWG2021/blob/main/Plaice_Baseline_UpdatedData_Runs.Rmd) and uses revised WHAM data and updated maturity but revert to the natural mortality used in the VPA (0.2). The run uses the model as specified in the ASAP-style .dat input file.

Major differences from run 1A include: revised discard data (estimated rather than imputed) and an 11+ group in the NEFSC spring and fall surveys (with selectivity of ages 10-11+ initially set at 1). Total catch was also corrected to be biomass rather than numbers. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
M_input <- list(initial_means = rep(0.2, 11))

input <- prepare_wham_input(asap3, model_name = "WHAM_Run10", M = M_input) 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run10 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run10)
print(paste("Number of parameters", length(WHAM_Run10$par), sep=" "))

plot_wham_output(mod=WHAM_Run10, out.type='html')
# plot_wham_output(mod=WHAM_Run10, out.type='png', dir.main = paste(here::here(), "WHAM_Run10", sep="/"))
```

### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run10_RevisedData-Maturity", "WHAM_Run10_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run10, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run10_RevisedData-Maturity", "WHAM_Run10_model.rds", sep="/"))
```

## Comments
Similar diagnostic problems with run 9, large residual patterns across survey ages. This run had lower SSB, higher F, and lower recruitment expectations than run 9, likely due to lower M (used VPA value of 0.2).

