---
title: "WHAM_Run36_allIndices"
output: html_document
date: '2022-03-25'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with all indices included (NEFSC, MADMF, MENH, LPUE - indices 1-7 respectively). 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)

# Overwrite settings to use the MENH indices
asap3$dat$use_index_acomp[13:14] <- 1 # use index age comp
asap3$dat$use_index[13:14] <- 1 # use indices 13-14 (MENH)

# Overwrite settings to use the LPUE indicex in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 7 
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 6), "logistic")

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF fall
                       c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1), # MENH spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1),  # MENH fall
                       c(2,0.4)) # LPUE

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2 NEFSC fall
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3 MADMF spring
fix_index_sel[[4]][1] <- 3 # Fix age 3 for for index 4 MADMF fall
fix_index_sel[[5]][1] <- 2 # Fix age 2 for index 5 MENH spring
fix_index_sel[[6]][1] <- 1 # Fix age 1 for index 6 MENH fall
# Don't fix parameters for logistic selectivity for index 7 LPUE

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices-1), "iid")

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, recruit_model = recruit_model, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run36") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run36_allIndices", "WHAM_Run36_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run36 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = FALSE) 
check_convergence(WHAM_Run36)
print(paste("Number of parameters", length(WHAM_Run36$par), sep=" "))

plot_wham_output(mod=WHAM_Run36, out.type='html')
# plot_wham_output(mod=WHAM_Run36, out.type='png', dir.main = paste(here::here(), "WHAM_Run36", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run36, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run36_allIndices", "WHAM_Run36_model.rds", sep="/"))
```

### Debug
```{r}
# Look at parameter list
WHAM_Run36$parList
WHAM_Run36$rep$logit_selpars

# Look at parameter estimates
WHAM_Run36$sdrep

# debug NA/NaN
WHAM_Run36A <- fit_wham(input, do.fit=F)
therep = WHAM_Run36A$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run36_allIndices/WHAM_Run36_input.rds", sep="/"))

# Rerun data
ReRun36 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model does not converge when a full state-space model is implemented, also does not converge when recruitment random effects implemented. 
