---
title: "WHAM_Run22_2SelBlock_changeESS"
output: html_document
date: '2022-03-01'
---

## Model description
Exactly the same as WHAM run 16 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, two selectivity blocks, one from 1980-1999 and another from 2000-2019), but change catch effective sample size to 30 rather than 100 and survey effective sample size to 30 rather than 50 as was done in ASAP run 12. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_2SelBlock_changeESS.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
use_n_selBlocks = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4), c(2,0.4)) # logistic parameters for each selectivity block, based on model type

init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:(asap3$dat$n_fleets*use_n_selBlocks), function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run22") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run22_2SelBlock_changeESS", "WHAM_Run22_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run22 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run22)
print(paste("Number of parameters", length(WHAM_Run22$par), sep=" "))

plot_wham_output(mod=WHAM_Run22, out.type='html')
# plot_wham_output(mod=WHAM_Run22, out.type='png', dir.main = paste(here::here(), "WHAM_Run22", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run22, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run22_2SelBlock_changeESS", "WHAM_Run22_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run22_2SelBlock_changeESS/WHAM_Run22_input.rds", sep="/"))

# Rerun data
Rerun22 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
AIC is larger than run 16, R CV is higher at the end of the timeseries than run 16.

