---
title: "WHAM_Run23_SelRandEffect-iid"
output: html_document
date: '2022-03-02'
---

## Model description
This run is similar to run 13 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity), but incorporates an iid random effect for selectivity rather than a constant selectivity over time/age as in run 13 or two fleet selectivity blocks as explored in runs 16-22.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run23") 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run23 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run23)
print(paste("Number of parameters", length(WHAM_Run23$par), sep=" "))

plot_wham_output(mod=WHAM_Run23, out.type='html')
# plot_wham_output(mod=WHAM_Run23, out.type='png', dir.main = paste(here::here(), "WHAM_Run23", sep="/"))
```

### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run23_SelRandEffect-iid", "WHAM_Run23_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run23, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run23_SelRandEffect-iid", "WHAM_Run23_model.rds", sep="/"))
```

## Comment
The still fixed index 1 (NEFSC spring) selectivity for ages 4 and 5 at 1 and index 2 (NEFSC fall) selectivity for age 4 at 1. Selectivity at age 1 was more variable over time for index 2 (NEFSC fall) than index 1 (NEFSC spring) or the fleet. Index 2 (NEFSC fall) consistently had an increase in selectivity for age 11+ compared to the age 10 selectivity estimate. Age comp residuals for the fleet and both indices were generally smaller than run 16 which used 2 fleet selectivity blocks. Recruitment CV at the end of the timeseries is larger than that in run 16.

