---
title: "WHAM_Run45_addEnvCov-q-AMO-noEffect"
output: html_document
date: '2022-05-10'
---

## Model description
Model specified as in run 29B with 2 major differences, 1) only age 5 in spring indices and age 4 in fall indices were fixed at full selectivity and 2) this run was fit with an environmental covariate that has no effect so it can be directly compared to run 45A that incorporates this environmental effect on catchability. The Atlantic Multidecadal Oscillation (AMO) was the environmental covariate considered here.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load and filter environmental data to match year range of other model data
AMO <- read.csv(paste(here::here(), "data", "AMO_se.csv", sep="/"))
# Add placeholder for missing years of data
AMO <- rbind(c(1981, -999, -999, -999, -999), AMO) # 1981 years in the wrong order will cause R to bomb
AMO <- rbind(c(1980, -999, -999, -999, -999), AMO) # 1980
AMO <- rbind(c(1979, -999, -999, -999, -999), AMO) # 1979
```

### Initial run with freely estimated selectivity
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "AMO",
    mean = as.matrix(AMO$mean),
    logsigma = as.matrix(AMO$se),
    year = as.numeric(AMO$Year),
    use_obs = matrix(c(FALSE, FALSE, FALSE, rep(TRUE, nrow(AMO)-3)), ncol = 1, nrow=nrow(AMO)), # use all obs except the first 3 (no data 1979, 1980, and 1981 not full year of data in 1981) 
    lag = 0, # no lag for catchability
    #process_model = "ar1",
    process_model = "rw",
    where = "none", # "q" when turned on
    how = 0, # 1 when turned on
    indices = list(c(1,2,3,4)) # Indices to apply rand effect to NULL if not applying to an index (may want to exclude for Bigelow?)
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

# fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
# fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
# fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
# fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run45") 

WHAM_Run45 <- fit_wham(input, do.osa = FALSE, do.retro = FALSE) 
check_convergence(WHAM_Run45)
print(paste("Number of parameters", length(WHAM_Run45$par), sep=" "))

# ID ages that should be fixed at full selectivity
#divide by max selectivity
t(sapply(WHAM_Run45$rep$selAA[2:5], function(x) x[1,]/max(x[1,])))
```

### Prepare model input for full run
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "AMO",
    mean = as.matrix(AMO$mean),
    logsigma = as.matrix(AMO$se),
    year = as.numeric(AMO$Year),
    use_obs = matrix(c(FALSE, FALSE, FALSE, rep(TRUE, nrow(AMO)-3)), ncol = 1, nrow=nrow(AMO)), # use all obs except the first 3 (no data 1979, 1980, and 1981 not full year of data in 1981) 
    lag = 0, # AMO anomaly in year t impact R in year t+1
    #process_model = "ar1",
    process_model = "rw",
    where = "none", 
    how = 0,
    indices = list(c(1,2,3,4))
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(5) # Fix age 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(5) # Fix age 5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4) # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run45") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run45_addEnvCov-q-AMO-noEffect", "WHAM_Run45_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run45 <- fit_wham(input, do.osa = TRUE, do.retro = TRUE) 
check_convergence(WHAM_Run45)
print(paste("Number of parameters", length(WHAM_Run45$par), sep=" "))

plot_wham_output(mod=WHAM_Run45, out.type='html')
# plot_wham_output(mod=WHAM_Run45, out.type='png', dir.main = paste(here::here(), "WHAM_Run45", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run45, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run45_addEnvCov-q-AMO-noEffect", "WHAM_Run45_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run45_addEnvCov-q-AMO-noEffect/WHAM_Run45_input.rds", sep="/"))

# Rerun data
ReRun45 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Run did not converge, it appears that the fit to AMO enviromental covariate data was poor, whith OSA residuals that were not normally distributed..

