---
title: "WHAM_Run29F-2_swapInitSel-randAlbFall"
output: html_document
date: '2022-04-28'
---

## Model description
Model identical to run 29F-1 (full state-space model, revised data, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean, with split Albatross and Bigelow indices and a logistic-normal age composition likelihood, selectivity-at-age initial values similar to 29B), but include selectivity random effects for index 3 (Albatross fall). 

I tried freely estimating the selectivity for age 11+ for index 3 (Albatross fall), but the model did not converge unless selectivity for this age was fixed, so this run fixed Albatross fall age 11+ selectivity at the estimated value from Run 29B. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))
```

### Read in model results from Run 29B
Use selectivity estimates as starting estimates for this run (29F-1)
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds",
                     "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp/WHAM_Run29F_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29B", "29F"), sep="")
Run29B <- models$Run29B
```

### Prepare model input for full run
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# Use selectivity estimates from run 29B as starting estimates
  # read in run 29 and 29B
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29_splitNEFSC/WHAM_Run29_model.rds",
                     "WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds"), sep="/")
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c(29, "29B"), sep="")
  # Use selectivity estimates
init_index_sel <- list(c(models$Run29B$rep$selAA[[2]][1,]), # Albatross spring
                       c(models$Run29B$rep$selAA[[3]][1,]), # Bigelow spring
                       c(models$Run29B$rep$selAA[[4]][1,]), # Albatross fall
                       c(models$Run29B$rep$selAA[[5]][1,])) # Bigelow fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(5,6) # Fix age 5 & 6  for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4,11) # Fix age 4 & 11 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(3,4) # Fix age 3 & 4 for for index 4 (NEFSC fall Bigelow)

# Update initial selectivity estimates based on fully selected fixed ages
init_index_sel[[1]][fix_index_sel[[1]]] <- 1 # Fix at full selectivity
init_index_sel[[1]][4] <- 0.5 # Reset starting estimates that were fixed at 1 in run 29B but not estimated at full selectivity in initial freely estimated run here
init_index_sel[[2]][fix_index_sel[[2]]] <- 1
init_index_sel[[3]][4] <- 1
init_index_sel[[4]][fix_index_sel[[4]]] <- 1
init_index_sel[[4]][5] <- 0.5

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), "none", "none", "iid", "none") # Include a selectivity random effect for index 3 (Albatross fall)

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F2", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-2_swapInitSel-randAlbFall", "WHAM_Run29F-2_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# Run with OSA residuals
WHAM_Run29F2 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=TRUE) 
check_convergence(WHAM_Run29F2)
print(paste("Number of parameters", length(WHAM_Run29F2$par), sep=" "))

plot_wham_output(mod=WHAM_Run29F2, out.type='html')
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29F2, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-2_swapInitSel-randAlbFall", "WHAM_Run29F-2_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29F-2_swapInitSel-randAlbFall/WHAM_Run29F-2_input.rds", sep="/"))

# Rerun data
ReRun29F2 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

### Plot Bigelow:Albatross catchability for spring and fall indices
Lines 110-123 borrowed from plot_q() function used to generate default q plots in WHAM
```{r}
# Read in model (need to read > 1 so subsetting works)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29F-1_swapInitSel/WHAM_Run29F-1_model.rds",
                     "WHAM_Run29F-2_swapInitSel-randAlbFall/WHAM_Run29F-2_model.rds",
                     "WHAM_Run29F-3_swapInitSel-fixAlbFall/WHAM_Run29F-3_model.rds"), sep="/")
# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29F1", "29F2", "29F3"), sep="")

mod <-  models$Run29F2

  if("sdrep" %in% names(mod)){
    if("q_re" %in% mod$input$random){
      se = as.list(mod$sdrep, "Std. Error", report=TRUE)$logit_q_mat
    }else{
      se = t(matrix(as.list(mod$sdrep, "Std. Error")$logit_q, nrow = NCOL(mod$rep$logit_q_mat), 
      ncol = NROW(mod$rep$logit_q_mat)))
    }
    logit_q_lo = mod$rep$logit_q_mat - qnorm(0.975)*se
    logit_q_hi = mod$rep$logit_q_mat + qnorm(0.975)*se
    ### Retransform out of logit space
    q = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(mod$rep$logit_q_mat))))
    q_lo = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(logit_q_lo))))
    q_hi = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(logit_q_hi))))
  }

### Constant q over time series so pick first line and plot 2 ways:
q <- q[1,]
q_lo <- q_lo[1,]
q_hi <- q_hi[1,]

q_dat <- data.frame(q = q, q_lo = q_lo, q_hi = q_hi, index = c("Alb spring", "Big spring", "Alb fall", "Big fall"))

# Plot q value with confidence bounds
ggplot(q_dat) + 
  geom_bar(aes(x=index, y=q), stat="identity") + 
  scale_x_discrete(limits = c("Alb spring", "Big spring", "Alb fall", "Big fall")) + 
  geom_errorbar(aes(index, ymin = q_lo, ymax = q_hi), width = 0.4, colour = "orange", size = 1.3) +
  ylim(0,0.00029)
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-2_swapInitSel-randAlbFall/plots_png/q_barplot.png", sep="/"))

# Plot ratio of bigelow to albatross q values
springRatio <- q_dat[which(q_dat$index == "Big spring"), "q"]/ q_dat[which(q_dat$index == "Alb spring"), "q"]
fallRatio <- q_dat[which(q_dat$index == "Big fall"), "q"]/ q_dat[which(q_dat$index == "Alb fall"), "q"]

qRatio <- data.frame(qRatio = c(springRatio, fallRatio), Season = c("Spring", "Fall"))

ggplot() +
  geom_bar(data = qRatio, aes(x=Season, y = qRatio), stat = "identity") +
  ylim(0,1.5)
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-2_swapInitSel-randAlbFall/plots_png/qRatio_barplot.png", sep="/"))
```

### Plot sel*catchability Bigelow:Albatross ratio
```{r}
# Read in model (need to read > 1 so subsetting works)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29F-1_swapInitSel/WHAM_Run29F-1_model.rds",
                     "WHAM_Run29F-2_swapInitSel-randAlbFall/WHAM_Run29F-2_model.rds",
                     "WHAM_Run29F-3_swapInitSel-fixAlbFall/WHAM_Run29F-3_model.rds"), sep="/")
# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29F1", "29F2", "29F3"), sep="")

# Catchability at age: QAA [1list, index number, age/s]
albSpringQ <- models$Run29F2$rep$QAA[1,1,]
bigSpringQ <- models$Run29F2$rep$QAA[1,2,]
albFallQ <- models$Run29F2$rep$QAA[1,3,]
bigFallQ <- models$Run29F2$rep$QAA[1,4,]

# Selectivity-at-age used for selectivity blocks - pick first row for indices since no random effect implemented (constant value over time series)
albSpringSel <- models$Run29F2$rep$selAA[[2]][1,] # Albatross spring
bigSpringSel <- models$Run29F2$rep$selAA[[3]][1,] # Bigelow spring
albFallSel <- models$Run29F2$rep$selAA[[4]][1,] # Albatross fall
bigFallSel <- models$Run29F2$rep$selAA[[5]][1,] # Bigelow fall

# Multiply q*selectivity estimate
albSpring <- albSpringQ*albSpringSel
bigSpring <- bigSpringQ*bigSpringSel
albFall <- albFallQ*albFallSel
bigFall <- bigFallQ*bigFallSel

# Plot spring Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpring = albSpring, bigSpring = bigSpring, albFall = albFall, bigFall = bigFall) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigSpring/albSpring), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") + 
  ggtitle("Spring Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-2_swapInitSel-randAlbFall/plots_png/sel-q-Spring_barplot.png", sep="/"))

# Plot fall Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpring = albSpring, bigSpring = bigSpring, albFall = albFall, bigFall = bigFall) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigFall/albFall), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") +
  ggtitle("Fall Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-2_swapInitSel-randAlbFall/plots_png/sel-q-Fall_barplot.png", sep="/"))
```

## Comment
F and recruitment estimates for run 29F-2 were lower and SSB was slightly higher than run 29. The CVs around these estimates were slightly lower for R and SSB across the time series. 

OSA residuals for the fit to aggregate data for the fleet and all indices for run 29F-2 were similarly or slightly more normally distributed than run 29F. OSA residuals for fit to age comp data were similarly distributed in both runs. 

AIC and Mohn's rho values for run 29F-2 were larger than in run 29F.  