---
title: "WHAM_Run19_2SelBlock_logistic-normal-agecomp_Index2Sel-logistic"
output: html_document
date: '2022-02-28'
---

## Model description
This run is the same as run 18, (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, two selectivity blocks, one from 1980-1999 and another from 2000-2019) with logistic-normal-miss0 age composition model which applies a logistic normal model and treats zero observations as missing, but selectivity for index 2 (NEFSC fall) is logistic.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_2SelBlock.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
use_n_selBlocks = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), c("age-specific", "logistic"))

init_fleet_sel <- list(c(2,0.4), c(2,0.4)) # logistic parameters for each selectivity block, based on model type

init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(2,0.4))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:(asap3$dat$n_fleets*use_n_selBlocks), function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- NA # Don't fix any parameters for logistic selectivity

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

# Specify age_comp model to use
age_comp <- "logistic-normal-miss0"

input <- prepare_wham_input(asap3, selectivity = sel_list, age_comp = age_comp, model_name = "WHAM_Run19") 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run19 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run19)
print(paste("Number of parameters", length(WHAM_Run19$par), sep=" "))

plot_wham_output(mod=WHAM_Run19, out.type='html')
# plot_wham_output(mod=WHAM_Run19, out.type='png', dir.main = paste(here::here(), "WHAM_Run19", sep="/"))
```


### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run19_2SelBlock_logistic-normal-agecomp_Index2Sel-logistic", "WHAM_Run19_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run19, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run19_2SelBlock_logistic-normal-agecomp_Index2Sel-logistic", "WHAM_Run19_model.rds", sep="/"))
```

## Comment
Model converged and the hessian was invertible which improves on run 18. Similar to run 14 that also applied logistic selectivity to index 2 (NEFSC fall), this run had more similar catchability estimates for index 1 and 2, however index 1 had larger confidence intervals than index 2 (compared to those observed in run 16). Index 1 selectivity was bumpier/less dome-shaped after age 5 than in run 16. There were large fleet age comp residuals for age 3 (some years), 4 (most years), and age 5 (some years) , index 1 (NEFSC spring) age comp residuals for age 2-3 and index 2 (NEFSC fall) age 2. OSA residuals may be slightly less normally distributed for the fleet and more normally distributed for the indices when compared to run 16.

