---
title: "WHAM_Run13_FixSelectivity-at-age"
output: html_document
date: '2022-02-28'
---

## Model description
This run is similar to [run 3](https://github.com/ahart1/PlaiceWG2021/blob/main/Plaice_Baseline_UpdatedData_Runs.Rmd) and uses revised WHAM, updated maturity and natural mortality. Selectivity at age 4 and 5 was fixed at 1 for both the NEFSC spring survey and age 4 was fixed at 1 for the fall surveys, both assuming age-specific selectivity. Commercial fleet selectivity is assumed to be logistic and was freely estimated at all ages.

Major differences from run 3 include: revised discard data (estimated rather than imputed), and an 11+ group in the NEFSC spring and fall surveys. Total catch was also corrected to be biomass rather than numbers. Selectivity in the .dat file is different than that in run 3, but this is overwritten by the input so it is not a significant difference. Additionally, age 4 and 5 were both fixed at 1 for the NEFSC spring survey while run 3 only fixed age 4 at 1.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA.DAT", sep="/"))
```

### Prepare model input
```{r}
# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
# fix_index_sel <- lapply(1:use_n_indices, function(x) 4) # Fix age 4 for both indices,  NA means do not fix 

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, selectivity = sel_list, model_name = "WHAM_Run13") 
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run13 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run13)
print(paste("Number of parameters", length(WHAM_Run13$par), sep=" "))

plot_wham_output(mod=WHAM_Run13, out.type='html')
# plot_wham_output(mod=WHAM_Run13, out.type='png', dir.main = paste(here::here(), "WHAM_Run13", sep="/"))
```

### Save input & output
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run13_FixSelectivity-at-age", "WHAM_Run13_input.rds", sep="/"))

# Save fitted model
saveRDS(WHAM_Run13, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run13_FixSelectivity-at-age", "WHAM_Run13_model.rds", sep="/"))
```

## Comment
The model converged and the hessian was invertable so this improves upon run 12. Index 2 (NEFSC fall) still has an increase in estimated selectivity for the 11+ group. May be worth exploring logistic selectivity for this index, also selectivity blocks or time-varying selectivity. There are still some large residuals for index ages 1 and 2 in some years but in general the patterns observed in runs 9-11 are no longer apparent. 
