---
title: "WHAM_Run44_addEnvCov-R-anomBT-noEffect"
output: html_document
date: '2022-05-06'
---

## Model description
Model specified as in run 29B but is fit with an environmental covariate that has no effect so it can be directly compared to run 44A that incorporates this environmental effect on catchability. Annual bottom temperature anomaly was the environmental covariate considered here.


### Environmental covariate description
Annual bottom temperature anomalies were calculated by Jamie Behan using the GLORYS reanalysis product. A base period of 1981-2010 was used to calculate the temperature anomalies


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load environmental data 
BT <- read.csv(paste(here::here(), "data", "GLORYS_se.csv", sep="/"))
BT <- BT %>% filter(Year>1979)
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "BT_GLORYS",
    mean = as.matrix(BT$anomaly_bt),
    logsigma = as.matrix(BT$se_anomaly),
    year = as.numeric(BT$Year),
    use_obs = matrix(c(rep(TRUE, nrow(BT))), ncol = 1, nrow=nrow(BT)), # use all obs except the first 2 (no data 1979 and 1980, not full year of data in 1981) 
    lag = 1, # SST anomaly in year t impact R in year t+1
    #process_model = "ar1",
    process_model = "rw",
    where = "none", 
    how = 0 
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run44") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run44_addEnvCov-R-anomBT-noEffect", "WHAM_Run44_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run44 <- fit_wham(input, do.osa = TRUE, do.retro = TRUE) 
check_convergence(WHAM_Run44)
print(paste("Number of parameters", length(WHAM_Run44$par), sep=" "))

plot_wham_output(mod=WHAM_Run44, out.type='html')
# plot_wham_output(mod=WHAM_Run44, out.type='png', dir.main = paste(here::here(), "WHAM_Run44", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run44, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run44_addEnvCov-R-anomBT-noEffect", "WHAM_Run44_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run44_addEnvCov-R-anomBT-noEffect/WHAM_Run44_input.rds", sep="/"))

# Rerun data
ReRun44 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
AIC score is within +/-2 of runs 44A so considered equivalent to this run (see scripts for run 44A for more specifics).
