---
title: "Diagnostics"
output: html_document
date: '2022-04-25'
---

This script includes code to plot other diagnostics. 

### Look at survey data by age
The Albatross fall index consistently had an increased selectivity for the 11+ group compared to age 10, while this pattern was not observed for the spring indices and the Bigelow fall in run 29B. The following plots the distribution of survey ages in a couple of different ways to investigate whether the survey caught more older fish in the fall Albatross years.
```{r}
# Read in data
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

albSpring <- asap3$dat$IAA_mats[[1]][,c(1,4:14)] %>% as.data.frame() # Albatross spring index
colnames(albSpring) <- c("Year", "Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11")
albSpring <- albSpring %>% subset(Age1 != -999) %>% pivot_longer(cols = c("Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11"), names_to = "Ages", values_to = "NAA") %>% group_by(Year)
albSpring <- cbind(albSpring, rep(c(1:11), 29))
colnames(albSpring) <- c("Year", "Ages", "NAA", "Age")

bigSpring <- asap3$dat$IAA_mats[[2]][,c(1,4:14)] %>% as.data.frame() # Bigelow spring index
colnames(bigSpring) <- c("Year", "Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11")
bigSpring <- bigSpring %>% subset(Age1 != -999) %>% pivot_longer(cols = c("Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11"), names_to = "Ages", values_to = "NAA") %>% group_by(Year)
bigSpring <- cbind(bigSpring, rep(c(1:11), 11))
colnames(bigSpring) <- c("Year", "Ages", "NAA", "Age")

albFall <- asap3$dat$IAA_mats[[3]][,c(1,4:14)] %>% as.data.frame() # Albatross fall index
colnames(albFall) <- c("Year", "Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11")
albFall <- albFall %>% subset(Age1 != -999) %>% pivot_longer(cols = c("Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11"), names_to = "Ages", values_to = "NAA") %>% group_by(Year)
albFall <- cbind(albFall, rep(c(1:11), 29))
colnames(albFall) <- c("Year", "Ages", "NAA", "Age")

bigFall <- asap3$dat$IAA_mats[[4]][,c(1,4:14)] %>% as.data.frame() # Bigelow fall index
colnames(bigFall) <- c("Year", "Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11")
bigFall <- bigFall %>% subset(Age1 != -999) %>% pivot_longer(cols = c("Age1", "Age2", "Age3", "Age4", "Age5", "Age6", "Age7", "Age8", "Age9", "Age10", "Age11"), names_to = "Ages", values_to = "NAA") %>% group_by(Year)
bigFall <- cbind(bigFall, rep(c(1:11), 11))
colnames(bigFall) <- c("Year", "Ages", "NAA", "Age")
```
Plot time series for each fleet
```{r}
albSpring %>% ggplot() + geom_line(aes(x=Age, y=NAA)) + geom_area(aes(x=Age, y=NAA)) + facet_wrap(~Year)

bigSpring %>% ggplot() + geom_line(aes(x=Age, y=NAA)) + geom_area(aes(x=Age, y=NAA)) + facet_wrap(~Year)

albFall %>% ggplot() + geom_line(aes(x=Age, y=NAA)) + geom_area(aes(x=Age, y=NAA)) + facet_wrap(~Year)

albSpring %>% ggplot() + geom_line(aes(x=Age, y=NAA)) + geom_area(aes(x=Age, y=NAA)) + facet_wrap(~Year)
```
Overlap by season
```{r}
ggplot()  + geom_area(data = albFall, aes(x=Age, y=NAA), alpha=0.25, color = "blue", fill = "blue") +
  geom_area(data = albSpring, aes(x=Age, y=NAA), alpha=0.25, color = "gold", fill = "gold") +
  facet_wrap(~Year)

ggplot()  + geom_area(data = bigFall, aes(x=Age, y=NAA), alpha=0.25, color = "blue", fill = "blue") +
  geom_area(data = bigSpring, aes(x=Age, y=NAA), alpha=0.25, color = "gold", fill = "gold") +
  facet_wrap(~Year)
```

Overlap by season
```{r}
# Albatross
albFallMore11 <- albFall %>% filter(Age>9) %>% select(Year, Ages, NAA) %>% pivot_wider(names_from = Ages, values_from = NAA) %>%  filter(Age11 > Age10)
percentAlbFallMore11 <- nrow(albFallMore11)/length(unique(albFall$Year))

albSprMore11 <- albSpring %>% filter(Age>9) %>% select(Year, Ages, NAA) %>% pivot_wider(names_from = Ages, values_from = NAA) %>%  filter(Age11 > Age10)
percentAlbSprMore11 <- nrow(albSprMore11)/length(unique(albSpring$Year))

# 86.2069 % Albatross fall years have age 11+ numbers per tow > age 10
# 41.37931 % Albatross spring years have age 11+ numbers per tow > age 10
ggplot()  + geom_area(data = albFall[which(albFall$Age>8),], aes(x=Age, y=NAA), alpha=0.25, color = "blue", fill = "blue") +
  geom_area(data = albSpring[which(albSpring$Age>8),], aes(x=Age, y=NAA), alpha=0.25, color = "gold", fill = "gold") +
  facet_wrap(~Year) 

# Bigelow 
bigFallMore11 <- bigFall %>% filter(Age>9) %>% select(Year, Ages, NAA) %>% pivot_wider(names_from = Ages, values_from = NAA) %>%  filter(Age11 > Age10)
percentBigFallMore11 <- nrow(bigFallMore11)/length(unique(bigFall$Year))

bigSprMore11 <- bigSpring %>% filter(Age>9) %>% select(Year, Ages, NAA) %>% pivot_wider(names_from = Ages, values_from = NAA) %>%  filter(Age11 > Age10)
percentBigSprMore11 <- nrow(bigSprMore11)/length(unique(bigSpring$Year))

# 54.54545 % Bigelow fall years have age 11+ numbers per tow > age 10
# 63.63636 % Bigelow spring years have age 11+ numbers per tow > age 10
vars <- c("Bigelow_fall"="blue", "Bigelow_spring" = "gold")
ggplot()  + geom_area(data = bigFall[which(bigFall$Age>8),], aes(x=Age, y=NAA), alpha=0.25, color = vars["Bigelow_fall"], fill = vars["Bigelow_fall"]) +
  geom_area(data = bigSpring[which(bigSpring$Age>8),], aes(x=Age, y=NAA), alpha=0.25, color = vars["Bigelow_spring"], fill = vars["Bigelow_spring"]) +
  # scale_color_manual(name = "Season", values = vars) +
  # theme(legend.position = "right") +
  facet_wrap(~Year)
  
```

# Example plot to look at sel*catchability
This code is an example for Run 29B but was integrated into the scripts for run 27, 29B and 29F and any other possible candidates.
```{r}
# Catchability at age: QAA [1list, index number, age/s]
albSpringQ <- models$Run29B$rep$QAA[1,1,]
bigSpringQ <- models$Run29B$rep$QAA[1,2,]
albFallQ <- models$Run29B$rep$QAA[1,3,]
bigFallQ <- models$Run29B$rep$QAA[1,4,]

# Selectivity-at-age used for selectivity blocks - pick first row for indices since no random effect implemented (constant value over time series)
albSpringSel <- models$Run29B$rep$selAA[[2]][1,] # Albatross spring
bigSpringSel <- models$Run29B$rep$selAA[[3]][1,] # Bigelow spring
albFallSel <- models$Run29B$rep$selAA[[4]][1,] # Albatross fall
bigFallSel <- models$Run29B$rep$selAA[[5]][1,] # Bigelow fall

# Multiply q*selectivity estimate
albSpring <- albSpringQ*albSpringSel
bigSpring <- bigSpringQ*bigSpringSel
albFall <- albFallQ*albFallSel
bigFall <- bigFallQ*bigFallSel

# Plot spring Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpring = albSpring, bigSpring = bigSpring, albFall = albFall, bigFall = bigFall) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigSpring/albSpring), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") + 
  ggtitle("Spring Bigelow:Albatross Ratio")

# Plot fall Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpring = albSpring, bigSpring = bigSpring, albFall = albFall, bigFall = bigFall) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigFall/albFall), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") +
  ggtitle("Fall Bigelow:Albatross Ratio")
```



