---
title: "WHAM_Run29F-3_swapInitSel-fixAlbFall"
output: html_document
date: '2022-04-28'
---

## Model description
Model identical to run 29F-2 (full state-space model, revised data, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean, with split Albatross and Bigelow indices and a logistic-normal age composition likelihood, selectivity-at-age initial values similar to 29B, fixed Albatross fall selectivity for age 11+ at the estimate from run 29B) but do not include a selectivity random effect for the Albatross fall index (index 3). 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))
```

### Read in model results from Run 29B
Use selectivity estimates as starting estimates for this run (29F-1)
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds",
                     "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp/WHAM_Run29F_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29B", "29F"), sep="")
Run29B <- models$Run29B
```

### Prepare model input for full run
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# Use selectivity estimates from run 29B as starting estimates
  # read in run 29 and 29B
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29_splitNEFSC/WHAM_Run29_model.rds",
                     "WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds"), sep="/")
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c(29, "29B"), sep="")
  # Use selectivity estimates
init_index_sel <- list(c(models$Run29B$rep$selAA[[2]][1,]), # Albatross spring
                       c(models$Run29B$rep$selAA[[3]][1,]), # Bigelow spring
                       c(models$Run29B$rep$selAA[[4]][1,]), # Albatross fall
                       c(models$Run29B$rep$selAA[[5]][1,])) # Bigelow fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(5,6) # Fix age 5 & 6  for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4,11) # Fix age 4 & 11 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(3,4) # Fix age 3 & 4 for for index 4 (NEFSC fall Bigelow)

# Update initial selectivity estimates based on fully selected fixed ages
init_index_sel[[1]][fix_index_sel[[1]]] <- 1 # Fix at full selectivity
init_index_sel[[1]][4] <- 0.5 # Reset starting estimates that were fixed at 1 in run 29B but not estimated at full selectivity in initial freely estimated run here
init_index_sel[[2]][fix_index_sel[[2]]] <- 1
init_index_sel[[3]][4] <- 1
init_index_sel[[4]][fix_index_sel[[4]]] <- 1
init_index_sel[[4]][5] <- 0.5

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), "none", "none", "none", "none") # Don't include a selectivity random effect for index 3 (Albatross fall)

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F3", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-3_swapInitSel-fixAlbFall", "WHAM_Run29F-3_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# Run with OSA residuals
WHAM_Run29F3 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=TRUE) 
check_convergence(WHAM_Run29F3)
print(paste("Number of parameters", length(WHAM_Run29F3$par), sep=" "))

plot_wham_output(mod=WHAM_Run29F3, out.type='html')
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29F3, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-3_swapInitSel-fixAlbFall", "WHAM_Run29F-3_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29F-3_swapInitSel-fixAlbFall/WHAM_Run29F-3_input.rds", sep="/"))

# Rerun data
ReRun29F3 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

### Plot sel*catchability(precalculated as QAA output) Bigelow:Albatross ratio
```{r}
# Read in model (need to read > 1 so subsetting works)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29F-1_swapInitSel/WHAM_Run29F-1_model.rds",
                     "WHAM_Run29F-2_swapInitSel-randAlbFall/WHAM_Run29F-2_model.rds",
                     "WHAM_Run29F-3_swapInitSel-fixAlbFall/WHAM_Run29F-3_model.rds"), sep="/")
# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29F1", "29F2", "29F3"), sep="")

# Catchability at age: QAA [1list, index number, age/s]
albSpringQ <- models$Run29F3$rep$QAA[1,1,]
bigSpringQ <- models$Run29F3$rep$QAA[1,2,]
albFallQ <- models$Run29F3$rep$QAA[1,3,]
bigFallQ <- models$Run29F3$rep$QAA[1,4,]

# Plot spring Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpringQ = albSpringQ, bigSpringQ = bigSpringQ, albFallQ = albFallQ, bigFallQ = bigFallQ) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigSpring/albSpring), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") + 
  ggtitle("Spring Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-3_swapInitSel-fixAlbFall/plots_png/sel-q-Spring_barplot.png", sep="/"))

# Plot fall Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpringQ = albSpringQ, bigSpringQ = bigSpringQ, albFallQ = albFallQ, bigFallQ = bigFallQ) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigFall/albFall), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") +
  ggtitle("Fall Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-3_swapInitSel-fixAlbFall/plots_png/sel-q-Fall_barplot.png", sep="/"))
```

## Comment
Estimates of F and R were slightly lower and SSB slightly highter for run 29F-3 compared to run 29F. CVs around these estimates for R and CV were higher than in run 29F. 

OSA residuals for fit to aggregate fleet and index data were similarly or very slighlty more normally distributed in run 29F-3 compared to 29F. OSA residuals for fit to age comp data were similarly distributed for these two runs and had similar patterns.

AIC and Mohn's rho values were larger for run 29F than for run 29F-3. 
