---
title: "WHAM_Run29B-1_changeESS"
output: html_document
date: '2022-05-03'
---

## Model description
Full state-space model as in run 29B (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, iid selectivity random effect only for fleet, recruitment that is random about the mean), with NEFSC bottom trawl surveys split into Albatross (1980-2008, indices 1 and 3 for spring/fall) and Bigelow (2009-2019, indices 2 and 4 for spring/fall) time series, with NEFSC data is in Albatross AND Bigelow units, rather than using only Albatross units as in run 29. The aggregate index for this run was also in biomass units rather than abundance. 

The effective sample size for the split ESS indices and fleet catch were changed in this run to reflect the model expectations from ASAP run 51a outlined, with ESS settings for ASAP run 51a, WHAM 29B and this run WHAM 29B-1 outlined below:

| Run           | Fleet | Alb spring | Big spring | Alb fall | Big fall |
| ASAP 51A      | 30    | 30         | 30         | 30       | 30       |
| WHAM 29B      | 50    | 50         | 50         | 50       | 50       |
| **Tried       | 40    | 40         | 40         | 50       | 60       | 
| *WHAM 29B-1   | 100   | 40         | 40         | 50       | 60       | 
*Increased fleet ESS to better reflect expectation in ASAP run 51a, index ESS settings were fine
** Using Steve's recommendations for ESS based on ASAP run 51a did not converge

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit_ASAP-ESS.DAT", sep="/"))
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29B1") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B-1_changeESS", "WHAM_Run29B-1_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# Run with OSA residuals
WHAM_Run29B1 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run29B1)
print(paste("Number of parameters", length(WHAM_Run29B1$par), sep=" "))

plot_wham_output(mod=WHAM_Run29B1, out.type='html')
# plot_wham_output(mod=WHAM_Run29B1, out.type='png', dir.main = paste(here::here(), "WHAM_Run29B1", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29B1, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B-1_changeESS", "WHAM_Run29B-1_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29B-1_changeESS/WHAM_Run29B-1_input.rds", sep="/"))

# Rerun data
ReRun29B1 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

### Compare AIC and Mohn's rho values & model estimates to run 29A (iid selectivity random effect for Albatross spring index + fleet) 
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds",
                     "WHAM_Run29B-1_changeESS/WHAM_Run29B-1_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c("29B", "29B-1"), sep="")

# Generate comparative diagnostics
compare_wham_models(models, do.plot = TRUE, do.table=TRUE, fdir=paste(here::here(), "WG_Revised_Runs", "Comparison_Output", sep="/"))
```

### Plot Bigelow:Albatross catchability for spring and fall indices
Lines 110-123 borrowed from plot_q() function used to generate default q plots in WHAM
```{r}
mod <- WHAM_Run29B1

  if("sdrep" %in% names(mod)){
    if("q_re" %in% mod$input$random){
      se = as.list(mod$sdrep, "Std. Error", report=TRUE)$logit_q_mat
    }else{
      se = t(matrix(as.list(mod$sdrep, "Std. Error")$logit_q, nrow = NCOL(mod$rep$logit_q_mat), 
      ncol = NROW(mod$rep$logit_q_mat)))
    }
    logit_q_lo = mod$rep$logit_q_mat - qnorm(0.975)*se
    logit_q_hi = mod$rep$logit_q_mat + qnorm(0.975)*se
    ### Retransform out of logit space
    q = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(mod$rep$logit_q_mat))))
    q_lo = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(logit_q_lo))))
    q_hi = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(logit_q_hi))))
  }

### Constant q over time series so pick first line and plot 2 ways:
q <- q[1,]
q_lo <- q_lo[1,]
q_hi <- q_hi[1,]

q_dat <- data.frame(q = q, q_lo = q_lo, q_hi = q_hi, index = c("Alb spring", "Big spring", "Alb fall", "Big fall"))

# Plot q value with confidence bounds
ggplot(q_dat) + 
  geom_bar(aes(x=index, y=q), stat="identity") + 
  scale_x_discrete(limits = c("Alb spring", "Big spring", "Alb fall", "Big fall")) + 
  geom_errorbar(aes(index, ymin = q_lo, ymax = q_hi), width = 0.4, colour = "orange", size = 1.3) +
  ylim(0,0.00022)
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29B-1_changeESS/plots_png/q_barplot.png", sep="/"))

# Plot ratio of bigelow to albatross q values
springRatio <- q_dat[which(q_dat$index == "Big spring"), "q"]/ q_dat[which(q_dat$index == "Alb spring"), "q"]
fallRatio <- q_dat[which(q_dat$index == "Big fall"), "q"]/ q_dat[which(q_dat$index == "Alb fall"), "q"]

qRatio <- data.frame(qRatio = c(springRatio, fallRatio), Season = c("Spring", "Fall"))

ggplot() +
  geom_bar(data = qRatio, aes(x=Season, y = qRatio), stat = "identity") +
  ylim(0,1.5)
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29B-1_changeESS/plots_png/qRatio_barplot.png", sep="/"))
```

### Plot sel*catchability Bigelow:Albatross ratio
```{r}
# Read in model (need to read > 1 so subsetting works)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B-1_changeESS/WHAM_Run29B-1_model.rds",
                     "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp/WHAM_Run29F_model.rds",), sep="/")
# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29B", "29F"), sep="")

# Catchability at age: QAA [1list, index number, age/s]
albSpringQ <- models$Run29B1$rep$QAA[1,1,]
bigSpringQ <- models$Run29B1$rep$QAA[1,2,]
albFallQ <- models$Run29B1$rep$QAA[1,3,]
bigFallQ <- models$Run29B1$rep$QAA[1,4,]

# Selectivity-at-age used for selectivity blocks - pick first row for indices since no random effect implemented (constant value over time series)
albSpringSel <- models$Run29B1$rep$selAA[[2]][1,] # Albatross spring
bigSpringSel <- models$Run29B1$rep$selAA[[3]][1,] # Bigelow spring
albFallSel <- models$Run29B1$rep$selAA[[4]][1,] # Albatross fall
bigFallSel <- models$Run29B1$rep$selAA[[5]][1,] # Bigelow fall

# Multiply q*selectivity estimate
albSpring <- albSpringQ*albSpringSel
bigSpring <- bigSpringQ*bigSpringSel
albFall <- albFallQ*albFallSel
bigFall <- bigFallQ*bigFallSel

# Plot spring Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpring = albSpring, bigSpring = bigSpring, albFall = albFall, bigFall = bigFall) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigSpring/albSpring), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") + 
  ggtitle("Spring Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29B-1_changeESS/plots_png/sel-q-Spring_barplot.png", sep="/"))

# Plot fall Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpring = albSpring, bigSpring = bigSpring, albFall = albFall, bigFall = bigFall) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigFall/albFall), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") +
  ggtitle("Fall Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29B-1_changeESS/plots_png/sel-q-Fall_barplot.png", sep="/"))
```

## Comment

