---
title: "WHAM_Run29F-1_swapInitSel"
output: html_document
date: '2022-04-28'
---

## Model description
Model identical to run 29F (full state-space model, revised data, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean, with split Albatross and Bigelow indices and a logistic-normal age composition likelihood) but swap the starting selectivity-at-age values for the estimates from run 29B. A preliminary run freely estimated parameters to see if this improves estimation of these parameters (particularly age 11+). This preliminary run did not converge, but suggested that ages 5&6 for index 1 (Albatross spring), 5 for index 2 (Bigelow spring), age 4&11 for index 3 (Albatross fall) and ages 3&4 for index 4 (Bigelow fall) should be fixed at full selectivity and were subsequently fixed at 1 in the full run for which results are recorded. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))
```

### Read in model results from Run 29B
Use selectivity estimates as starting estimates for this run (29F-1)
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds",
                     "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp/WHAM_Run29F_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29B", "29F"), sep="")
Run29B <- models$Run29B
```

### Freely estimate selectivity
Use selectivity estimates from run 29B as starting parameter estimates and freely estimate selectivity-at-age
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# Use selectivity estimates from run 29B as starting estimates
  # read in run 29 and 29B
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29_splitNEFSC/WHAM_Run29_model.rds",
                     "WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds"), sep="/")
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c(29, "29B"), sep="")
  # Use selectivity estimates
init_index_sel <- list(c(models$Run29B$rep$selAA[[2]][1,]), # Albatross spring
                       c(models$Run29B$rep$selAA[[3]][1,]), # Bigelow spring
                       c(models$Run29B$rep$selAA[[4]][1,]), # Albatross fall
                       c(models$Run29B$rep$selAA[[5]][1,])) # Bigelow fall


# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

# fix_index_sel[[1]] <- c(4,5,6) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
# fix_index_sel[[2]] <- c(4,5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
# fix_index_sel[[3]] <- c(4,11) # Fix age 4 for for index 3 (NEFSC fall Albatross)
# fix_index_sel[[4]] <- c(3,4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F-1-1", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing


### Fit model, check convergence, and run diagnostics
# Run with OSA residuals
WHAM_Run29F1 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = FALSE) 
check_convergence(WHAM_Run29F1)
print(paste("Number of parameters", length(WHAM_Run29F1$par), sep=" "))

plot_wham_output(mod=WHAM_Run29F1, out.type='html')
```






### Prepare model input for full run
Fix the following ages at full selectivity  based on the above preliminary run with free estimation of selectivity-at-age parameters (did not converge): 5&6 for index 1 (Albatross spring), 5 for index 2 (Bigelow spring), age 4&11 for index 3 (Albatross fall) and ages 3&4 for index 4 (Bigelow fall).
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# Use selectivity estimates from run 29B as starting estimates
  # read in run 29 and 29B
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29_splitNEFSC/WHAM_Run29_model.rds",
                     "WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds"), sep="/")
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c(29, "29B"), sep="")
  # Use selectivity estimates
init_index_sel <- list(c(models$Run29B$rep$selAA[[2]][1,]), # Albatross spring
                       c(models$Run29B$rep$selAA[[3]][1,]), # Bigelow spring
                       c(models$Run29B$rep$selAA[[4]][1,]), # Albatross fall
                       c(models$Run29B$rep$selAA[[5]][1,])) # Bigelow fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(5,6) # Fix age 5 & 6  for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4,11) # Fix age 4 & 11 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(3,4) # Fix age 3 & 4 for for index 4 (NEFSC fall Bigelow)

# Update initial selectivity estimates based on fully selected fixed ages
init_index_sel[[1]][fix_index_sel[[1]]] <- 1 # Fix at full selectivity
init_index_sel[[1]][4] <- 0.5 # Reset starting estimates that were fixed at 1 in run 29B but not estimated at full selectivity in initial freely estimated run here
init_index_sel[[2]][fix_index_sel[[2]]] <- 1
init_index_sel[[3]][fix_index_sel[[3]]] <- 1
init_index_sel[[4]][fix_index_sel[[4]]] <- 1
init_index_sel[[4]][5] <- 0.5

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F1", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-1_swapInitSel", "WHAM_Run29F-1_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# Run with OSA residuals
WHAM_Run29F1 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=TRUE) 
check_convergence(WHAM_Run29F1)
print(paste("Number of parameters", length(WHAM_Run29F1$par), sep=" "))

plot_wham_output(mod=WHAM_Run29F1, out.type='html')
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29F1, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-1_swapInitSel", "WHAM_Run29F-1_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29F-1_swapInitSel/WHAM_Run29F-1_input.rds", sep="/"))

# Rerun data
ReRun29F1 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

### Plot sel*catchability(precalculated as QAA output) Bigelow:Albatross ratio
```{r}
# Read in model (need to read > 1 so subsetting works)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29F-1_swapInitSel/WHAM_Run29F-1_model.rds",
                     "WHAM_Run29F-2_swapInitSel-randAlbFall/WHAM_Run29F-2_model.rds",
                     "WHAM_Run29F-3_swapInitSel-fixAlbFall/WHAM_Run29F-3_model.rds"), sep="/")
# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29F1", "29F2", "29F3"), sep="")

# Catchability at age: QAA [1list, index number, age/s]
albSpringQ <- models$Run29F1$rep$QAA[1,1,]
bigSpringQ <- models$Run29F1$rep$QAA[1,2,]
albFallQ <- models$Run29F1$rep$QAA[1,3,]
bigFallQ <- models$Run29F1$rep$QAA[1,4,]

# Plot spring Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpringQ = albSpringQ, bigSpringQ = bigSpringQ, albFallQ = albFallQ, bigFallQ = bigFallQ) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigSpringQ/albSpringQ), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") + 
  ggtitle("Spring Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-1_swapInitSel/plots_png/sel-q-Spring_barplot.png", sep="/"))

# Plot fall Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpringQ = albSpringQ, bigSpringQ = bigSpringQ, albFallQ = albFallQ, bigFallQ = bigFallQ) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigFallQ/albFallQ), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") +
  ggtitle("Fall Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-1_swapInitSel/plots_png/sel-q-Fall_barplot.png", sep="/"))
```

## Comment
Still needed to fix Albatross age 11+ at full selectivity to get model to converge. Initial run that freely estimated selectivity at age estimated this age at 1, but estimated a narrower range of intermediate ages were fully selected (so narrower range fixed at 1 here). 

F, R, and SSB estimates were very similar for run 29F and 29F-1. The biggest difference between these runs was in the selectivity estimates which were slightly lower for both spring and the Bigelow fall indices.

OSA age comp residuals had similar patterns and magnitudes for the fleet and all indices in run 29F and 29F-1. Other diagnostics were also very similar between these runs. 

Mohn's rho values for SSB and Fbar were slightly larger in run 29F and slightly smaller for R. 

