---
title: "WHAM_Run35_addMADMF-LPUE"
output: html_document
date: '2022-04-01'
---

## Model description
IID recruitment random effects as in run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), but implements a selectivity iid random effect for only the fleet and LPUE index, and adds additional MADMF spring and fall indices (index 3 and 4 respectively) and an LPUE index (index 5). 

MADMF spring data was pulled from MADMF_Spr_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MADMF fall data was pulled from MADMF_Fall_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

LPUE index and CV pulled from Plaice_LPUE_Standardization_Index_01242022.lxsx


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)

# Overwrite settings to use the LPUE indicex in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 5
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 4), "logistic")

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF fall
                       c(2,0.4)) # LPUE

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 # NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2 # NEFSC fall
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3 # MADMF spring
fix_index_sel[[4]][1] <- 2 # Fix age 2 for for index 4 # MADMF fall
# Don't fix LPUE parameters

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4), "iid")

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run35") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run35_addMADMF-LPUE", "WHAM_Run35_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run35 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run35)
print(paste("Number of parameters", length(WHAM_Run35$par), sep=" "))

plot_wham_output(mod=WHAM_Run35, out.type='html')
# plot_wham_output(mod=WHAM_Run35, out.type='png', dir.main = paste(here::here(), "WHAM_Run35", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run35, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run35_addMADMF-LPUE", "WHAM_Run35_model.rds", sep="/"))
```

### Debug
```{r}
# Look at parameter list
WHAM_Run35$parList
WHAM_Run35$rep$logit_selpars

# Look at parameter estimates
WHAM_Run35$sdrep

# debug NA/NaN
WHAM_Run35A <- fit_wham(input, do.fit=F)
therep = WHAM_Run35A$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run35_addMADMF-LPUE/WHAM_Run35_input.rds", sep="/"))

# Rerun data
ReRun35 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model converged with an invertible hessian after reverting to only recruitment random effects and imposing survey selectivity random effects only for the fleet and LPUE index. The hessian was not invertible for a full state-space run with no survey selectivity random effects (issue with LPUE selectivity estimates). 

Catch residuals were more normally distributed about zero but had larger extremes than Run25. Residuals for index 1 and 2 (NEFSC spring and fall) were similar to Run 25 but are largely positive near the end of the time series while indices 3 and 4 (MADMF spring and fall) have negative residuals during these years. 

Fits to annual age comp data for index 3 (MADMF spring) and 4 (MADMF fall) particularly at young ages (1-5) varied more than fits for the NEFSC indices. Age comp residuals for were larger for the NEFSC indices at younger ages than in Run 25. MADMF age comp residuals were generally larger than NEFSC index residuals, particularly for ages 1-3. 

OSA age comp residuals have large residuals for ages 1-3 in some years but are generally evenly distributed around 0 for any age class. Index 2 (NEFSC fall) has trends of larger negative residuals for age 1-6 with more positive residuals for older ages and earlier in the time-series. Indices 3 and 4 (MADFM spring and fall) are more evenly distributed around 0 at young ages, and are largely positive for older ages (5-11+).
Fleet OSA residuals were more normally distributed while index 1 and 2 (NEFSC) residuals were similarly distributed.

The CV for recruitment estimates were smaller than those in Run 25. NEFSC index selectivity for older ages (6-11+) was lower than in Run 25 and SSB estimates were lower towards the end of the time series (2014-2019). 

