---
title: "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp"
output: html_document
date: '2022-04-18'
---

## Model description
Full state-space model as in run 29B (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), with NEFSC bottom trawl surveys split into Albatross (1980-2008, indices 1 and 3 for spring/fall) and Bigelow (2009-2019, indices 2 and 4 for spring/fall) time series, with NEFSC data is in Albatross AND Bigelow units, rather than using only Albatross units as in run 29. The aggregate index for this run was also in biomass units rather than abundance. 
The age composition likelihood was switched to "logistic-normal-miss0" as in run 29E but selectivity was specified as in run 29B.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5),
                       c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 1),
                       c(0.5, 0.5, 1, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5,6) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(4,5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4,11) # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(3,4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp", "WHAM_Run29F_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# WHAM_Run29F <- fit_wham(input, do.osa=F,do.retro=F) 
# check_convergence(WHAM_Run29F)
# WHAM_Run29F$parList$sel_repars #variance of selectivity random effects -> 0 for (last 3) surveys except first (Albatross Spring?) 
# # I suspect that the increased flexibility in the random effects for numbers at age negates the need for selectivity RE for these surveys. So, perhaps try removing the selectivity re for at least the last 3 surveys.
# print(paste("Number of parameters", length(WHAM_Run29F$par), sep=" "))

# Run with OSA residuals
WHAM_Run29F <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run29F)
print(paste("Number of parameters", length(WHAM_Run29F$par), sep=" "))

plot_wham_output(mod=WHAM_Run29F, out.type='html')
# plot_wham_output(mod=WHAM_Run29F, out.type='png', dir.main = paste(here::here(), "WHAM_Run29F", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29F, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp", "WHAM_Run29F_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29F_splitNEFSC-BigUnits-nlAgeComp/WHAM_Run29F_input.rds", sep="/"))

# Rerun data
ReRun29F <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
