---
title: "WHAM_Run30_addMADMF"
output: html_document
date: '2022-04-01'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with additional MADMF spring and fall indices (index 3 and 4 respectively). Prior data files excluded age comp data for these indices.

MADMF spring data was pulled from MADMF_Spr_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MADMF fall data was pulled from MADMF_Fall_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # full random effect
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5)) # MADMF fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3
fix_index_sel[[4]][1] <- 3 # Fix age 3 for for index 4

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, recruit_model = recruit_model, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run30") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run30_addMADMF", "WHAM_Run30_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run30 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run30)
print(paste("Number of parameters", length(WHAM_Run30$par), sep=" "))

plot_wham_output(mod=WHAM_Run30, out.type='html')
# plot_wham_output(mod=WHAM_Run30, out.type='png', dir.main = paste(here::here(), "WHAM_Run30", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run30, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run30_addMADMF", "WHAM_Run30_model.rds", sep="/"))
```

### Debug
```{r}
# Look at parameter list
WHAM_Run30$parList
WHAM_Run30$rep$logit_selpars

# Look at parameter estimates
WHAM_Run30$sdrep

# debug NA/NaN
WHAM_Run30A <- fit_wham(input, do.fit=F)
therep = WHAM_Run30A$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run30_addMADMF/WHAM_Run30_input.rds", sep="/"))

# Rerun data
ReRun30 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model converged with an invertible hessian when selectivity random effects were included for the fleet but no indices. The model never converged when random effects were included for the survey indices. 

Both index 3 (MADMF spring) and index 4 (MADMF fall) had dome shaped selectivity patterns with peaks at younger ages than the NEFSC indices (MADMF age 3 in spring, 2 & 3 in fall). Age comp residuals for these indices were larger than for the NEFSC indices, particularly age 1 in the MADMF fall. 

Catch residuals were larger, while residuals towards the end of the time series were positive for the two NEFSC indices but negative for the two MADMF indices. Age comp residuals for the fleet followed a similar pattern to that in Run25, but were slightly larger for age 11+ near the end of the time series and some intermediate years for ages 2-4 in the NEFSC spring index (e.g. 1990 age 4 NEFSC spring index 1). Index 2 (NEFSC fall) had smaller age comp residuals for several years in ages 1-4.  

The fleet's age comp likelihood contribution was larger than in Run25, but index 1 and 2 age comp likelihoods and catch likelihoods were similar or smaller than in Run25. CV of recruitment estimates at the end of the time series were higher than Run25. OSA residuals for the fleet are slightly more normally distributed, but index 1 and 2 OSA residuals are similar or slightly less normally distributed than in Run25. OSA residuals for index 3 (MADMF spring) were somewhat normally distributed, but this was not the case for index 4 (MADMF fall). 

For full state-space model that did not converge: hessian is singular, indicates there are multiple numerically equivalent solutions and the optimizer has no way to pick between them. 104 param with NAA, 103 param with only recruitment random effects.

