---
title: "WHAM_Run30_addMADMF"
output: html_document
date: '2022-04-04'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), except with an iid random effect only for fleet selectivity, and added additional MADMF spring and fall indices (index 3 and 4 respectively). Prior data files excluded age comp data for these indices.

MADMF spring data was pulled from MADMF_Spr_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MADMF fall data was pulled from MADMF_Fall_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # full random effect
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5)) # MADMF fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3 MADMF spring
fix_index_sel[[4]][1] <- 2 # Fix age 2 for for index 4 MADMF fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run30") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run30_addMADMF", "WHAM_Run30_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run30 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run30)
print(paste("Number of parameters", length(WHAM_Run30$par), sep=" "))

plot_wham_output(mod=WHAM_Run30, out.type='html')
# plot_wham_output(mod=WHAM_Run30, out.type='png', dir.main = paste(here::here(), "WHAM_Run30", sep="/"))
beep()
beep()
beep()
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run30, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run30_addMADMF", "WHAM_Run30_model.rds", sep="/"))
```

### Debug
```{r}
# Look at parameter list
WHAM_Run30$parList
WHAM_Run30$rep$logit_selpars

# Look at parameter estimates
WHAM_Run30$sdrep

# debug NA/NaN
WHAM_Run30A <- fit_wham(input, do.fit=F)
therep = WHAM_Run30A$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run30_addMADMF/WHAM_Run30_input.rds", sep="/"))

# Rerun data
ReRun30 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model converged with an invertible hessian when selectivity random effects were included for the fleet but no indices. The model never converged when selectivity random effects were included for the survey indices in the full state-space model. 

Both index 3 (MADMF spring) and index 4 (MADMF fall) had dome shaped selectivity patterns with peaks at younger ages than the NEFSC indices (MADMF age 3 in spring, 2 in fall). Age comp (and OSA age comp) residuals for these indices were larger than for the NEFSC indices, particularly age 1 in the MADMF fall. 

Catch residuals followed a similar pattern but generally were smaller in magnitude.  Residuals towards the end of the time series were positive for the two NEFSC indices (in run 27 these were more evenly distributed around zero) but negative for the two MADMF indices. Age comp residuals for the fleet followed a similar pattern to that in Run27. Index 1 had some larger residuals for age 1 and 2 near the end of the time series with more negative and slightly larger residuals for age 4-6 during the same time period. Index 2 age comp residuals followed a similar pattern but also had larger negative residuals for age 1 early in the time series. 

Fleet OSA age comp residuals were generally larger for ages 1-3 for both run 27 and 30. Age 1 were generally negative with more positive residuals for ages 2-3 in run 27 while there was a more even distribution of positive and negative residuals in run 30, but this came with a larger magnitude for early ages. Index 1 OSA age comp residuals were more negative for age 1 but more evenly distributed around zero for run 30, while run 27 had more negative residuals for age 1-3. Index 2 had more negative residuals for ages 1-3 in run 30 while residuals were largely positive for run 27. Index 3 (MADMF spring) had more negative residuals for ages 1-3 than for older ages and index 4 (MADMF fall) had much larger residuals for ages 1-2 than for older ages. 

The fleet's age comp likelihood contribution was slightly smaller than in run 27, but index 1 and 2 age comp contributions were larger. OSA residuals for the fleet and indices are about as normally distributed as in run 27. Age comp OSA residuals by age for the fleet are more evenly distributed around zero while run 27 had more of a pattern.  Index 2 age comp OSA residuals were more normally distributed than in run 27.

CV of recruitment estimates were more variable over time but were generally smaller than those in run 27 with less of an increase towards the end of the time series. 


