---
title: "WHAM_Run37E_VAST-BigUnit-randSel"
output: html_document
date: '2022-04-27'
---

## Model description
A full state-space model was implemented as in run 37 (logistic fleet selectivity, age-specific index selectivity, recruitment about the mean, fit to VAST index spring and fall indices, with a selectivity iid random effect for fleet and both indices) but the VAST data was updated based on a VAST run fit to raw survey data (NEFSC in Albatross units from 1980-2008 and Bigelow units from 2009-2019, and raw MENH and MADMF data). 

Updated VAST indices based on run with raw data were taken from:
SPRING numbers-at-age 1-1+
- TOR3 -> VAST Spatiotemporal survey index -> For Assessment -> SpringBioCompVAST.csv

FALL numbers-at-age 1-11+
- TOR3 -> VAST Spatiotemporal survey index -> For Assessment -> FallBioCompVAST.csv

SPRING aggregate index 
- TOR3 -> VAST Spatiotemporal survey index -> For Assessment -> Spring_Biomass_Index.xlsx

FALL aggregate index
- TOR3 -> VAST Spatiotemporal survey index -> For Assessment -> Fall_Biomass_Index.xlsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateVASTIndices-BigUnitUpdate.DAT", sep="/"))

# Overwrite settings to stop using design-based NEFSC indices
asap3$dat$use_index_acomp[1:2] <- 0 # don't use index age comp
asap3$dat$use_index[1:2] <- 0 # don't use design-based NEFSC spring and fall indices

# Overwrite to use VAST index that integrates all available surveys (except LPUE index)
asap3$dat$use_index_acomp[11:12] <- 1 # use index age comp
asap3$dat$use_index[11:12] <- 1 # Use VAST model-based spring and fall indices

```

### Freely estimate selectivity
Model did not converge when same selectivity used as in run 37, do run to freely estimate selectivity given new data to inform the full run 37E. Freely estimating does not result in a clear selectivity pattern (spring generally increased with age, fall full selctivity for age 10). Tried implementing logistic selectivity rather than age-specific - model converged but fall selectivity pattern still not ideal (maybe fall plus group too young?).

```{r}
NAA_re = list(sigma = "rec+1") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("logistic", use_n_indices))# rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# init_index_sel <- list(c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # all VAST spring
init_index_sel <- list(c(2,0.4), c(2,0.4))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Setup storage object to populate 

# fix_index_sel[[1]] <- c(4) # Fix age 4 for for index 1 all VAST spring
# fix_index_sel[[2]] <- c(5) # Fix age 5 for for index 2 all VAST fall

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run37E") 

# Fit model with age 
WHAM_Run37E <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE) 
check_convergence(WHAM_Run37E)
print(paste("Number of parameters", length(WHAM_Run37E$par), sep=" "))
plot_wham_output(mod=WHAM_Run37E, out.type='html')
```

### Prepare model input
Run with age _ selectivity fixed at 1 based on freely estimated run above
```{r}
NAA_re = list(sigma = "rec+1") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 2
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("logistic", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(2,0.4), c(2,0.4)) 

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Setup storage object to populate 

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run37E") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37E_VAST-BigUnit-randSel", "WHAM_Run37E_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run37E <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=TRUE) 
check_convergence(WHAM_Run37E)
print(paste("Number of parameters", length(WHAM_Run37E$par), sep=" "))

plot_wham_output(mod=WHAM_Run37E, out.type='html')
# plot_wham_output(mod=WHAM_Run37E, out.type='png', dir.main = paste(here::here(), "WHAM_Run37E", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run37E, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run37E_VAST-BigUnit-randSel", "WHAM_Run37E_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run37E_VAST-BigUnit-randSel/WHAM_Run37E_input.rds", sep="/"))

# Rerun data
ReRun37E <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment


