---
title: "Plaice_Self_Test"
output: html_document
---

# Self test candidate plaice models
The following was adapted/coppied from Brian Stock's simulation test for butterfish and pulls from the following files: best_v4_1_sim.R, best_v4_2_fitsims.R, and best_v4_4_results.R

### Load packages
```{r}
library(wham)
library(tidyverse)
library(here)
library(ggplotFL)
library(ggsci)
```

### Read in runs to self test
```{r}
# List of runs to self test (without projections)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29F-2_swapInitSel-randAlbFall/WHAM_Run29F-2_model.rds",
                     "WHAM_Run29F-4_splitNEFSC-BigUnits-nlAgeComp-fix1/WHAM_Run29F4_model.rds"),
                     #"WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/WHAM_Run29F-5_model.rds"), 
  sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c("29F2", "29F4"), sep="")
#names(models) <- paste("Run", c("29F2", "29F4", "29F5"), sep="")
n.mods <- length(models)
```

### Set up simulation settings
```{r}
# Number of sims
n.sim <- 100

# Set random seed for each simulation so replicable, save and read in so used for each model
sim.seeds <- sample(1:1000000, n.sim, replace = FALSE)
saveRDS(sim.seeds, file.path(paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", "sim_seeds.rds", sep="/")))
seeds <- readRDS(paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", "sim_seeds.rds", sep="/"))
```

### Simulate data using models from runs 29F-2, 29F-4, and 29F-5
```{r}
for(imod in 1:n.mods){ # Loop over models
  # Set up storage for each model's simulations
  simdata <- vector("list", n.sim)
  
  for(isim in 1:n.sim){ # Loop over simulations for each model
    print(paste0("Model: ", imod, "Sim: ", isim))
    
    set.seed(seeds[isim])
    
    simdata[[isim]] <- models[[imod]]$simulate(par=models[[imod]]$env$last.par.best, complete=TRUE)
  } # end loop over model-specific simulations
  
  # Save data for each model's simulations
  saveRDS(simdata, file = paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", paste0("simdata_OM", names(models)[imod], ".rds"), sep="/"))
  
} # end loop over all models
```


### Fit EM to OM simulated data
```{r}
# Test smaller number of simulations
n.sim <- 5

#TJM: These are the only elements of input$data that need to be extracted from simulated data when the EM matches the OM
obs_names = c("agg_catch","agg_indices", "catch_paa", "index_paa", "Ecov_obs", "obs", "obsvec")

for(imod in 1:n.mods){
  # Read in OM data
  simdata <- readRDS(paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", paste0("simdata_OM", names(models)[imod], ".rds"), sep="/"))
  
  # Set up sims/years/ages based on OM data
  n.sim = length(simdata) #TJM: this changes n.sim defined above
  n.years <- simdata[[1]]$n_years_model
  n.ages <- simdata[[1]]$n_ages
  
  # Reload seeds (TJM: not necessary unless "seeds" are changed for some reason)
  #seeds <- readRDS(paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", "sim_seeds.rds", sep="/"))
  
  options(warn=-1) # suppress warning messages
  
  # Set up storage for reps
  sdreps <- vector("list", n.sim)
  reps <- vector("list", n.sim)
  res.colnames <- c("om","em","year","sim","F_fit","F_sim","SSB_fit","SSB_sim","catch_fit","catch_sim",paste0("NAA",1:n.ages),"R_sim")
  results <- list(rep(list(matrix(NA, ncol = length(res.colnames), nrow = n.years)),n.sim)) # nested lists with preallocated matrices
  
  #TJM: just doing 2 to test
  #for(isim in 1:n.sim){ # Loop over model-specific simulation
  for(isim in 1:2){ # Loop over model-specific simulation
    print(paste0("OM: ", imod, " Sim: ", isim))
    
    # Set seed
    set.seed(seeds[isim])
    
    # Read in estimation model (EM)
    EM <- readRDS(modelRuns[imod]) # Read in the EM 
    inputEM <- EM$input
    #n.data <- length(inputEM$data)
    
    # process + obs errors (don't overwrite estimation model values here!!!)
      # keep fixed effect param at optimized values from fit 
      # simulate NAA (process error) and catch
      # simulate index data (observation error)
    #n_sig <- inputEM$data$n_NAA_sigma 
		#n_sig_pointers <- inputEM$data$NAA_sigma_pointers
		#age_comp_model_fleets <- inputEM$data$age_comp_model_fleets
		# n_age_comp_pars_fleets <- inputEM$data$n_age_comp_pars_fleets # Not part of input ???
		#age_comp_model_indices <- inputEM$data$age_comp_model_indices
		# n_age_comp_pars_indices <- inputEM$data$n_age_comp_pars_indices # Not part of input???
    
		# Overwrite storage with OM data for this simulation and store (i.e. use OM data rather than data from initial EM fit), above input values are unchanged from initial EM fit
    inputEM$data[obs_names] <- simdata[[isim]][obs_names] # overwrite storage 
    # inputEM$data$n_NAA_sigma <- n_sig
    # inputEM$data$NAA_sigma_pointers <- n_sig_pointers
    # inputEM$data$age_comp_model_fleets <- c(age_comp_model_fleets) # Causes error "NOT A VECTOR!" ???
    # inputEM$data$n_age_comp_pars_fleets = n_age_comp_pars_fleets # Not a part of input???
		# inputEM$data$age_comp_model_indices = age_comp_model_indices # Causes error "NOT A VECTOR!" ???
		# inputEM$data$n_age_comp_pars_indices = n_age_comp_pars_indices # Not a part of input???
inputEM$par = EM$parList		
		# Save the data and several matching pieces of info
		ind.save <- c(1:n.data, match(c("F","SSB","pred_log_catch","NAA","log_FXSPR","FAA_tot","log_SSB_FXSPR","Fbar"), names(inputEM$data)))	
		#inputEM$data <- inputEM$data[ind.save]

inputEM$map$logit_q = factor(rep(NA,length(inputEM$par$logit_q))) 
  temp = fit_wham(inputEM, do.fit = F, do.sdrep=F, do.osa=F, do.retro=F, do.proj=F, MakeADFun.silent=TRUE)	
temp = fit_wham(inputEM, do.sdrep=F, do.osa=F, do.retro=F, do.proj=F, MakeADFun.silent = TRUE)	
		# Fit EM to simulated data from OM
				fit2 <- tryCatch(fit_wham(inputEM, do.sdrep=F, do.osa=F, do.retro=F, do.proj=F, MakeADFun.silent=TRUE),
					error = function(e) conditionMessage(e))
				
		# Deal with issues fitting EM to OM data
		if(!'err' %in% names(fit2) & class(fit2) != "character"){
			reps[[i]] <- fit2$rep
			fit2$sdrep <- tryCatch(TMB::sdreport(fit2), # no bc
							error = function(e) conditionMessage(e))
			if(class(fit2$sdrep) == "sdreport"){
				s2 <- summary(fit2$sdrep)
				sdreps[[i]] <- s2
				results[[i]] <- tryCatch(calc_results(om=om, em=em, sim=i, fit1=fit2, s1=s2),
					error = function(e) conditionMessage(e))
			} else {
				results[[i]] <- "Error: sdreport failed, no results to calculate"
				sdreps[[i]] <- fit2$sdrep # error message
			}
		} else {
			results[[i]] <- "Error: model did not converge, no results to calculate"
			if(class(fit2) != "character") reps[[i]] <- fit2$err # error message
			if(class(fit2) == "character") reps[[i]] <- fit2
			sdreps[[i]] <- "Error: model did not converge, sdreport not attempted"
		}
				
		rm(list=c("inputEM","fit2")) # remove temporary input and fit data for model-specific simulation
  } # End loop over model-specific simulations
  
  rm(list=c("simdata")) # Remove temporary data for model
  
  # Save results in a single matrix
  saveRDS(results, file=paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", paste0("fitresults_", names(models)[imod],".rds"), sep="/")) # Fitted results
  saveRDS(sdreps, file=paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", paste0("sdreps_",names(models)[imod],".rds"), sep="/"))
  saveRDS(reps, file=paste(here::here(), "WG_Revised_Runs", "Plaice_Self_Test", paste0("reps_", names(models)[imod],".rds"), sep="/"))
  
} # End loop over models
```

### Plot results of self test
Adapted from best_v4_4_results.R
```{r}
# Read in results into data frame
res_dir <- here::here("WG_Revised_Runs", "Plaice_Self_Test")
plots_dir <- here::here("Plaice_Self_Test", "plots")
# dir.create(plots_dir, showWarnings=FALSE)
res.files <- list.files(path=res_dir, pattern = "fitresults", full.names = TRUE)
res.list <- lapply(res.files, readRDS)

# Define function to handle nested list
flatten.nested.list <- function(X) if(is.list(X)) Reduce(c, lapply(X, flatten.nested.list)) else list(X)

results <- do.call(rbind, flatten.nested.list(res.list)) %>% as.data.frame
results <- sapply(results, as.numeric)
results <- as.data.frame(results[complete.cases(results),])
results$om <- factor(results$om, levels=1:4, # labels=c("25-NAA2-selAA","25-Base-FAA","25-NAA2-FAA","25-NAA4-FAA"))
labels <- c("Run29F2", "Run29F4", "Run29F5") #??? check that this is correct label
results$em <- factor(results$em, levels=1:4, # labels=c("25-NAA2-selAA","25-Base-FAA","25-NAA2-FAA","25-NAA4-FAA"))
labels <- c("Run29F2", "Run29F4", "Run29F5")

# calculate relative error
results$SSB.rel = results$SSB_fit / results$SSB_sim
results$F.rel = results$F_fit / results$F_sim
results$catch.rel = results$catch_fit / results$catch_sim
results$rec.rel = results$NAA1 / results$R_sim
df.plot <- results

# get convergence rates
n.sim <- length(res.list[[1]])
df.colnames <- c("om","em","sim","conv")
df <- as.data.frame(matrix(NA, ncol = length(df.colnames), nrow = 0))
colnames(df) <- df.colnames
for(m in 1:length(res.list)){
	res <- do.call(rbind, flatten.nested.list(res.list[[m]])) %>% as.data.frame
	res <- sapply(res, as.numeric)
	res <- as.data.frame(res)
	for(i in 1:n.sim){
		tmp <- data.frame(om = unique(res$om)[!is.na(unique(res$om))], em = unique(res$em)[!is.na(unique(res$em))], sim=i, conv=NA)
		if(class(res.list[[m]][[i]])[1] != 'character') tmp$conv <- 1 else tmp$conv <- 0
		df <- rbind(df, tmp)
	}
}
df.conv <- df %>% group_by(om, em) %>% 
	summarize(p.conv=100*sum(conv)/n.sim) %>% as.data.frame
df.conv$om <- factor(df.conv$om, levels=1:4, labels=c("25-NAA2-selAA","25-Base-FAA","25-NAA2-FAA","25-NAA4-FAA"))
df.conv$em <- factor(df.conv$em, levels=1:4, labels=c("25-NAA2-selAA","25-Base-FAA","25-NAA2-FAA","25-NAA4-FAA"))

# Fig 1. SSB (sim fit) / SSB (sim data)
p <- ggplot(df.plot, aes(x=year, y=SSB.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(SSB["sim fit"]~"/"~SSB["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_grid(rows=vars(em), cols=vars(om)) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,"1_ssb.png"), width=7, height=7, units='in',res=100)
print(p)
grid::grid.text(unit(0.98,"npc"),0.5, label = 'Estimation model', rot = 270) # right
grid::grid.text(unit(0.5,"npc"),unit(.98,'npc'), label = 'Operating model', rot = 0)   # top)
dev.off()

# boxplots (collapse time series)
png(file.path(plots_dir,paste0("1_ssb_boxplots.png")), width=8, height=3.5, units='in',res=100)
print(ggplot(df.plot, aes(x=em, y=SSB.rel)) +
	geom_boxplot(aes(fill=em), outlier.shape = NA) +
	scale_fill_jco(name="Estimation model") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Estimation model") +
	ylab(expression(SSB["sim fit"]~"/"~SSB["sim data"])) +
	labs(title="Operating model") +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(plot.title = element_text(hjust = 0.5)))
dev.off()

# Fig 2. F (sim fit) / F (sim data)
p <- ggplot(df.plot, aes(x=year, y=F.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(F["sim fit"]~"/"~F["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_grid(rows=vars(em), cols=vars(om)) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,paste0("2_F.png")), width=7, height=7, units='in',res=100)
print(p)
grid::grid.text(unit(0.98,"npc"),0.5, label = 'Estimation model', rot = 270) # right
grid::grid.text(unit(0.5,"npc"),unit(.98,'npc'), label = 'Operating model', rot = 0)   # top)
dev.off()

# boxplots (collapse time series)
png(file.path(plots_dir,paste0("2_F_boxplots.png")), width=8, height=3, units='in',res=100)
print(ggplot(df.plot, aes(x=em, y=F.rel)) +
	geom_boxplot(aes(fill=em), outlier.shape = NA) +
	scale_fill_jco(name="Estimation model") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Estimation model") +
	ylab(expression(F["sim fit"]~"/"~F["sim data"])) +
	labs(title="Operating model") +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(plot.title = element_text(hjust = 0.5)))
dev.off()


# Fig 3. pred_catch (sim data) / pred_catch (true data)
p <- ggplot(df.plot, aes(x=year, y=catch.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(Catch["sim fit"]~"/"~Catch["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_grid(rows=vars(em), cols=vars(om)) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,paste0("3_catch.png")), width=7, height=7, units='in',res=100)
print(p)
grid::grid.text(unit(0.98,"npc"),0.5, label = 'Estimation model', rot = 270) # right
grid::grid.text(unit(0.5,"npc"),unit(.98,'npc'), label = 'Operating model', rot = 0)   # top)
dev.off()

# boxplots (collapse time series)
png(file.path(plots_dir,paste0("3_catch_boxplots.png")), width=8, height=3, units='in',res=100)
print(ggplot(df.plot, aes(x=em, y=catch.rel)) +
	geom_boxplot(aes(fill=em), outlier.shape = NA) +
	scale_fill_jco(name="Estimation model") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Estimation model") +
	ylab(expression(Catch["sim fit"]~"/"~Catch["sim data"])) +
	labs(title="Operating model") +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(plot.title = element_text(hjust = 0.5)))
dev.off()

# Fig 4. Recruitment (sim data) / Recruitment (true data)
p <- ggplot(df.plot, aes(x=year, y=rec.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(Recruitment["sim fit"]~"/"~Recruitment["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_grid(rows=vars(em), cols=vars(om)) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,paste0("4_R.png")), width=7, height=7, units='in',res=100)
print(p)
grid::grid.text(unit(0.98,"npc"),0.5, label = 'Estimation model', rot = 270) # right
grid::grid.text(unit(0.5,"npc"),unit(.98,'npc'), label = 'Operating model', rot = 0)   # top)
dev.off()

# boxplots (collapse time series)
png(file.path(plots_dir,paste0("4_R_boxplots.png")), width=8, height=3, units='in',res=100)
print(ggplot(df.plot, aes(x=em, y=rec.rel)) +
	geom_boxplot(aes(fill=em), outlier.shape = NA) +
	scale_fill_jco(name="Estimation model") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Estimation model") +
	ylab(expression(Recruitment["sim fit"]~"/"~Recruitment["sim data"])) +
	labs(title="Operating model") +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(plot.title = element_text(hjust = 0.5)))
dev.off()

# ----------------------------------------------
# only self-test 
df.plot$self <- 0
df.plot$self[df.plot$em == df.plot$om] = 1
df.self <- filter(df.plot, self == 1)
df.conv$self <- 0
df.conv$self[df.conv$em == df.conv$om] = 1
df.conv2 <- filter(df.conv, self == 1)

p <- ggplot(df.self, aes(x=year, y=SSB.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(SSB["sim fit"]~"/"~SSB["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv2, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,"self_1_ssb.png"), width=7, height=3, units='in',res=200)
print(p)
dev.off()

# Fig 2. F (sim fit) / F (sim data)
p <- ggplot(df.self, aes(x=year, y=F.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(F["sim fit"]~"/"~F["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv2, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,paste0("self_2_F.png")), width=7, height=3, units='in',res=200)
print(p)
dev.off()

# Fig 3. pred_catch (sim data) / pred_catch (true data)
p <- ggplot(df.self, aes(x=year, y=catch.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(Catch["sim fit"]~"/"~Catch["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv2, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,paste0("self_3_catch.png")), width=7, height=3, units='in',res=200)
print(p)
dev.off()

# Fig 4. Recruitment (sim data) / Recruitment (true data)
p <- ggplot(df.self, aes(x=year, y=rec.rel)) +
    stat_flquantiles(probs=c(0.25, 0.75), alpha=0.5, fill="grey", geom="ribbon") + # middle 50%
    stat_flquantiles(probs=c(0.10, 0.90), alpha=0.35, fill="grey", geom="ribbon") + # middle 80%
	stat_summary(fun = "median", geom = "line", color = "red") +
	coord_cartesian(ylim=c(0,2)) +
	xlab("Year") +
	ylab(expression(Recruitment["sim fit"]~"/"~Recruitment["sim data"])) +
	geom_hline(yintercept = 1, linetype=2, color='black') +
	geom_text(data = df.conv2, aes(x = 1992, y = 1.85, label = paste0(p.conv,"%")), size=4) +
	facet_wrap(vars(om), nrow=1) +
	theme_bw() +
	theme(axis.text.x = element_text(size=8), plot.margin = unit(c(0.3,0.3,0.1,0.1), "in"))
png(file.path(plots_dir,paste0("self_4_R.png")), width=7, height=3, units='in',res=200)
print(p)
dev.off()

```







