---
title: "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match"
output: html_document
date: '2022-05-12'
---

## Model description
Model identical to run 29F-4 (full state-space model, revised data, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean, with split Albatross and Bigelow indices and a logistic-normal age composition likelihood, only a single age was fixed at full selectivity for each index). 

A single age was fixed at full selectivity for each index based on the preliminary run done for run 29F-4: age 6 for index 1 (Albatross spring), 5 for index 2 (Bigelow spring), age 4 for index 3 (Albatross fall) and age 3 for index 4 (Bigelow fall) fixed at full selectivity. 

Here a preliminary run set selectivity for ages 10 and 11+ to be estimated as a single parameter. This resulted in a high parameter estimate for these ages (~0.97) which was considered high.

Instead of estimating the same value for ages 10 and 11+, the full run implemented ar1 random effects on age (not time varying, just age varying) for the Albatross fall index. This led to a selectivity at age greater than earlier ages but not near 1.

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))
```

### Prepare model input for preliminary run
Fix only 1 age selectivity at 1 for each index based on highest estimated selectivity in preliminary run from run 29F-4 (same model structure except for treatment of Albatross fall age 10/11+). Albatross fall age 10 and 11+ were freely estimated but mapped so they have the same estimate.
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

# fix_index_sel[[1]] <- c(4) # Fix age 4  for for index 1 (NEFSC spring Albatross) # From Tim's exploration
# fix_index_sel[[2]] <- c(5) # Fix age  5 for for index 2 (NEFSC spring Bigelow)
# fix_index_sel[[3]] <- c(11) # Fix age 11 for for index 3 (NEFSC fall Albatross)
# fix_index_sel[[4]] <- c(4) # Fix age 4  for for index 4 (NEFSC spring Bigelow)

fix_index_sel[[1]] <- c(6) # Fix age 6  for for index 1 (NEFSC spring Albatross) # Based on preliminary run in run 29F-4 (same model structure except for treatment of Albatross fall age 10/11+ selectivity)
fix_index_sel[[2]] <- c(5) # Fix age 5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4) # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(3) # Fix age 3  for for index 4 (NEFSC spring Bigelow)

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))
for(i in 1:use_n_indices) init_index_sel[[i]][fix_index_sel[[i]]] <- 1 # replace initial values for 1 for the ages where selectivity fixed


# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F5", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing

# Change mapping for parameters so age 10 and 11 freely estimated but both estimated at same value
temp = input$par$logit_selpars
temp[] = as.integer(input$map$logit_selpars)
temp[4,10:11] = temp[4,10]
input$map$logit_selpars = factor(temp)

```

### Save preliminary input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "WHAM_Run29F5_basic_input.rds", sep="/"))
```

### Preliminary run and diagnostics: estimate Albatross fall age 10 & 11+ jointly
```{r}
#checking fit before OSA, retro
WHAM_Run29F5_basic <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = FALSE, do.retro=FALSE) 
check_convergence(WHAM_Run29F5_basic)

# Compare number of parameters in run 29F-4 and 29F-5_basic
WHAM_Run29F4 = readRDS(paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-4_splitNEFSC-BigUnits-nlAgeComp-fix1", "WHAM_Run29F4_model.rds", sep="/"))
length(WHAM_Run29F4$opt$par) + WHAM_Run29F4$opt$obj
length(WHAM_Run29F5_basic$opt$par) + WHAM_Run29F5_basic$opt$obj

# Look at report and selectivity objects for 29F-5_basic run
WHAM_Run29F5_basic$sdrep
WHAM_Run29F5_basic$rep$selAA[[4]][1,]
```

### Save output for preliminary run
```{r}
# Save fitted model
saveRDS(WHAM_Run29F5_basic, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "WHAM_Run29F-5_basic_model.rds", sep="/"))
```

# Update model input for full run
```{r}
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), c("none","none","ar1","none")) # Apply ar1 selectivity random effect for Albatross fall index

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29F5", age_comp = "logistic-normal-miss0") # logistic normal age comp, 0s treated as missing

# TJM: I believe I have uncovered a "bug" in the configuration of "ar1" with age-specific selectivity. When these are chosen, any logit_selpars that are estimated should be set to be a single "mean" value for the ar1 process. Doing this by hand below. # This also means the CI bounds are constant around this mean
temp = input$par$logit_selpars
temp[] = as.integer(input$map$logit_selpars)
temp[4,c(1:3,5:11)] = temp[4,3]
input$map$logit_selpars = factor(temp)
```

### Save input for full run
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "WHAM_Run29F-5_input.rds", sep="/"))
```

### Full model run
```{r}
# Initial check that run converges and selectivity appropriately estimated
WHAM_Run29F5_ar1_AIV_Fall <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = FALSE, do.retro=FALSE) 
WHAM_Run29F4$rep$selAA[[4]][1,]
WHAM_Run29F5_ar1_AIV_Fall$rep$selAA[[4]][1,]

# Full run with OSA residuals
input$par = WHAM_Run29F5_ar1_AIV_Fall$parList #start at the optimized values (from run without OSA, retro) to save time
WHAM_Run29F5 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = TRUE) 
check_convergence(WHAM_Run29F5)
print(paste("Number of parameters", length(WHAM_Run29F5$par), sep=" "))

WHAM_Run29F5$rep$selAA[[4]][1,]

plot_wham_output(mod=WHAM_Run29F5, out.type='html')
# plot_wham_output(mod=WHAM_Run29F5, out.type='png', dir.main = paste(here::here(), "WHAM_Run29F5", sep="/"))
```

### Save output for full run
```{r}
# Save fitted model
saveRDS(WHAM_Run29F5, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "WHAM_Run29F-5_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/WHAM_Run29F-5_input.rds", sep="/"))

# Rerun data
ReRun29F5 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

### Plot Bigelow:Albatross catchability for spring and fall indices
Lines 110-123 borrowed from plot_q() function used to generate default q plots in WHAM
```{r}
mod <- WHAM_Run29F5

  if("sdrep" %in% names(mod)){
    if("q_re" %in% mod$input$random){
      se = as.list(mod$sdrep, "Std. Error", report=TRUE)$logit_q_mat
    }else{
      se = t(matrix(as.list(mod$sdrep, "Std. Error")$logit_q, nrow = NCOL(mod$rep$logit_q_mat), 
      ncol = NROW(mod$rep$logit_q_mat)))
    }
    logit_q_lo = mod$rep$logit_q_mat - qnorm(0.975)*se
    logit_q_hi = mod$rep$logit_q_mat + qnorm(0.975)*se
    ### Retransform out of logit space
    q = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(mod$rep$logit_q_mat))))
    q_lo = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(logit_q_lo))))
    q_hi = t(mod$input$data$q_lower + (mod$input$data$q_upper - mod$input$data$q_lower)/(1+exp(-t(logit_q_hi))))
  }

### Constant q over time series so pick first line and plot 2 ways:
q <- q[1,]
q_lo <- q_lo[1,]
q_hi <- q_hi[1,]

q_dat <- data.frame(q = q, q_lo = q_lo, q_hi = q_hi, index = c("Alb spring", "Big spring", "Alb fall", "Big fall"))

# Plot q value with confidence bounds
ggplot(q_dat) + 
  geom_bar(aes(x=index, y=q), stat="identity") + 
  scale_x_discrete(limits = c("Alb spring", "Big spring", "Alb fall", "Big fall")) + 
  geom_errorbar(aes(index, ymin = q_lo, ymax = q_hi), width = 0.4, colour = "orange", size = 1.3) +
  ylim(0,0.00029)
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/plots_png/q_barplot.png", sep="/"))

# Plot ratio of bigelow to albatross q values
springRatio <- q_dat[which(q_dat$index == "Big spring"), "q"]/ q_dat[which(q_dat$index == "Alb spring"), "q"]
fallRatio <- q_dat[which(q_dat$index == "Big fall"), "q"]/ q_dat[which(q_dat$index == "Alb fall"), "q"]

qRatio <- data.frame(qRatio = c(springRatio, fallRatio), Season = c("Spring", "Fall"))

ggplot() +
  geom_bar(data = qRatio, aes(x=Season, y = qRatio), stat = "identity") +
  ylim(0,1.5)
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/plots_png/qRatio_barplot.png", sep="/"))
```

### Plot sel*catchability(precalculated as QAA output) Bigelow:Albatross ratio
```{r}
# Read in model (need to read > 1 so subsetting works)
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_splitNEFSC-BigUnits-noSurvRandSel/WHAM_Run29B_model.rds",
                     "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/WHAM_Run29F-5_model.rds"), sep="/")
# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Run", c( "29B", "29F5"), sep="")

# Catchability at age: QAA [1list, index number, age/s]
albSpringQ <- models$Run29F5$rep$QAA[1,1,]
bigSpringQ <- models$Run29F5$rep$QAA[1,2,]
albFallQ <- models$Run29F5$rep$QAA[1,3,]
bigFallQ <- models$Run29F5$rep$QAA[1,4,]

# Plot spring Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpringQ = albSpringQ, bigSpringQ = bigSpringQ, albFallQ = albFallQ, bigFallQ = bigFallQ) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigSpringQ/albSpringQ), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") + 
  ggtitle("Spring Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/plots_png/sel-q-Spring_barplot.png", sep="/"))

# Plot fall Bigelow:Albatross ratio
data.frame(age = c(1,2,3,4,5,6,7,8,9,10,11), albSpringQ = albSpringQ, bigSpringQ = bigSpringQ, albFallQ = albFallQ, bigFallQ = bigFallQ) %>%
  ggplot() +
  geom_bar(aes(x=age, y=bigFallQ/albFallQ), stat = "identity") + 
  geom_hline(yintercept = 1, color="orange") +
  ggtitle("Fall Bigelow:Albatross Ratio")
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match/plots_png/sel-q-Fall_barplot.png", sep="/"))
```

### Plot selectivity with CI 
Borrowed code from plot.fleet.sel.blocks() for plot and par_tables_fn() for CI data
-currently pull CI mannually from WHAM Output Tables but would be good to automate so we can loop over indices
```{r}
dat <- WHAM_Run29F5$env$data
ages = 1:dat$n_ages

# Plot index selectivity (fleet doesn't have age-specific CI since logistic selectivity)
sb_p = dat$selblock_pointer_indices #selblock pointer by year and index
  # sb_p = dat$selblock_pointer_fleets #selblock pointer by year and fleet

# Index 1
i = 1
blocks = unique(sb_p[,i])
sel = do.call(rbind, lapply(WHAM_Run29F5$rep$selAA, function(x) apply(x,2,mean)))[blocks,,drop=FALSE]

data.frame(ages = ages, 
           sel = c(sel), 
           lowerCI = c(0.007, 0.132, 0.257, 0.045, 0.000, 0, 0.160, 0.262, 0.287, 0.289, 0.326),
           upperCI = c(	0.022,	0.392,	0.752,	0.999,	1.000, 1, 0.989,	0.842,	0.844,	0.877, 	0.758)) %>%
  ggplot() +
  geom_line(aes(x=ages, y=sel)) + 
  geom_ribbon(aes(x=ages,ymin=lowerCI, ymax=upperCI), alpha=0.2) + 
  ggtitle("Index 1 Selectivity")
ggsave(filename = paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "plots_png", "results", "Selectivity_index1_CI.png", sep="/"))

# Index 2
i = 2
blocks = unique(sb_p[,i])
sel = do.call(rbind, lapply(WHAM_Run29F5$rep$selAA, function(x) apply(x,2,mean)))[blocks,,drop=FALSE]

data.frame(ages = ages, 
           sel = c(sel), 
           lowerCI = c(0.052, 0.220, 0.439, 0.030, 1, 0.489, 0.446, 0.419, 0.394, 0.369, 0.374),
           upperCI = c(0.111,	0.447,	0.869,	1.000, 1, 0.933, 0.854,	0.819,	0.780, 0.741,	0.640)) %>%
  ggplot() +
  geom_line(aes(x=ages, y=sel)) + 
  geom_ribbon(aes(x=ages,ymin=lowerCI, ymax=upperCI), alpha=0.2) + 
  ggtitle("Index 2 Selectivity")
ggsave(filename = paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "plots_png", "results", "Selectivity_index2_CI.png", sep="/"))

# Index 3
i = 3
blocks = unique(sb_p[,i])
sel = do.call(rbind, lapply(WHAM_Run29F5$rep$selAA, function(x) apply(x,2,mean)))[blocks,,drop=FALSE]

data.frame(ages = ages, 
           sel = c(sel), 
           lowerCI = c(0.285, 0.285, 0.285, 1, 0.285, 0.285, 0.285, 0.285, 0.285, 0.285, 0.285),
           upperCI = c(0.804,	0.804,	0.804, 1, 	0.804, 	0.804, 0.804,	0.804,	0.804,	0.804,	0.804)) %>%
  ggplot() +
  geom_line(aes(x=ages, y=sel)) + 
  geom_ribbon(aes(x=ages,ymin=lowerCI, ymax=upperCI), alpha=0.2) + 
  ggtitle("Index 3 Selectivity")
ggsave(filename = paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "plots_png", "results", "Selectivity_index3_CI.png", sep="/"))

# Index 4
i = 4
blocks = unique(sb_p[,i])
sel = do.call(rbind, lapply(WHAM_Run29F5$rep$selAA, function(x) apply(x,2,mean)))[blocks,,drop=FALSE]

data.frame(ages = ages, 
           sel = c(sel), 
           lowerCI = c(0.148, 0.194, 1, 0.032, 0.129, 0.202, 0.192, 0.179, 0.173, 0.185, 0.207),
           upperCI = c(0.630,	0.874, 1,	0.999,	0.989,	0.909, 0.853,	0.833,	0.812,	0.960,	0.640)) %>%
  ggplot() +
  geom_line(aes(x=ages, y=sel)) + 
  geom_ribbon(aes(x=ages,ymin=lowerCI, ymax=upperCI), alpha=0.2) + 
  ggtitle("Index 4 Selectivity")
ggsave(filename = paste(here::here(), "WG_Revised_Runs", "WHAM_Run29F-5_splitNEFSC-BigUnits-nlAgeComp-11Match", "plots_png", "results", "Selectivity_index4_CI.png", sep="/"))
```

## Comment
Albatross fall selectivity estimates were slightly lower for all but age 4 (fixed at full selectivity) than run 29F-4 but were still freely estimated in run 29F-5. The bigelow fall index also had slightly lower selectivity estimates for age 5-11+.

Age comp OSA residual distribution and patterns were similar across runs 29F-4 and 29F-5. OSA residuals for fit to aggregate fleet and index data were similarly or slightly more normally distributed than in run 29F-4. In particular, the OSA residuals for Albatross fall were more normally distributed.

Mohn's rho values for R, SSB, and F_bar were larger than in run 29F-4, and the AIC value for run 29F-5 was larger. SSB estimates for these two runs were very similar but F and R estimates tended to be slightly lower across the time series which resulted in slightly lower reference points.
