---
title: "WHAM_Run29G_splitNEFSC-BigUnits-dirmultAgeComp"
output: html_document
date: '2022-04-18'
---

## Model description
Full state-space model as in run 29B (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), with NEFSC bottom trawl surveys split into Albatross (1980-2008, indices 1 and 3 for spring/fall) and Bigelow (2009-2019, indices 2 and 4 for spring/fall) time series, with NEFSC data is in Albatross AND Bigelow units, rather than using only Albatross units as in run 29. The aggregate index for this run was also in biomass units rather than abundance. 
The age composition likelihood was switched to "dir-mult" (dirichlet multinomial age comp likelihood that estimates effective sample size).

Selectivity-at-age was first freely estimated (comment out lines 49-52), which did not result in a converged model but did suggest the following ages should be fixed at full selectivity: 



### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
Same data as PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT but survey index effective sample size set to 100. 
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit-highESS.DAT", sep="/"))
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
# init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5),
#                        c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
#                        c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.75),
#                        c(0.5, 0.5, 1, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))
init_index_sel <- lapply(1:use_n_indices, function(x) rep( 0.5,11))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

# fix_index_sel[[1]] <- c(4,5,6) # Fix age 4, 5 & 6 for for index 1 (NEFSC spring Albatross)
# fix_index_sel[[2]] <- c(4,5) # Fix age 4 & 5 for for index 2 (NEFSC spring Bigelow)
# fix_index_sel[[3]] <- c(4) # Fix age 4 for index 3 (NEFSC fall Albatross)
# fix_index_sel[[4]] <- c(3,4,5) # Fix age 3, 4 & 5 for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("none", asap3$dat$n_fleet_sel_blocks), rep("none", 4))
#randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29G", age_comp = "dir-mult") # dirichlet multinomial
input$data$index_Neff[] = 500
input$data$catch_Neff[] = 500
input$map$logit_q = factor(rep(NA,use_n_indices))
input$par$logit_q = wham:::gen.logit(2,input$data$q_lower,input$data$q_upper)
```


### Fit model, check convergence, and run diagnostics
```{r}
# Run with OSA residuals
WHAM_Run29H_free <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE, do.retro=FALSE)

#selectivity
lapply(WHAM_Run29H_free$rep$selAA[-1], function(x) x[1,]/max(x[1,]))
#index 1: age 4 
#index 2: age 5 (age 4 ~0.95) 
#index 3: age 4
#index 4: age 5 (age 4 ~0.99)  #age 4 goes to 1 when RE for fleet selectivity is turned on below

#overdispersion parameter
apply(rbind(WHAM_Run29H_free$parList$catch_paa_par,WHAM_Run29H_free$parList$index_paa_par), 1, function(x)  exp(x[1]))
#variance inflation relative to multinomial
apply(rbind(WHAM_Run29H_free$parList$catch_paa_par,WHAM_Run29H_free$parList$index_paa_par), 1, function(x) (200 + exp(x[1]))/(1+exp(x[1])))

init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
                       c(0.5, 0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
                       c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))
fix_index_sel[[1]] <- c(4) # Fix age 4, 5 & 6 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]] <- c(5) # Fix age 4 & 5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]] <- c(4) # Fix age 4 for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 3, 4 & 5 for index 4 (NEFSC fall Bigelow)

randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4))

sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29H", age_comp = "dir-mult") # dirichlet multinomial
input$data$index_Neff[] = 500
input$data$catch_Neff[] = 500

#need to change do.retro, and do.osa for full results
WHAM_Run29H <- fit_wham(input, MakeADFun.silent = TRUE, do.osa=FALSE, do.retro=FALSE)

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29H_splitNEFSC-BigUnits-dirmultAgeComp", "WHAM_Run29H_input.rds", sep="/"))
```

check_convergence(WHAM_Run29H)
print(paste("Number of parameters", length(WHAM_Run29H$par), sep=" "))

plot_wham_output(mod=WHAM_Run29H, out.type='html')
# plot_wham_output(mod=WHAM_Run29H, out.type='png', dir.main = paste(here::here(), "WHAM_Run29H", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29H, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29H_splitNEFSC-BigUnits-dirmultAgeComp", "WHAM_Run29H_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29G_splitNEFSC-BigUnits-dirmultAgeComp/WHAM_Run29G_input.rds", sep="/"))

# Rerun data
ReRun29G <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Even with only recruitment random effects implemented the model struggled to estimate the dirichlet-multinomial dispersion parameters, and those that were estimated had very large values. 
