---
title: "WHAM_Run47A_addEnvCov-q-anomBT-withEffect-ar1"
output: html_document
date: '2022-05-17'
---

## Model description
Model specified as in run 41A with an environmental effect on catchability for all indices, but implements and ar1 process rather than a random walk. Annual bottom temperature anomaly was the environmental covariate considered here.


### Environmental covariate description
Annual bottom temperature anomalies were calculated by Jamie Behan using the GLORYS reanalysis product. A base period of 1981-2010 was used to calculate the temperature anomalies 


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load environmental data 
BT <- read.csv(paste(here::here(), "data", "GLORYS_se.csv", sep="/"))
BT <- BT %>% filter(Year>1979)
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "BT_GLORYS",
    mean = as.matrix(BT$anomaly_bt),
    logsigma = as.matrix(log(BT$se_anomaly)),
    year = as.numeric(BT$Year),
    use_obs = matrix(c(rep(TRUE, nrow(BT))), ncol = 1, nrow=nrow(BT)), # use all obs except the first 2 (no data 1979 and 1980, not full year of data in 1981) 
    lag = 0, # No  lag for catchability effect
    process_model = "ar1",
    where = "q", # "q" when turned on
    how = 1, # 1 when turned on
    indices = list(c(1,2,3,4)) # Indices to apply rand effect to NULL if not applying to an index (may want to exclude for Bigelow?)
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run47A") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run47A_addEnvCov-q-anomBT-withEffect-ar1", "WHAM_Run47A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run47A <- fit_wham(input, do.osa = TRUE, do.retro = TRUE) 
check_convergence(WHAM_Run47A)
print(paste("Number of parameters", length(WHAM_Run47A$par), sep=" "))

plot_wham_output(mod=WHAM_Run47A, out.type='html')
# plot_wham_output(mod=WHAM_Run47A, out.type='png', dir.main = paste(here::here(), "WHAM_Run47A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run47A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run47A_addEnvCov-q-anomBT-withEffect-ar1", "WHAM_Run47A_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run47A_addEnvCov-q-anomBT-withEffect-ar1/WHAM_Run47A_input.rds", sep="/"))

# Rerun data
ReRun47A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Age comp OSA residuals for the fleet and all indices had similar magnitudes and patterns for run 47 and 47A. OSA residuals for fit to aggregate fleet and index data were similarly distributed in both runs except for Albatross fall which was slightly more normally distributed.

BT anomaly OSA residuals were not very normally distributed.

SSB and R estimates were slightly lower and F estimates were slightly higher than in run 47 and CVs around these estimates were slightly higher at the end of the time series. Selectivity at ages older than 5 were slightly higher in Bigelow spring and Albatross fall indices but slightly lower for Albatross spring and Bigelow fall. 

AIC was smaller for run 47A  but Mohn's rho values were larger except for recruitment. There were minor improvements for this run, but the fit to the environmental covariate was still poor.

Note: not all diagnostic plots were generated due to an issue plotting OSA residuals for fit to the BT anomaly data