---
title: "WHAM_Run29C_splitNEFSC-biomass"
output: html_document
date: '2022-04-07'
---

## Model description
Full state-space model as in run 29 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), with NEFSC bottom trawl surveys split into Albatross (1980-2008, indices 1 and 3 for spring/fall) and Bigelow (2009-2019, indices 2 and 4 for spring/fall) time series in Albatross units, but NEFSC data is biomass units rather than abundance. 

An initial run was conducted to freely estimate selectivity-at-age for the fleet and with a selectivity random effect implemented for all indices (see comment on line 44 for details and WHAM_Run29C_input_FreeSelEstimate.rds for data used in this run). Although this run did not converge, it suggested that ages 4-5 for Albatross spring (index 1), age 5 for Bigelow spring (index 2), age 4 for Albatross spring (index 3), and ages 4-5 for Bigelow fall (index 4) were fully selected so selectivity was fixed at 1 for these ages in the converged run below, and only Albatross spring had variable selectivity so a random effect was only included for this index in the full run below. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-biomass.DAT", sep="/"))
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

# Tried running with the following 4 lines commented to freely estimate all survey selectivities-at-age and no survey selectivity random effect (line 52 uncommented, line 51 commented) 
fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks),  "iid", rep("none", 3)) # Don't include selectivity random effects for surveys except for Albatross spring 
# randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks),  rep("iid", use_n_indices)) # Include selectivity random effects for surveys, and fleet

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29C") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29C_splitNEFSC-biomass", "WHAM_Run29C_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# WHAM_Run29C <- fit_wham(input, do.osa=F,do.retro=F) 
# check_convergence(WHAM_Run29C)
# WHAM_Run29C$parList$sel_repars #variance of selectivity random effects -> 0 for (last 3) surveys except first (Albatross Spring?) 
# # I suspect that the increased flexibility in the random effects for numbers at age negates the need for selectivity RE for these surveys. So, perhaps try removing the selectivity re for at least the last 3 surveys.
# print(paste("Number of parameters", length(WHAM_Run29C$par), sep=" "))

# Run with OSA residuals
WHAM_Run29C <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run29C)
print(paste("Number of parameters", length(WHAM_Run29C$par), sep=" "))

plot_wham_output(mod=WHAM_Run29C, out.type='html')
# plot_wham_output(mod=WHAM_Run29C, out.type='png', dir.main = paste(here::here(), "WHAM_Run29C", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run29C, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29C_splitNEFSC-biomass", "WHAM_Run29C_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run29C_splitNEFSC-biomass/WHAM_Run29C_input.rds", sep="/"))

# Rerun data
ReRun29C <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
This run (Albatross and biomass units) was conducted to identify if improvement in selectivity patterns between run 29 (Albatross and abundance units) and run 29A (Bigelow and biomass units) was due to the switch to Bigelow units or biomass units, or both.

Catchability estimates for index 3 (Albatross fall) were higher than for the other indices with index 1 (Albatross spring) and 4 (Bigelow fall) more similar than in run 29.

Selectivity random effects for index 1 (Albatross spring) were smaller than in run 29 and could probably be turned off before this run would be considered a reasonable candidate (run 29B still appears to be a bit better). Selectivity estimates for age 11+ in both fall indices (3 and 4) are still higher than for age 10 so the improvement in this pattern for index 4 (Bigelow fall) appears to be due to the switch to Bigelow units in runs 29A and 29B. 

Catch residuals more evenly distributed around zero early in the time series as was also seen in run 29A and 29B but not in run 29. This suggests that this improvement is due to the switch to biomass units NOT to the switch to Bigelow units. 

OSA age comp residuals for the fleet and spring indices had similar patterns but larger maximum values compared to run 29. The fall indices followed similar patterns but had slightly smaller maximum values. The patterns and magnitude of these residuals were very similar to those in run 29B. 
