---
title: "WHAM_Run32_addLPUE"
output: html_document
date: '2022-04-11'
---

## Model description
Recruitment random effects as in run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with additional LPUE index (index 3). The selectivity for the LPUE index was set to mirror that estimated for the fleet. 

LPUE index and CV pulled from Plaice_LPUE_Standardization_Index_01242022.lxsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the LPUE index in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 3
#modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices)) # LPUE 
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 2), "logistic") # LPUE assumed logistic selectivity

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(2,0.4))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # set up index selectivity object
fix_index_sel[[3]] = 1:2 #fix logistic selectivity pars for third index because we aren't going to use it.

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block - index 3 (LPUE) selectivity will be the same as the fleet
randeffect <- c(rep("iid", 3), "none")#, asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(n_selblocks = 1+use_n_indices,
                 model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run32") 
input$data$selblock_pointer_indices[,3] = 1 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run32_addLPUE", "WHAM_Run32_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
# WHAM_Run32 <- fit_wham(input, do.osa =F, do.retro=F) # Run without OSA and retro calculations
WHAM_Run32 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run32)
print(paste("Number of parameters", length(WHAM_Run32$par), sep=" "))

plot_wham_output(mod=WHAM_Run32, out.type='html')
# plot_wham_output(mod=WHAM_Run32, out.type='png', dir.main = paste(here::here(), "WHAM_Run32", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run32, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run32_addLPUE", "WHAM_Run32_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run32_addLPUE/WHAM_Run32_input.rds", sep="/"))

# Rerun data
ReRun32 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model didn't converge when full state-space model implemented, but did converge with an invertible hessian when only recruitment random effects were included, and survey selectivity random effects were implemented (except for the LPUE index with selectivity mirroring the fleet).

Fit to catch data has larger negative residuals than Run25 in the middle of the time series. OSA residuals for the fleet were less normally distributed than in run 25, but were similarly distributed for the NEFSC indices. 

Age comp OSA residuals for the fleet and NEFSC spring index had similar patterns to run 25. The NEFSC fall index had more differences in residual magnitude, particularly for ages 4-7 (generally smaller in earlier years but very large positive residuals at the end of the time series in run 32). Fleet OSA age comp residuals and the NEFSC indices age comp residuals are similar or slightly less normally distributed than in run 25.
