---
title: "WHAM_Run32_addLPUE"
output: html_document
date: '2022-04-01'
---

## Model description
Recruitment random effects as in run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, with an iid random effect for selectivity, recruitment that is random about the mean), with additional LPUE index (index 3).

LPUE index and CV pulled from Plaice_LPUE_Standardization_Index_01242022.lxsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the LPUE indicex in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") # Full state space
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 3
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 2), "logistic") # LPUE assumed logistic selectivity

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), c(2,0.4))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # set up index selectivity object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2

# Setup random effect by selectivity block (here: fleet, index1, index2, index3)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run32") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run32_addLPUE", "WHAM_Run32_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run32 <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run32)
print(paste("Number of parameters", length(WHAM_Run32$par), sep=" "))

plot_wham_output(mod=WHAM_Run32, out.type='html')
# plot_wham_output(mod=WHAM_Run32, out.type='png', dir.main = paste(here::here(), "WHAM_Run32", sep="/"))
beep()
beep()
beep()
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run32, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run32_addLPUE", "WHAM_Run32_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run32_addLPUE/WHAM_Run32_input.rds", sep="/"))

# Rerun data
ReRun32 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model didn't converge when full state-space model implemented, even after survey selectivity random effects were removed. Model did converge with an invertible hessian when only recruitment random effects were included, and survey selectivity random effects were implemented.

Fit to catch data has slightly larger negative residuals than Run25 at the end of the timeseries, but the fleet age comp likelihood contribution is slightly smaller. Other likelihood contributions are similar to Run25. OSA age comp residuals for index 1 (NEFSC spring) were largely negative while for index 2 these were largely positive. Observed-predicted residuals were similar for the fleet and indices 1 and 2 across runs 25 and 32. Fleet OSA residuals are slightly more normally distributed, NEFSC index OSA residuals are similar across runs, and LPUE index 3 OSA residuals are normally distributed.
