---
title: "WHAM_Run33_addMADMF-MENH"
output: html_document
date: '2022-04-01'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), except with an iid random effect for only fleet selectivity, and added additional MADMF spring and fall (index 3 and 4 respectively) and MENH spring and fall (index 5 and 6 respectively) indices. 

MADMF spring data was pulled from MADMF_Spr_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MADMF fall data was pulled from MADMF_Fall_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MENH spring data was pulled from AMP_MENH_Spring_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

MENH fall data was pulled from AMP_MENH_Fall_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)

# Overwrite settings to use the MENH indices
asap3$dat$use_index_acomp[13:14] <- 1 # use index age comp
asap3$dat$use_index[13:14] <- 1 # use indices 13-14 (MENH)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # Full state space 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 6
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF fall
                       c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1), # MENH spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1))  # MENH fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2 NEFSC fall
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3 MADMF spring
fix_index_sel[[4]][1] <- 2 # Fix age 2 for for index 4 MADMF fall
fix_index_sel[[5]][1] <- 2 # Fix age 2 for index 5 MENH spring
fix_index_sel[[6]][1] <- 1 # Fix age 1 for index 6 MENH fall

# Setup random effect by selectivity block 
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run33") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run33_addMADMF-MENH", "WHAM_Run33_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run33 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = TRUE) 
check_convergence(WHAM_Run33)
print(paste("Number of parameters", length(WHAM_Run33$par), sep=" "))

plot_wham_output(mod=WHAM_Run33, out.type='html')
# plot_wham_output(mod=WHAM_Run33, out.type='png', dir.main = paste(here::here(), "WHAM_Run33", sep="/"))
beep()
beep()
beep()
```

### Debug
```{r}
# Look at parameter list
WHAM_Run33$parList
WHAM_Run33$rep$logit_selpars

# Look at parameter estimates
WHAM_Run33$sdrep

# debug NA/NaN
WHAM_Run33A <- fit_wham(input, do.fit=F)
therep = WHAM_Run33A$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run33, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run33_addMADMF-MENH", "WHAM_Run33_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run33_addMADMF-MENH/WHAM_Run33_input.rds", sep="/"))

# Rerun data
ReRun33 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model converged with an invertible hessian after removing survey selectivity random effects (only include fleet selectivity random effects. The model never converged when random effects were included for the survey indices in the full state-space model.

CV of recruitment estimates were lower towards the end of the timeseries than in Run25. NEFSC spring and fall selectivity at older ages (6-11+) was slightly higher than in Run25, selectivity patterns for the spring and fall MADMF indices were similar to Run30, but the fall index had lower estimates for selectivity at age 3. Similarly, the selectivity patterns for spring and fall MENH indices were similar to Run31, including a higher estimate of selectivity for age 10 than for ages 9 or 11+. 

The fit to catch data was slightly worse than in Run25, with larger residuals. Fits to the NEFSC indices were similar to Run25, but residuals toward the end of the time series were largely positive while residuals for MADMF and MENH indices in the same years were mostly negative. 

Fleet age comp residuals were larger in some years and ages (particularly age 11+ near the end of the time series and age 4). Age comp residuals for both spring and fall NEFSC indices were slightly larger in many years, especially near the end of the time series and for ages 1-4. MADMF and MENH indices had much larger age comp residuals, particularly for ages 1-2. 

Fleet and NEFSC index age comp likelihood contributions were higher than in Run25. 

Comments on full state-space attempt and exploration of freely estimating selectivity while developing this model: Unidentifiable parameters when full state-space model implemented. Freely estimating all selectivity parameters allowed the model to converge but with selectivity estimated at 0 for MADMF fall and both spring and fall MENH indices. 

