---
title: "WHAM_Run33_addMADMF-MENH"
output: html_document
date: '2022-04-01'
---

## Model description
Full state-space model as in run 27 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), except with an iid random effect for only fleet selectivity, and added additional MADMF spring and fall (index 3 and 4 respectively) and MENH spring and fall (index 5 and 6 respectively) indices. 

MADMF spring data was pulled from MADMF_Spr_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MADMF fall data was pulled from MADMF_Fall_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MENH spring data was pulled from AMP_MENH_Spring_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

MENH fall data was pulled from AMP_MENH_Fall_Survey_AgeComp_2000-2019_11Plus.xlsx with CVs pulled from Americanplaice_indices_MEDMR.xlsx

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)

# Overwrite settings to use the MENH indices
asap3$dat$use_index_acomp[13:14] <- 1 # use index age comp
asap3$dat$use_index[13:14] <- 1 # use indices 13-14 (MENH)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec+1") # Full state space 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 6
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF fall
                       c(0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1), # MENH spring
                       c(1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.1, 0.1))  # MENH fall

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2 NEFSC fall
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3 MADMF spring
fix_index_sel[[4]][1] <- 2 # Fix age 2 for for index 4 MADMF fall
fix_index_sel[[5]][1] <- 2 # Fix age 2 for index 5 MENH spring
fix_index_sel[[6]][1] <- 1 # Fix age 1 for index 6 MENH fall

# Setup random effect by selectivity block 
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", use_n_indices))

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run33") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run33_addMADMF-MENH", "WHAM_Run33_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run33 <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = TRUE) 
check_convergence(WHAM_Run33)
print(paste("Number of parameters", length(WHAM_Run33$par), sep=" "))

plot_wham_output(mod=WHAM_Run33, out.type='html')
# plot_wham_output(mod=WHAM_Run33, out.type='png', dir.main = paste(here::here(), "WHAM_Run33", sep="/"))
beep()
beep()
beep()
```

### Debug
```{r}
# Look at parameter list
WHAM_Run33$parList
WHAM_Run33$rep$logit_selpars

# Look at parameter estimates
WHAM_Run33$sdrep

# debug NA/NaN
WHAM_Run33A <- fit_wham(input, do.fit=F)
therep = WHAM_Run33A$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run33, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run33_addMADMF-MENH", "WHAM_Run33_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run33_addMADMF-MENH/WHAM_Run33_input.rds", sep="/"))

# Rerun data
ReRun33 <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Model converged with an invertible hessian after removing survey selectivity random effects (only include fleet selectivity random effects). The model never converged when selectivity random effects were included for the survey indices in the full state-space model.

Extreme catch residuals have a smaller magnitude and are more evenly distributed around zero near the end of the time series than in run 27. Index 1 and 2 (NEFSC) residuals are positive at the end of the time series while MADMF (index 3 and 4) and index 5 and 6 (MENH) have generally negative residuals during the same time period.

Fleet age comp, and index 1 and 2 age comp likelihood were larger than for run 27, but the NAA likelihood contribution was smaller. Recruitment residuals were more consistently negative near the end of the time series than in run 27. NEFSC selectivity at ages 6-11+ was lower than for run 27. 

Fits to annual age comp data for index 3 and 4 (MADMF spring and fall) and index 5 and 6 (MENH spring and fall) were often worse (larger observed-predicted residuals) for age 1 and 2 than for older ages.  Fleet observed-predicted residuals are comparable to run 27, but index 1 (NEFSC spring) had larger residuals towards the end of the time series, particularly for age 2. Similarly residuals for index 2 (NEFSC fall) were larger for age 1 and 2 for run 33.  Index 3 (MADMF spring) consistently had larger residuals for age 2, index 4 (MADMF fall) had large residuals for age 1 and 2 in the final years of the time series. Indices 5 and 6 (MENH spring and fall) had large residuals for ages 1-3 but were a mix of positive and negative residuals. OSA age comp residuals for the fleet, and indices 1 and 2 had higher max residuals that were very evident for ages 1-3. 

Fleet OSA residuals were slightly less normally distributed than in run 27, as were index 1 (NEFSC spring) OSA residuals. Index 2 (NEFSC fall) OSA residuals were similar to run 27. Index 3 and 4 (MADMF) had OSA residuals that did not have particularly normal distributions, while index 5 and 6 (MENH) were normally distributed. OSA age comp residuals were more normally distributed for the fleet and index 2 in run 33 than in run 27.

CV of recruitment estimates were lower and did not increase toward the end of the time series as in run 27. 

