---
title: "WHAM_Run29B_EffectiveSampleSize"
output: html_document
date: '2022-04-18'
---

## Description
This script fits a series of models specified like run 29B but with effective sample size varied from 10-100 in increments of 10 to evaluate the sensitivity of this model to different assumed effective sample size. The model did not converge with an invertible hessian when the effective sample size was set to 10. 

 
### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

## Indices
### Loop over effective sample size settings for indices
```{r}
### Load data
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))


### Prepare model input
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29B") 

### Loop over effective sample size options
for(ieff in seq(10, 100, by = 10)){
  ### Update effective sample size
  # Catch 
  # input$data$catch_Neff <- matrix(rep(ieff,40), ncol = 1)
  # Indices
  input$data$index_Neff[which(input$data$index_Neff != -999)] <- ieff
  
  ### Save input
  saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B_EffectiveSampleSize", paste("WHAM_Run29B_eff", ieff, "input.rds", sep="_"), sep="/"))
  
  ### Fit model
  # Run without OSA residuals and retrospective analysis
  WHAM_Run29B_eff <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = FALSE) 
  print(paste("EFF", ieff))
  check_convergence(WHAM_Run29B_eff)
  
  ### Save output
  saveRDS(WHAM_Run29B_eff, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B_EffectiveSampleSize", paste("WHAM_Run29B_eff", ieff, "model.rds", sep="_"), sep="/"))
}

```






### Compare runs across index ESS values
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_20_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_30_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_40_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_50_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_60_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_70_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_80_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_90_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_100_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Eff", c(20, 30, 40, 50, 60, 70, 80, 90, 100), sep="")

# Generate comparative diagnostics
compare_wham_models(models, do.plot = TRUE, do.table=TRUE,  fdir=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B_EffectiveSampleSize", sep="/"), plot.opts=list(which = c(1, 2, 3, 4, 5, 6, 7, 8, 9)))
```
### Generate likelihood profiles for the above runs
Borrowed lines 119-146 from plot.ll.table.fn()
```{r}
totalNLL <- rep(NA, 10) 
names(totalNLL) <- c(paste("Run", seq(10,100,by=10), sep="_"))
for(ieff in seq(20,100,by=10)){
  ### Load fitted model results
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29_splitNEFSC/WHAM_Run29_model.rds",
                   paste("WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff", ieff, "model.rds", sep="_")), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- c("Run29", "RunCalcNLL")

mod <- models$RunCalcNLL

### Calculate total negative log likelihood
  npar <- length(mod$opt$par)
  lls = mod$rep[c(grep("nll",names(mod$rep)), grep("lprior_b", names(mod$rep)))]
  ll.names = names(lls)
  #n.like <- length(lls)
  n_fleets = mod$env$data$n_fleets
  n_indices = mod$env$data$n_indices
  obs.lls = lls[names(lls) %in% c("nll_agg_catch", "nll_catch_acomp", "nll_agg_indices", "nll_index_acomp")]
  obs.lls = lapply(obs.lls, function(x) apply(x,2,sum))
  names(obs.lls$nll_agg_catch) = paste0("Fleet ", 1:n_fleets, " Catch")
  names(obs.lls$nll_catch_acomp) = paste0("Fleet ", 1:n_fleets, " Age Comp")
  names(obs.lls$nll_agg_indices) = paste0("Index ", 1:n_indices, " Catch")
  names(obs.lls$nll_index_acomp) = paste0("Index ", 1:n_indices, " Age Comp")
  names(obs.lls) = NULL
  obs.lls = unlist(obs.lls)
  n.obs.ll = length(obs.lls)
  obs.dists = character(n.obs.ll)
  names(obs.dists) = names(obs.lls)
  obs.dists[grep("Catch", names(obs.lls))] = "log(x) ~ Gaussian"
  acm = c("Multinomial", "Dirichlet-multinomial", "Dirichlet (miss0)", "Dirichlet (pool0)","Logistic normal (miss0)",
    "Logistic normal AR1 corr (miss0)", "Logistic normal (pool0)", "ZI-logistic normal(1)","ZI-logistic normal(2)")
  obs.dists[paste0("Fleet ", 1:n_fleets, " Age Comp")] = paste0("x ~ ", acm[mod$env$data$age_comp_model_fleets])
  obs.dists[paste0("Index ", 1:n_indices, " Age Comp")] = paste0("x ~ ", acm[mod$env$data$age_comp_model_fleets])
  proc.lls = lls[names(lls) %in% c("nll_M", "nll_NAA", "nll_recruit", "lprior_b")]
  names(proc.lls) = c("M", "NAA", "recruit", "W_b_M")[match(names(proc.lls),c("nll_M", "nll_NAA", "nll_recruit", "lprior_b"))]
  proc.lls = unlist(lapply(proc.lls, sum))
  n.proc.ll = length(proc.lls)
  proc.dists = rep("log(x) ~ Gaussian", n.proc.ll)
  likes = -c(obs.lls, proc.lls)
  
  ### Total NLL
  totalNLL[ieff/10] <- sum(likes)
}

NLL <- data_frame(totalNLL = totalNLL[-1], Effective_Sample_Size = seq(20,100,by=10))
ggplot() +
  geom_line(data = NLL, aes(x=Effective_Sample_Size, y=totalNLL))
ggsave(filename = paste(here::here(), "WG_Revised_Runs/WHAM_Run29B_EffectiveSampleSize/Likelihood_profile.png", sep="/"))

```

## Fleet
### Loop over effective sample size settings for fleet
```{r}
### Load data
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))


### Prepare model input
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run29B") 

### Loop over effective sample size options
for(ieff in seq(10, 100, by = 10)){
  ### Update effective sample size
  # Catch 
  input$data$catch_Neff <- matrix(rep(ieff,40), ncol = 1)
  # Indices
  # input$data$index_Neff[which(input$data$index_Neff != -999)] <- ieff
  
  ### Save input
  saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B_EffectiveSampleSize", paste("WHAM_Run29B_eff", ieff, "fleet", "input.rds", sep="_"), sep="/"))
  
  ### Fit model
  # Run without OSA residuals and retrospective analysis
  WHAM_Run29B_eff <- fit_wham(input, MakeADFun.silent = TRUE, do.osa = FALSE) 
  print(paste("EFF", ieff))
  check_convergence(WHAM_Run29B_eff)
  
  ### Save output
  saveRDS(WHAM_Run29B_eff, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B_EffectiveSampleSize", paste("WHAM_Run29B_eff", ieff, "fleet", "model.rds", sep="_"), sep="/"))
}

```

### Compare runs across fleet ESS values
```{r}
modelRuns <- paste(here::here(), "WG_Revised_Runs",
                   c("WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_20_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_30_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_40_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_50_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_60_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_70_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_80_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_90_fleet_model.rds",
                     "WHAM_Run29B_EffectiveSampleSize/WHAM_Run29B_eff_100_fleet_model.rds"), sep="/")

# Read in model Rdata
models <- lapply(modelRuns, readRDS)
names(models) <- paste("Eff", c(20, 30, 40, 50, 60, 70, 80, 90, 100), sep="")

# Generate comparative diagnostics
compare_wham_models(models, do.plot = TRUE, do.table=TRUE,  fdir=paste(here::here(), "WG_Revised_Runs", "WHAM_Run29B_EffectiveSampleSize", sep="/"), plot.opts=list(which = c(1, 2, 3, 4, 5, 6, 7, 8, 9)))
```

