---
title: "WHAM_Run35A_addMADMF-LPUE_mirrorLPUE"
output: html_document
date: '2022-04-13'
---

## Model description
IID recruitment random effects as in run 25 (revised data, fixed selectivity at intermediate ages, logistic fleet selectivity, age-specific index selectivity, recruitment that is random about the mean), but implements a selectivity iid random effect for only the fleet and mirrors this selectivity for the LPUE index (index 5) and also adds additional MADMF spring and fall indices (index 3 and 4 respectively).

MADMF spring data was pulled from MADMF_Spr_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

MADMF fall data was pulled from MADMF_Fall_Survey Age Composition_11Plus (1980-2019).xlsx with CVs pulled from Indices.csv

LPUE index and CV pulled from Plaice_LPUE_Standardization_Index_01242022.lxsx


### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_StateIndices.DAT", sep="/"))

# Overwrite settings to use the MADMF indices
asap3$dat$use_index_acomp[3:4] <- 1 # use index age comp
asap3$dat$use_index[3:4] <- 1 # use indices 3-4 (MADMF)

# Overwrite settings to use the LPUE indicex in addition to NEFSC
asap3$dat$use_index_acomp[15] <- 0 # No age comp for this index 
asap3$dat$use_index[15] <- 1 # use indicex 15 (LPUE)
```

### Prepare model input
```{r}
# iid random effects for recruitment only 
NAA_re = list(sigma = "rec") 
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup initial selectivity model and parameters
use_n_indices = 5
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", 4), "logistic")  # LPUE assumed logistic selectivity

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- list(c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC spring
                       c(0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # NEFSC fall
                       c(0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF spring
                       c(0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5), # MADMF fall
                       c(2,0.4)) # LPUE

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index selectivity fix object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 # NEFSC spring
fix_index_sel[[2]][1] <- 4 # Fix age 4 for for index 2 # NEFSC fall
fix_index_sel[[3]][1] <- 3 # Fix age 3 for for index 3 # MADMF spring
fix_index_sel[[4]][1] <- 2 # Fix age 2 for for index 4 # MADMF fall
fix_index_sel[[5]] = 1:2 #fix logistic selectivity pars for LPUE index because we aren't going to use it.

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4), "none") # Don't estimate random effect for LPUE index

# Setup selectivity list
sel_list <- list(n_selblocks = 1+use_n_indices,
                 model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, model_name = "WHAM_Run35A") 
input$data$selblock_pointer_indices[,5] = 1 # Mirror selectivity for LPUE index (5) using fleet selectivity
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run35A_addMADMF-LPUE_mirrorLPUE", "WHAM_Run35A_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run35A <- fit_wham(input, MakeADFun.silent = TRUE) 
check_convergence(WHAM_Run35A)
print(paste("Number of parameters", length(WHAM_Run35A$par), sep=" "))

plot_wham_output(mod=WHAM_Run35A, out.type='html')
# plot_wham_output(mod=WHAM_Run35A, out.type='png', dir.main = paste(here::here(), "WHAM_Run35A", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run35A, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run35A_addMADMF-LPUE_mirrorLPUE", "WHAM_Run35A_model.rds", sep="/"))
```

### Debug
```{r}
# Look at parameter list
WHAM_Run35A$parList
WHAM_Run35A$rep$logit_selpars

# Look at parameter estimates
WHAM_Run35A$sdrep

# debug NA/NaN
WHAM_Run35AA <- fit_wham(input, do.fit=F)
therep = WHAM_Run35AA$report()
names(therep)
sapply(grep("nll",names(therep),value=T), function(x) sum(therep[[x]]))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run35A_addMADMF-LPUE_mirrorLPUE/WHAM_Run35A_input.rds", sep="/"))

# Rerun data
ReRun35A <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
Estimates of Full F and accompanying CVs followed very different trends from run 30 (only included NEFSC + MADMF indices). CVs around estimates of SSB and R were both smaller in magnitude than those in run 30 except for R near the end of the time series. NEFSC index (1 and 2) selectivity patterns followed similar trends but estimates of selectivity at ages greater than 4 tended to be higher in run 35A than in run 30. MADMF indices (3 and 4) had similar selectivity patterns and the LPUE index (5) selectivity was set to mirror the fleet.

Catch residuals had more of a pattern with much larger extreme residuals across the time series compared to run 30. Fleet OSA residuals were less normally distributed than in run 30 while the NEFSC and MADMF indices had residuals that were similar or slightly less normally distributed. The LPUE index (5) did not have particularly normally distributed residuals. The NEFSC age comp OSA residuals were more normally distributed and the MADMF age comp OSA residuals had a similar distribution to run 30. 

Fleet and index age comp residuals tended to follow similar patterns, but there were more large residuals in run 35A than in run 30, particularly for ages 1-5. 
