---
title: "WHAM_Run38B_addEnvCov-BT-withEffect-2lag"
output: html_document
date: '2022-04-20'
---

## Model description
Model specified as identically to run 38 but incorporates the environmental effect on recruitment. Mean annual bottom temperature was the environmental covariate considered here, with a 2 year lag (bottom temperature in year t impacts recruitment in year t+2) and a random walk process model. 

### Load R packages
```{r, echo=FALSE}
library(tidyverse)
library(wham)
library(readxl)
library(DataExplorer)
```

### Load data
```{r}
# ASAP data input
asap3 <- read_asap3_dat(paste(here::here(), "data", "PlaiceWHAM-2019_revised_NEFSC-LW-WAA_splitNEFSC-BigUnit.DAT", sep="/"))

# Load and filter environmental data to match year range of other model data
annualBT <- read.csv(paste(here::here(), "data", "year_bt_stdmean.csv", sep="/"))
annualBT <- filter(annualBT, as.numeric(Year) > 1978) # Filter to match timeframe of other data + 1 year before other data (here 1979) to allow for 1 year lag
```

### Prepare model input
```{r}
NAA_re = list(sigma = "rec+1") # Full state-space model
NAA_re$cor = "iid" # iid random effects
NAA_re$recruit_model = 2 # recruitment is random about the mean
NAA_re$recruit_pars = exp(10) #initial guess for mean recruitment

# Setup environmental covariate and options
  ecov <- list(
    label = "BT_FVCOM",
    mean = as.matrix(annualBT$mean_bt),
    logsigma = as.matrix(log(annualBT$standard_err_bt)),
    # logsigma = as.matrix(log(10*annualBT$standard_err_bt)),
    year = as.numeric(annualBT$Year),
    use_obs = matrix(T, ncol = 1, nrow=nrow(annualBT)), # use all obs = T
    lag = 2, # BT in year t impact R in year t+2
    #process_model = "ar1",
    process_model = "rw",
    where = "recruit", # "recruit" for recruitment effect
    how = 1 # 1 for controlling = density-independent mortality
  )

# Setup initial selectivity model and parameters
use_n_indices = 4
modelsetup <- c(rep("logistic", asap3$dat$n_fleet_sel_blocks), rep("age-specific", use_n_indices))

init_fleet_sel <- list(c(2,0.4)) # logistic parameters, based on model type
init_index_sel <- lapply(1:use_n_indices, function(x) c(0.5, 0.5, 0.5, 1, 1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5))

# Setup fixed parameters
fix_fleet_sel <- lapply(1:asap3$dat$n_fleets, function(x) NA) 
fix_index_sel <- lapply(1:use_n_indices, function(x) NA) # Set up index object

fix_index_sel[[1]] <- c(4,5) # Fix age 4 & 5 for for index 1 (NEFSC spring Albatross)
fix_index_sel[[2]][1] <- 5 # Fix age  5 for for index 2 (NEFSC spring Bigelow)
fix_index_sel[[3]][1] <- 4 # Fix age 4 for for index 3 (NEFSC fall Albatross)
fix_index_sel[[4]] <- c(4,5) # Fix age 4 for for index 4 (NEFSC fall Bigelow)

# Setup random effect by selectivity block (here: fleet, index1, index2)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("iid", use_n_indices))

# Setup random effect by selectivity block (here: fleet, index1, index2, index3, index4)
randeffect <- c(rep("iid", asap3$dat$n_fleet_sel_blocks), rep("none", 4)) # Don't include selectivity random effects for any surveys 

# Setup selectivity list
sel_list <- list(model = modelsetup, # list selectivity model for each fleet and index
                 re = randeffect,
                 initial_pars = c(init_fleet_sel, init_index_sel),
                 fix_pars = c(fix_fleet_sel, fix_index_sel))

input <- prepare_wham_input(asap3, NAA_re = NAA_re, selectivity = sel_list, ecov=ecov, model_name = "WHAM_Run38B") 
```

### Save input
```{r}
# Save model data input
saveRDS(input, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run38B_addEnvCov-BT-withEffect-2lag", "WHAM_Run38B_input.rds", sep="/"))
```

### Fit model, check convergence, and run diagnostics
```{r}
WHAM_Run38B <- fit_wham(input, do.osa = FALSE, do.retro = FALSE) 
check_convergence(WHAM_Run38B)
print(paste("Number of parameters", length(WHAM_Run38B$par), sep=" "))

plot_wham_output(mod=WHAM_Run38B, out.type='html')
# plot_wham_output(mod=WHAM_Run38B, out.type='png', dir.main = paste(here::here(), "WHAM_Run38B", sep="/"))
```

### Save output
```{r}
# Save fitted model
saveRDS(WHAM_Run38B, file=paste(here::here(), "WG_Revised_Runs", "WHAM_Run38B_addEnvCov-BT-withEffect-2lag", "WHAM_Run38B_model.rds", sep="/"))
```

### Rerun model using saved input data
Load data from saved input RData and rerun model
```{r}
inputRerun <- readRDS(paste(here::here(), "WG_Revised_Runs",
                     "WHAM_Run38B_addEnvCov-BT-withEffect-2lag/WHAM_Run38B_input.rds", sep="/"))

# Rerun data
ReRun38B <- fit_wham(input = inputRerun, MakeADFun.silent = TRUE)
```

## Comment
